### 2019-04-15 README.Rmd
Create README.Rmd

---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# `robvis`: an R pacakge for quick visualisation of risk-of-bias assessment results

[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)
[![Build Status](https://travis-ci.org/mcguinlu/robvis.svg?branch=master)](https://travis-ci.org/mcguinlu/robvis)

## Description
The `robvis` package takes the summary table from risk-of-bias assessments, converts it to tidy data, produces a summary plot (incorporating some measure of weighting for each study), and formats the plot according to the assessment tool used.

The package contains two functions:

### rob_summary()
Returns a ggplot object displaying a weighted barchart of the risk of bias of included studies across the domains of the specified tool.

### rob_summary_tools()
Outputs a list of the risk of bias assessment tools for which a template currently exists in rob_suumary(). Users can currently produce summary plots for three commonly used tools: ROB2.0, ROBINS-I and QUADAS-2. We expect this list to be updated in the near future to inlcude tools such as ROBIS (tool for assessing risk of bias in systematic reviews).

    rob_summary_tools()
    [1] "ROB2"
    [1] "ROBINS-I"
    [1] "QUADAS-2"

## Getting started
### Install the `robvis` R package
First ensure you have the `devtools` package installed:

```{r, eval=FALSE}
install.packages("devtools")
library(devtools)
```

Then, to install:
```{r, eval=FALSE}   
install_github("mcguinlu/robvis")
library(robvis)
```

To update the package, run the `install_github("mcguinlu/robvis")` command again.

### Load data
Load your own data (mostly likely from a .csv)

```{r, eval=FALSE}
mydata <- read.csv("path/to/mydata.csv", header = TRUE)
```

To familiarise users with the package, we have included three example datasets, one for each fo the tool templates that currently exist within `rob_summary()`. These datasets are used to create the example plots below.

### Create basic plots
```{r include = FALSE}
library(robvis)
```

**For the RoB2.0 tool for randomized controlled trials:**
```{r}
plot_rob <- rob_summary(data = data_rob, tool = "ROB2")
plot_rob
```

**For the ROBINS-I tool for non-randomised studies of interventions:**
```{r}
plot_robins <- rob_summary(data = data_robins, tool = "ROBINS-I")
plot_robins
```

**For the QUADAS-2 tool for diagnostic accuracy studies:**
```{r}
plot_quadas <- rob_summary(data = data_quadas, tool = "QUADAS-2")
plot_quadas
```

### Include overall risk-of-bias judgements
```{r}
plot_rob <- rob_summary(data = data_robins, tool = "ROBINS-I", overall = TRUE)
plot_rob
```

## Additional usage
Because the output (`plot` in the above examples) is a ggplot2 object, it is easy to adjust the plot to your own preferences.

For example, to add a title to the RoB2.0 plot created above:
```{r warning=FALSE}
library(ggplot2)

plot_rob +
  ggtitle("Summary of RoB2.0 assessments")
```

## License

This project is licensed under the MIT License - see the [LICENSE.md](LICENSE.md) file for details

## Acknowledgments

* Emily Kothe for contribution to `ggplot2` coding issues

### 2019-04-15 README.Rmd
Update README.md

@@
   fig.path = "man/figures/README-",
-  out.width = "100%"
-)
+  out.width = "90%",
+  fig.width= 8, 
+  fig.height=3)
 ```

### 2019-04-15 README.Rmd
Update README.md

--- 2019-04-15 README.Rmd
@@
   fig.path = "man/figures/README-",
-  out.width = "100%"
-)
+  out.width = "70%",
+  fig.width= 10, 
+  fig.height=3)
 ```

### 2019-04-15 README.Rmd
Update README.md

--- 2019-04-15 README.Rmd
@@
   fig.path = "man/figures/README-",
-  out.width = "100%"
-)
+  out.width = "80%",
+  fig.width= 12, 
+  fig.height=3)
 ```

### 2019-04-15 README.Rmd
Update README.md

--- 2019-04-15 README.Rmd
@@
   out.width = "90%",
-  fig.width= 8, 
+  fig.width= 12, 
   fig.height=3)

### 2019-04-24 R/rob_summary.R
Updated description.

@@ -1,5 +1,5 @@
 #' Produce summary weighted barplots of risk-of-bias assessments.
-#' @description A function to convert standard risk-of-bias output to tidy data .
+#' @description A function to convert standard risk-of-bias output to tidy data and plot a summary barplot.
 #' @param data A dataframe containing summary (domain) level risk-of-bias assessments, with the first column containing the study details, the second column containing the first domain of your assessments, and the final column containing a weight to assign to each study. The function assumes that the data includes a column for overall risk-of-bias. For example, a ROB2.0 dataset would have 8 columns (1 for study details, 5 for domain level judgements, 1 for overall judgements, and 1 for weights, in that order).
 #' @param tool The risk of bias assessment tool used. RoB2.0 (tool="ROB2"), ROBINS-I (tool="ROBINS-I"), and QUADAS-2 (tool="QUADAS-2") are currently supported.
 #' @param save An option to save the plot as the specified file type. Default is FALSE, and available extensions are ".eps", ".ps", ".tex", ".pdf", ".jpeg", ".tiff", ".png" and ".bmp".

### 2019-04-24 R/rob_traffic_light.R
Create rob_traffic_light.R

@@ -1,0 +1,48 @@
+#' Produce traffic-light plots of risk-of-bias assessments.
+#' @description A function
+#' @param data A dataframe containing summary (domain) level risk-of-bias assessments, with the first column containing the study details, the second column containing the first domain of your assessments, and the final column containing a weight to assign to each study. The function assumes that the data includes a column for overall risk-of-bias. For example, a ROB2.0 dataset would have 8 columns (1 for study details, 5 for domain level judgements, 1 for overall judgements, and 1 for weights, in that order).
+#' @param tool The risk of bias assessment tool used. RoB2.0 (tool="ROB2"), ROBINS-I (tool="ROBINS-I"), and QUADAS-2 (tool="QUADAS-2") are currently supported.
+#' @param save An option to save the plot as the specified file type. Default is FALSE, and available extensions are ".eps", ".ps", ".tex", ".pdf", ".jpeg", ".tiff", ".png" and ".bmp".
+#' @param overall An option to include a bar for overall risk-of-bias in the figure. Default is FALSE.
+#' @param quiet An option to quietly produce and save the plot without it displaying in R/Rstudio.
+#' @return Risk of bias assessment barplot figure..
+#' @export
+
+data.tmp <- data_rob
+  if(NCOL(data.tmp) < 8){stop("Column missing (number of columns < 8). Likely that a column detailing weights for each study is missing.")}
+  names(data.tmp)[2] <- "Bias due to randomisation"
+  names(data.tmp)[3] <- "Bias due to deviations from intended intervention"
+  names(data.tmp)[4] <- "Bias due to missing data"
+  names(data.tmp)[5] <- "Bias due to outcome measurement"
+  names(data.tmp)[6] <- "Bias due to selection of reported result"
+  names(data.tmp)[7] <- "Overall risk of bias"
+  names(data.tmp)[8] <- "Weight"
+
+  data.tmp <- data.tmp[, c(1:7)]
+
+  rob.tidy <- suppressWarnings(tidyr::gather(data.tmp,
+                                            domain, judgement, -Study))
+
+psize <- 3
+
+outcome_graph <-  ggplot(rob.tidy, aes(x=1, y=1, colour = judgement)) +
+  facet_grid(Study ~ factor(domain, levels=c("Bias due to randomisation",
+                                             "Bias due to deviations from intended intervention",
+                                             "Bias due to missing data",
+                                             "Bias due to outcome measurement",
[…]

### 2019-04-24 README.Rmd
Updated README to include line on metaverse
Add hex sticker, thanks to Eliza Grames

@@
 ```
-# `robvis`: an R pacakge for quick visualisation of risk-of-bias assessment results
+# robvis <img src="man/figures/robvis_hex_box.png" align="right" width="18%" height="18%" />
 
@@
 [![Build Status](https://travis-ci.org/mcguinlu/robvis.svg?branch=master)](https://travis-ci.org/mcguinlu/robvis)
+
+Part of the [metaverse](https://github.com/rmetaverse/metaverse)
 

### 2019-04-24 R/rob_traffic_light.R
Remove traffic light plot function from Master branch

@@ -1,48 +1,0 @@
-#' Produce traffic-light plots of risk-of-bias assessments.
-#' @description A function
-#' @param data A dataframe containing summary (domain) level risk-of-bias assessments, with the first column containing the study details, the second column containing the first domain of your assessments, and the final column containing a weight to assign to each study. The function assumes that the data includes a column for overall risk-of-bias. For example, a ROB2.0 dataset would have 8 columns (1 for study details, 5 for domain level judgements, 1 for overall judgements, and 1 for weights, in that order).
-#' @param tool The risk of bias assessment tool used. RoB2.0 (tool="ROB2"), ROBINS-I (tool="ROBINS-I"), and QUADAS-2 (tool="QUADAS-2") are currently supported.
-#' @param save An option to save the plot as the specified file type. Default is FALSE, and available extensions are ".eps", ".ps", ".tex", ".pdf", ".jpeg", ".tiff", ".png" and ".bmp".
-#' @param overall An option to include a bar for overall risk-of-bias in the figure. Default is FALSE.
-#' @param quiet An option to quietly produce and save the plot without it displaying in R/Rstudio.
-#' @return Risk of bias assessment barplot figure..
-#' @export
-
-data.tmp <- data_rob
-  if(NCOL(data.tmp) < 8){stop("Column missing (number of columns < 8). Likely that a column detailing weights for each study is missing.")}
-  names(data.tmp)[2] <- "Bias due to randomisation"
-  names(data.tmp)[3] <- "Bias due to deviations from intended intervention"
-  names(data.tmp)[4] <- "Bias due to missing data"
-  names(data.tmp)[5] <- "Bias due to outcome measurement"
-  names(data.tmp)[6] <- "Bias due to selection of reported result"
-  names(data.tmp)[7] <- "Overall risk of bias"
-  names(data.tmp)[8] <- "Weight"
-
-  data.tmp <- data.tmp[, c(1:7)]
-
-  rob.tidy <- suppressWarnings(tidyr::gather(data.tmp,
-                                            domain, judgement, -Study))
-
-psize <- 3
-
-outcome_graph <-  ggplot(rob.tidy, aes(x=1, y=1, colour = judgement)) +
-  facet_grid(Study ~ factor(domain, levels=c("Bias due to randomisation",
-                                             "Bias due to deviations from intended intervention",
-                                             "Bias due to missing data",
-                                             "Bias due to outcome measurement",
[…]

### 2019-04-24 R/rob_traffic_light.R
Inital commit for final traffic light plotting function

@@ -1,21 +1,28 @@
 #' Produce traffic-light plots of risk-of-bias assessments.
-#' @description A function
+#' @description A function to take a summary table of risk of bias assessments and produce a traffic light plot from it.
 #' @param data A dataframe containing summary (domain) level risk-of-bias assessments, with the first column containing the study details, the second column containing the first domain of your assessments, and the final column containing a weight to assign to each study. The function assumes that the data includes a column for overall risk-of-bias. For example, a ROB2.0 dataset would have 8 columns (1 for study details, 5 for domain level judgements, 1 for overall judgements, and 1 for weights, in that order).
 #' @param tool The risk of bias assessment tool used. RoB2.0 (tool="ROB2"), ROBINS-I (tool="ROBINS-I"), and QUADAS-2 (tool="QUADAS-2") are currently supported.
 #' @param save An option to save the plot as the specified file type. Default is FALSE, and available extensions are ".eps", ".ps", ".tex", ".pdf", ".jpeg", ".tiff", ".png" and ".bmp".
-#' @param overall An option to include a bar for overall risk-of-bias in the figure. Default is FALSE.
 #' @param quiet An option to quietly produce and save the plot without it displaying in R/Rstudio.
-#' @return Risk of bias assessment barplot figure..
+#' @return Risk-of-bias assessment traffic light plot ggplot2::ggplot2 object
 #' @export
 
-data.tmp <- data_rob
-  if(NCOL(data.tmp) < 8){stop("Column missing (number of columns < 8). Likely that a column detailing weights for each study is missing.")}
-  names(data.tmp)[2] <- "Bias due to randomisation"
-  names(data.tmp)[3] <- "Bias due to deviations from intended intervention"
-  names(data.tmp)[4] <- "Bias due to missing data"
-  names(data.tmp)[5] <- "Bias due to outcome measurement"
-  names(data.tmp)[6] <- "Bias due to selection of reported result"
-  names(data.tmp)[7] <- "Overall risk of bias"
+rob_traffic_light <- function(data, tool, save = FALSE, quiet = FALSE) {
+
+judgement <- NULL
+Study <- NULL
+domain <- NULL
+
+
+if (tool == "ROB2") {
+  data.tmp <- data
[…]

### 2019-04-24 vignettes/Introduction_to_robvis.R

@@ -1,0 +1,22 @@
+## ----setup, include=FALSE------------------------------------------------
+knitr::opts_chunk$set(
+  collapse = TRUE,
+  comment = "#>",
+  warning = FALSE,
+  fig.width = 8,
+  fig.height = 2.41)
+  library(ggplot2)
+  library(robvis)
+
+## ----headrob-------------------------------------------------------------
+knitr::kable(data_rob)
+
+## ----rob2summary---------------------------------------------------------
+rob_summary(data_rob, tool = "ROB2")
+
+## ----robinssummary-------------------------------------------------------
+rob_summary(data_robins, tool = "ROBINS-I")
+
+## ----quadassummary-------------------------------------------------------
+rob_summary(data_quadas, tool = "QUADAS-2")
+

### 2019-04-24 R/rob_traffic_light.R
traffic light plot

@@ -1,0 +1,177 @@
+#' Produce traffic-light plots of risk-of-bias assessments.
+#' @description A function to take a summary table of risk of bias assessments and produce a traffic light plot from it.
+#' @param data A dataframe containing summary (domain) level risk-of-bias assessments, with the first column containing the study details, the second column containing the first domain of your assessments, and the final column containing a weight to assign to each study. The function assumes that the data includes a column for overall risk-of-bias. For example, a ROB2.0 dataset would have 8 columns (1 for study details, 5 for domain level judgements, 1 for overall judgements, and 1 for weights, in that order).
+#' @param tool The risk of bias assessment tool used. RoB2.0 (tool="ROB2"), ROBINS-I (tool="ROBINS-I"), and QUADAS-2 (tool="QUADAS-2") are currently supported.
+#' @param save An option to save the plot as the specified file type. Default is FALSE, and available extensions are ".eps", ".ps", ".tex", ".pdf", ".jpeg", ".tiff", ".png" and ".bmp".
+#' @param quiet An option to quietly produce and save the plot without it displaying in R/Rstudio.
+#' @return Risk-of-bias assessment traffic light plot ggplot2::ggplot2 object
+#' @export
+
+rob_traffic_light <- function(data, tool, save = FALSE, quiet = FALSE) {
+
+judgement <- NULL
+Study <- NULL
+domain <- NULL
+
+
+if (tool == "ROB2") {
+  data.tmp <- data
+  if(NCOL(data.tmp) < 7){stop("Column missing (number of columns < 7).")}
+  names(data.tmp)[2] <- "D1"
+  names(data.tmp)[3] <- "D2"
+  names(data.tmp)[4] <- "D3"
+  names(data.tmp)[5] <- "D4"
+  names(data.tmp)[6] <- "D5"
+  names(data.tmp)[7] <- "Overall"
+  names(data.tmp)[8] <- "Weight"
+
+  data.tmp <- data.tmp[, c(1:7)]
+
+  rob.tidy <- suppressWarnings(tidyr::gather(data.tmp,
+                                            domain, judgement, -Study))
+
+  psize <- 20
+  ssize <- psize - (psize/4)
+
+trafficlightplot <-  ggplot2::ggplot(rob.tidy, ggplot2::aes(x=1, y=1, colour = judgement)) +
+  ggplot2::facet_grid(Study ~ factor(domain, levels=c("D1",
[…]

### 2019-04-24 README.Rmd

@@
 ### rob_summary_tools()
-Outputs a list of the risk of bias assessment tools for which a template currently exists in rob_suumary().
+Outputs a list of the risk of bias assessment tools for which a template currently exists in rob_summary().
 Users can currently produce summary plots for three commonly used tools: ROB2.0, ROBINS-I and QUADAS-2.
@@
 
-This project is licensed under the MIT License - see the [LICENSE.md](LICENSE.md) file for details
+This project is licensed under the MIT License - see the [LICENSE.md](https://github.com/mcguinlu/robvis/blob/traffic_light_plot/LICENSE) file for details.
 
@@
 
-* Emily Kothe for contribution to `ggplot2` coding issues
+* [Emily Kothe](https://github.com/ekothe) for help in fixing `ggplot2` coding issues.
+* [Eliza Grames](https://github.com/elizagrames) for creating the `robvis` hex sticker.

### 2019-05-01 README.Rmd
Move to v0.1.1 Update DESCRIPTION to reflect new version number Update README to add in new function (rob_traffic_light) Renamed rob_summary_tools() function to rob_tools()

@@
   comment = "#>",
-  fig.path = "man/figures/README-",
-  out.width = "90%",
-  fig.width= 12, 
-  fig.height=3)
+  fig.path = "man/figures/README-")
 ```
@@
 ## Description
+**UPDATE**: `robvis` now exists as a [web-app](https://mcguinlu.shinyapps.io/robvis), aimed at those who are not confident with R/those who want to explore the package's functionality.
+
 The `robvis` package takes the summary table from risk-of-bias assessments, converts it to tidy data, produces a summary plot (incorporating some measure of weighting for each study), and formats the plot according to the assessment tool used.
 
-The package contains two functions:
+The package contains three functions:
 
@@
 
-### rob_summary_tools()
+### rob_traffic_light()
+Returns a ggplot object displaying a ["traffic light plot"](https://handbook-5-1.cochrane.org/chapter_8/figure_8_6_c_example_of_a_risk_of_bias_summary_figure.htm), displaying the risk of bias judgement made in each domain for each study.
+
+### rob_tools()
 Outputs a list of the risk of bias assessment tools for which a template currently exists in rob_summary().
@@
 
-**For the RoB2.0 tool for randomized controlled trials:**
-```{r}
+#### RoB2.0 tool for randomized controlled trials:
+```{r out.width = "90%", fig.width= 12, fig.height=3}
 plot_rob <- rob_summary(data = data_rob, tool = "ROB2")
@@
 
-**For the ROBINS-I tool for non-randomised studies of interventions:**
+```{r out.width = "90%", fig.width= 8, fig.height=8}
+trafficlight_rob <- rob_traffic_light(data = data_rob, tool = "ROB2")
+trafficlight_rob
+```
+
+#### ROBINS-I tool for non-randomised studies of interventions:**
 ```{r}
@@
 
-**For the QUADAS-2 tool for diagnostic accuracy studies:**
+#### QUADAS-2 tool for diagnostic accuracy studies:**
 ```{r}
@@
 
-### Include overall risk-of-bias judgements
-```{r}
-plot_rob <- rob_summary(data = data_robins, tool = "ROBINS-I", overall = TRUE)
-plot_rob
-```
-
 ## Additional usage
-Because the output (`plot` in the above examples) is a ggplot2 object, it is easy to adjust the plot to your own preferences.
+Because the output (`plot_tool` in the above examples) is a ggplot2 object, it is easy to adjust the plot to your own preferences.
 
@@
 
+## Planned updates
+
+* Templates for additional risk of bias tools, including:
+  * Cochrane risk of bias tool for randomised controlled trials (RoB Version 1)
+  * PROBAST
+  * ROBIS
+* Ability to specify file type extension when saving image. Priority being Window 
+* Additional functionality to specify the element of QUADAS-2 that you want to visualise (applicability or risk of bias)
+* Choice of colour schemes (or ability to specify your own colours, have not decided yet)
+* Improved text processing to allow for imperfect matching of judgements, primarily to allow for differences in cases (e.g.
+"low" will match with "Low"" and for minor spelling errors (e.g.
+"loq" will match with "Low")
+* A planned function to provide a brief draft paragraph summarising the risk-of-bias assessment results, which authors can then edit/elaborate on as needed.
+This element of the project was inspired by the reporter function in `metafor`
+
 ## License

### 2019-05-01 R/rob_summary_tools.R

@@ -1,8 +1,8 @@
 #' List tools covered by rob_summary().
-#' @description rob_sumary_tools() will list the tools that can currently be plotted using the rob_summary() function.
+#' @description rob_tools() will list the tools that can currently be plotted using the rob_summary() function.
 #' @export
 
-rob_summary_tools <- function(){
+rob_tools <- function(){
   print("ROB2")
   print("ROBINS-I")
   print("QUADAS-2")

### 2019-05-01 README.Rmd
Update README
Fix figure sizing in README

@@
   comment = "#>",
-  fig.path = "man/figures/README-")
+  fig.path = "man/figures/README-", 
+  out.width = "90%",
+  fig.width= 12,
+  fig.height=3)
 ```
@@
 
-    rob_summary_tools()
+    rob_tools()
     [1] "ROB2"
@@
 #### RoB2.0 tool for randomized controlled trials:
-```{r out.width = "90%", fig.width= 12, fig.height=3}
+```{r}
 plot_rob <- rob_summary(data = data_rob, tool = "ROB2")

### 2019-05-13 README.Rmd
Added Travis logo to the README badge for Travis CI status

@@
 [![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)
-[![Build Status](https://travis-ci.org/mcguinlu/robvis.svg?branch=master)](https://travis-ci.org/mcguinlu/robvis)
+[![Build Status](https://img.shields.io/travis/mcguinlu/robvis.svg?label=build&logo=travis&branch=master)](https://travis-ci.org/mcguinlu/robvis)
 

### 2019-05-13 README.Rmd
Added "Part of the metaverse" badge

--- 2019-05-01 README.Rmd
@@
 [![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)
-[![Build Status](https://travis-ci.org/mcguinlu/robvis.svg?branch=master)](https://travis-ci.org/mcguinlu/robvis)
-
-Part of the [metaverse](https://github.com/rmetaverse/metaverse)
+[![Build Status](https://img.shields.io/travis/mcguinlu/robvis.svg?label=build&logo=travis&branch=master)](https://travis-ci.org/mcguinlu/robvis) 
+[![metaverse Identifier](https://img.shields.io/static/v1.svg?label=Part%20of%20the&message=metaverse&color=informational)](https://www.github.com/rmetaverse/metaverse)
+<br>
 

### 2019-05-13 README.Rmd
Fix spacing issues on GitHub

--- 2019-05-01 README.Rmd
@@
 [![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)
-[![Build Status](https://travis-ci.org/mcguinlu/robvis.svg?branch=master)](https://travis-ci.org/mcguinlu/robvis)
+[![Build Status](https://img.shields.io/travis/mcguinlu/robvis.svg?label=build&logo=travis&branch=master)](https://travis-ci.org/mcguinlu/robvis) 
+[![metaverse Identifier](https://img.shields.io/static/v1.svg?label=Part%20of%20the&message=metaverse&color=informational)](https://www.github.com/rmetaverse/metaverse)
 
-Part of the [metaverse](https://github.com/rmetaverse/metaverse)
+<br>
 

### 2019-05-20 R/rob_summary.R
Updated to include functionality for ROB1/generic tool
Solves mcguinlu/robvisapp#5, as users will not need to specify the number of user-defined columns because the tool automatically detects it.

@@ -374,8 +374,7 @@ if (tool == "QUADAS-2") {
       low_colour <- colour[c(1)]
       concerns_colour <- colour[c(2)]
       high_colour <- colour[c(3)]
-    }
-    else {
+    } else {
       if (colour == "colourblind") {
         low_colour <- "#fee8c8"
         concerns_colour <- "#fdbb84"
@@ -427,20 +426,14 @@ if (tool == "QUADAS-2") {
 
     rob.tidy$judgement <- as.factor(rob.tidy$judgement)
 
-    rob.tidy$domain <- as.factor(rob.tidy$domain)
+    rob.tidy$judgement <- factor(rob.tidy$judgement,
+                                 levels(rob.tidy$judgement)[c(1, 3, 2)])
 
-    rob.tidy$domain <- factor(rob.tidy$domain)
-
-    i<-1
-    while(i != (ncol(data.tmp))){
+    for (i in 1:(ncol(data.tmp)-1)) {
     levels(rob.tidy$domain)[i] <- colnames(data.tmp)[i]
-    i<-i+1
     }
 
     rob.tidy$domain <- factor(rob.tidy$domain, levels = rev(levels(rob.tidy$domain)))
-
-    rob.tidy$judgement <- factor(rob.tidy$judgement,
-                                 levels(rob.tidy$judgement)[c(1, 3, 2)])
 
     # Create plot
     plot <- ggplot2::ggplot(data = rob.tidy) +

### 2019-05-20 vignettes/Introduction_to_robvis.R
Updates to vignettes
Main change is "data_rob" to "data_rob2", as we know have a distinct example dataset for each tool.

@@ -9,10 +9,10 @@ knitr::opts_chunk$set(
   library(robvis)
 
 ## ----headrob-------------------------------------------------------------
-knitr::kable(data_rob)
+knitr::kable(data_rob2)
 
 ## ----rob2summary---------------------------------------------------------
-rob_summary(data_rob, tool = "ROB2")
+rob_summary(data_rob2, tool = "ROB2")
 
 ## ----robinssummary-------------------------------------------------------
 rob_summary(data_robins, tool = "ROBINS-I")

### 2019-05-23 R/rob_summary.R
Fixes #18

@@ -54,11 +54,11 @@ if (tool == "ROB2") {
 
     # Rename column headings
     data.tmp <- data
-    names(data.tmp)[2] <- "Bias due to randomisation"
-    names(data.tmp)[3] <- "Bias due to deviations from intended intervention"
-    names(data.tmp)[4] <- "Bias due to missing data"
-    names(data.tmp)[5] <- "Bias due to outcome measurement"
-    names(data.tmp)[6] <- "Bias due to selection of reported result"
+    names(data.tmp)[2] <- "Bias arising from the randomization process"
+    names(data.tmp)[3] <- "Bias due to deviations from intended interventions"
+    names(data.tmp)[4] <- "Bias due to missing outcome data"
+    names(data.tmp)[5] <- "Bias in measurement of the outcome"
+    names(data.tmp)[6] <- "Bias in selection of the reported result"
     names(data.tmp)[7] <- "Overall risk of bias"
     names(data.tmp)[8] <- "Weights"
 

### 2019-05-23 R/rob_traffic_light.R
Fixes #19

@@ -46,6 +46,7 @@ if (tool == "ROB2") {
 
   data.tmp <- data
   if(NCOL(data.tmp) < 7){stop("Column missing (number of columns < 7).")}
+  names(data.tmp)[1] <- "Study"
   names(data.tmp)[2] <- "D1"
   names(data.tmp)[3] <- "D2"
   names(data.tmp)[4] <- "D3"
@@ -125,6 +126,7 @@ if (tool == "ROBINS-I") {
 
   data.tmp <- data
   if(NCOL(data.tmp) < 9){stop("Column missing (number of columns < 9).")}
+  names(data.tmp)[1] <- "Study"
   names(data.tmp)[2] <- "D1"
   names(data.tmp)[3] <- "D2"
   names(data.tmp)[4] <- "D3"
@@ -207,6 +209,7 @@ if (tool == "QUADAS-2") {
 
   data.tmp <- data
   if(NCOL(data.tmp) < 6){stop("Column missing (number of columns < 6).")}
+  names(data.tmp)[1] <- "Study"
   names(data.tmp)[2] <- "D1"
   names(data.tmp)[3] <- "D2"
   names(data.tmp)[4] <- "D3"
@@ -303,12 +306,10 @@ if (tool == "ROB1") {
   caption <- paste(captiondf$V1, collapse=" ")
 
   # Rename columns headings
+  names(data.tmp)[1] <- "Study"
   for (i in 2:(ncol(data.tmp)-1)) {
     names(data.tmp)[i] <- paste0("D",i-1)
   }
-
-
-
 
   # Convert to long format
   rob.tidy <- suppressWarnings(tidyr::gather(data.tmp,

### 2019-05-23 R/rob_summary_tools.R
Added "ROB1" to the rob_tools() function

@@ -6,4 +6,5 @@ rob_tools <- function(){
   print("ROB2")
   print("ROBINS-I")
   print("QUADAS-2")
+  print("ROB1")
 }

### 2019-05-23 README.Rmd
Fix spacing issues on GitHub
Major update to the README to reflect recent changes as part of V0.2.0

@@
 
-<br>
+**UPDATE**: `robvis` now exists as a [web-app](https://mcguinlu.shinyapps.io/robvis), aimed at those who are not familiar with R or who want to explore the package's functionality before installing it locally.
 
 ## Description
-**UPDATE**: `robvis` now exists as a [web-app](https://mcguinlu.shinyapps.io/robvis), aimed at those who are not confident with R/those who want to explore the package's functionality.
-
-The `robvis` package takes the summary table from risk-of-bias assessments, converts it to tidy data, produces a summary plot (incorporating some measure of weighting for each study), and formats the plot according to the assessment tool used.
-
-The package contains three functions:
-
-### rob_summary()
-Returns a ggplot object displaying a weighted barchart of the risk of bias of included studies across the domains of the specified tool.
-
-### rob_traffic_light()
-Returns a ggplot object displaying a ["traffic light plot"](https://handbook-5-1.cochrane.org/chapter_8/figure_8_6_c_example_of_a_risk_of_bias_summary_figure.htm), displaying the risk of bias judgement made in each domain for each study.
-
-### rob_tools()
-Outputs a list of the risk of bias assessment tools for which a template currently exists in rob_summary().
-Users can currently produce summary plots for three commonly used tools: ROB2.0, ROBINS-I and QUADAS-2.
-We expect this list to be updated in the near future to inlcude tools such as ROBIS (tool for assessing risk of bias in systematic reviews).
-
-    rob_tools()
-    [1] "ROB2"
-    [1] "ROBINS-I"
-    [1] "QUADAS-2"
+```{r include = FALSE}
+library(robvis)
+library(kableExtra)
+library(magrittr)
+```
+The `robvis` package takes the summary table from risk-of-bias assessments, converts it to tidy data, and produces summary plots formatted according to the assessment tool used.
 
 ## Getting started
-### Install the `robvis` R package
+### Install the `robvis` pacakage
 First ensure you have the `devtools` package installed:
@@
 ### Load data
-Load your own data (mostly likely from a .csv)
+To load your own data from a .csv file:
 
@@
 
-To familiarise users with the package, we have included three example datasets, one for each fo the tool templates that currently exist within `rob_summary()`.
-These datasets are used to create the example plots below.
+To help users explore `robvis`, we have included example datasets in the package, one for each fo the tool templates that currently exist within `rob_summary()`.
+The `data_rob2` dataset ([view it here](https://github.com/mcguinlu/robvis/blob/master/data_raw/data_rob2.csv)), which contains example risk-of-bias assessments performed using the RoB2.0 tool for randomized controlled trials, is used to create the plots in subsequent sections.
 
-### Create basic plots
-```{r include = FALSE}
-library(robvis)
+### Create plots
+
+The package contains two plotting functions:
+
+#### 1. rob_summary()
+Returns a ggplot object displaying a weighted barchart of the risk of bias of included studies across the domains of the specified tool.
+
+```{r, fig.height=3}
+summary_rob <- rob_summary(data = data_rob2, tool = "ROB2")
+summary_rob
 ```
 
-#### RoB2.0 tool for randomized controlled trials:
-```{r}
-plot_rob <- rob_summary(data = data_rob, tool = "ROB2")
-plot_rob
+#### 2. rob_traffic_light()
+Returns a ggplot object displaying a ["traffic light plot"](https://handbook-5-1.cochrane.org/chapter_8/figure_8_6_c_example_of_a_risk_of_bias_summary_figure.htm), displaying the risk of bias judgement in each domain for each study.
+
+```{r eval=FALSE}
+trafficlight_rob <- rob_traffic_light(data = data_rob2, tool = "ROB2")
+trafficlight_rob
+```    
+<img src="man/figures/rob2trafficlight.png" width="70%" height="70%"/>
+
+### Other functions
+#### rob_tools()
+Outputs a list of the risk of bias assessment tools for which a template currently exists in rob_summary().
+We expect this list to be updated in the near future to inlcude tools such as ROBIS (tool for assessing risk of bias in systematic reviews).
+
+    rob_tools()
+    [1] "ROB2"
+    [1] "ROBINS-I"
+    [1] "QUADAS-2"
+    [1] "ROB1"
+
+## Advanced usage
+### Change the colour scheme
+The `colour` argument of both plotting functions allows users to select from two predefined colour schemes ("cochrane" or "colourblind") or to define their own pallete by providing a vector of hex codes.
+
+For example, to use the predefined "colourblind" palette:
+
+```{r, fig.height=3}
+summary_rob <- rob_summary(data = data_rob2, tool = "ROB2", colour = "colourblind")
+summary_rob
 ```
 
-```{r out.width = "90%", fig.width= 8, fig.height=8}
-trafficlight_rob <- rob_traffic_light(data = data_rob, tool = "ROB2")
-trafficlight_rob
+And to define your own colour scheme:
+```{r, fig.height=3}
+summary_rob <- rob_summary(data = data_rob2, tool = "ROB2", colour = c("#f442c8","#bef441","#000000"))
+summary_rob
 ```
 
-#### ROBINS-I tool for non-randomised studies of interventions:**
-```{r}
-plot_robins <- rob_summary(data = data_robins, tool = "ROBINS-I")
-plot_robins
+### Created an unweighted summary barplot:
+By default, the `rob_summary()` function creates a barplot weighted by some measure of a study's precision.
+This can be prevented using the "weighted" argument.
+For example, compare the following two plots:
+
+```{r, fig.height=3}
+summary_rob <- rob_summary(data = data_rob2, tool = "ROB2")
+summary_rob
 ```
 
-#### QUADAS-2 tool for diagnostic accuracy studies:**
-```{r}
-plot_quadas <- rob_summary(data = data_quadas, tool = "QUADAS-2")
-plot_quadas
+```{r, fig.height=3}
+summary_rob <- rob_summary(data = data_rob2, tool = "ROB2", weighted = FALSE)
+summary_rob
 ```
 
-## Additional usage
-Because the output (`plot_tool` in the above examples) is a ggplot2 object, it is easy to adjust the plot to your own preferences.
+### Editing the plots
+Finally, because the output (`summary_rob` and `trafficlight_rob` in the examples above) is a ggplot2 object, it is easy to adjust the plot to your own preferences.
 
-For example, to add a title to the RoB2.0 plot created above:
-```{r warning=FALSE}
+For example, to add a title to the unweighted RoB2.0 plot created above:
+```{r warning=FALSE, fig.height=3}
 library(ggplot2)
 
-plot_rob +
+summary_rob +
   ggtitle("Summary of RoB2.0 assessments")
 ```
-
-## Planned updates
-
-* Templates for additional risk of bias tools, including:
-  * Cochrane risk of bias tool for randomised controlled trials (RoB Version 1)
-  * PROBAST
-  * ROBIS
-* Ability to specify file type extension when saving image. Priority being Window 
-* Additional functionality to specify the element of QUADAS-2 that you want to visualise (applicability or risk of bias)
-* Choice of colour schemes (or ability to specify your own colours, have not decided yet)
-* Improved text processing to allow for imperfect matching of judgements, primarily to allow for differences in cases (e.g.
-"low" will match with "Low"" and for minor spelling errors (e.g.
-"loq" will match with "Low")
-* A planned function to provide a brief draft paragraph summarising the risk-of-bias assessment results, which authors can then edit/elaborate on as needed.
-This element of the project was inspired by the reporter function in `metafor`
 

### 2019-05-23 README.Rmd
Fixed small typo
Fixed typo

@@
 
-To help users explore `robvis`, we have included example datasets in the package, one for each fo the tool templates that currently exist within `rob_summary()`.
+To help users explore `robvis`, we have included example datasets in the package, one for each of the tool templates that currently exist within the package.
 The `data_rob2` dataset ([view it here](https://github.com/mcguinlu/robvis/blob/master/data_raw/data_rob2.csv)), which contains example risk-of-bias assessments performed using the RoB2.0 tool for randomized controlled trials, is used to create the plots in subsequent sections.
@@
 
-### Created an unweighted summary barplot:
+### Created an unweighted summary barplot
 By default, the `rob_summary()` function creates a barplot weighted by some measure of a study's precision.

### 2019-06-20 README.Rmd
Add appveyor logo

@@
 [![Build Status](https://img.shields.io/travis/mcguinlu/robvis.svg?label=build&logo=travis&branch=master)](https://travis-ci.org/mcguinlu/robvis) 
+[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/mcguinlu/robvis?branch=master&svg=true)](https://ci.appveyor.com/project/mcguinlu/robvis)
 [![metaverse Identifier](https://img.shields.io/static/v1.svg?label=Part%20of%20the&message=metaverse&color=informational)](https://www.github.com/rmetaverse/metaverse)

### 2019-06-20 R/rob_traffic_light.R

@@ -323,7 +323,7 @@ if (tool == "ROB1") {
   rob.tidy$domain <- factor(rob.tidy$domain, levels = levels(rob.tidy$domain))
 
   # Set sizes
-  psize <- 20
+  psize <- 10
   ssize <- psize - (psize/4)
 
   # PLot graph

### 2019-06-20 R/rob_traffic_light.R
Update to add psize as an argument

@@ -3,11 +3,12 @@
 #' @param data A dataframe containing summary (domain) level risk-of-bias assessments, with the first column containing the study details, the second column containing the first domain of your assessments, and the final column containing a weight to assign to each study. The function assumes that the data includes a column for overall risk-of-bias. For example, a ROB2.0 dataset would have 8 columns (1 for study details, 5 for domain level judgements, 1 for overall judgements, and 1 for weights, in that order).
 #' @param tool The risk of bias assessment tool used. RoB2.0 (tool="ROB2"), ROBINS-I (tool="ROBINS-I"), and QUADAS-2 (tool="QUADAS-2") are currently supported.
 #' @param colour An argument to specify the colour scheme for the plot. Default is "cochrane" which used the ubiquitous Cochrane colours, while a preset option for a colour-blind friendly palette is also available (colour = "colourblind").
+#' @param psize Controll the size of the traffic lights
 #' @param quiet An option to quietly produce and save the plot without it displaying in R/Rstudio.
 #' @return Risk-of-bias assessment traffic light plot (ggplot2 object)
 #' @export
 
-rob_traffic_light <- function(data, tool, colour = "cochrane", quiet = FALSE) {
+rob_traffic_light <- function(data, tool, colour = "cochrane", psize = 20, quiet = FALSE) {
 
 judgement <- NULL
 Study <- NULL
@@ -60,7 +61,6 @@ if (tool == "ROB2") {
   rob.tidy <- suppressWarnings(tidyr::gather(data.tmp,
                                             domain, judgement, -Study))
 
-  psize <- 20
   ssize <- psize - (psize/4)
 
 trafficlightplot <-  ggplot2::ggplot(rob.tidy, ggplot2::aes(x=1, y=1, colour = judgement)) +
@@ -142,7 +142,6 @@ if (tool == "ROBINS-I") {
   rob.tidy <- suppressWarnings(tidyr::gather(data.tmp,
                                              domain, judgement, -Study))
 
-  psize <- 20
   ssize <- psize - (psize/4)
 
   trafficlightplot <-  ggplot2::ggplot(rob.tidy, ggplot2::aes(x=1, y=1, colour = judgement)) +
@@ -223,7 +222,6 @@ if (tool == "QUADAS-2") {
   rob.tidy <- suppressWarnings(tidyr::gather(data.tmp,
[…]

### 2019-08-09 README.Rmd
Updates to the README Added acknowledgement - closes #36 Automated creation of the rob_traffic_light() image

@@
 library(robvis)
+
 library(kableExtra)
@@
 
-```{r eval=FALSE}
+```{r, eval=FALSE}
 trafficlight_rob <- rob_traffic_light(data = data_rob2, tool = "ROB2")
@@
 ```
-<img src="man/figures/rob2trafficlight.png" width="70%" height="70%"/>
+
+``` {r, include=FALSE}
+trafficlight_rob <- rob_traffic_light(data = data_rob2, tool = "ROB2")
+ggplot2::ggsave(
+          "man/figures/rob2trafficlight.png",
+          plot = trafficlight_rob,
+          device = "png",
+          width = 6,
+          height = 9,
+          units = "in",
+          dpi = 800, 
+          limitsize = FALSE)
+```
+<center><img src="man/figures/rob2trafficlight.png" width="70%" height="70%"/></center>
 
@@
 
+* The `rob_summary()` function was based on code forwarded by a colleague.
+I have recently learnt that this code was adapted from the wonderful "[Doing Meta-Analysis in R](https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/)" guide, so I would like to retrospectively acknowledge the authors for their indirect help.
 * [Emily Kothe](https://github.com/ekothe) for help in fixing `ggplot2` coding issues.

### 2019-08-09 README.Rmd
Update README layout

@@
 ```
-<center><img src="man/figures/rob2trafficlight.png" width="70%" height="70%"/></center>
+<div style="text-align:center"><img src="man/figures/rob2trafficlight.png" width="70%" height="70%"/></div>
 

### 2019-08-09 R/rob_traffic_light.R
Updated the rob_traffic_light() function so that it no longer requires a "Weights" column, but can handle one if it is included in the uploaded dataset

@@ -45,7 +45,7 @@ if (tool == "ROB2") {
     data[[i]] <- substr(data[[i]], 0, 1)
   }
 
-  data.tmp <- data
+  data.tmp <- data[, c(1:7)]
   if(NCOL(data.tmp) < 7){stop("Column missing (number of columns < 7).")}
   names(data.tmp)[1] <- "Study"
   names(data.tmp)[2] <- "D1"
@@ -54,9 +54,8 @@ if (tool == "ROB2") {
   names(data.tmp)[5] <- "D4"
   names(data.tmp)[6] <- "D5"
   names(data.tmp)[7] <- "Overall"
-  names(data.tmp)[8] <- "Weight"
 
-  data.tmp <- data.tmp[, c(1:7)]
+
 
   rob.tidy <- suppressWarnings(tidyr::gather(data.tmp,
                                             domain, judgement, -Study))
@@ -145,7 +144,7 @@ if (tool == "ROBINS-I") {
     data[[i]] <- substr(data[[i]], 0, 1)
   }
 
-  data.tmp <- data
+  data.tmp <- data[, c(1:9)]
   if(NCOL(data.tmp) < 9){stop("Column missing (number of columns < 9).")}
   names(data.tmp)[1] <- "Study"
   names(data.tmp)[2] <- "D1"
@@ -156,9 +155,8 @@ if (tool == "ROBINS-I") {
   names(data.tmp)[7] <- "D6"
   names(data.tmp)[8] <- "D7"
   names(data.tmp)[9] <- "Overall"
-  names(data.tmp)[10] <- "Weight"
 
-  data.tmp <- data.tmp[, c(1:9)]
+
 
   rob.tidy <- suppressWarnings(tidyr::gather(data.tmp,
                                              domain, judgement, -Study))
@@ -215,7 +213,111 @@ if (tool == "ROBINS-I") {
                    plot.caption = ggplot2::element_text(size = 10, hjust = 0, vjust = 1)) +
     ggplot2::guides(shape = ggplot2::guide_legend(override.aes = list(fill=NA))) +
     ggplot2::labs(shape = "Judgement", colour = "Judgement") # Need to be exactly the same
+}
+
+# ROBINS-I ONLINE ==============================================================
+
+if (tool == "ROBINS-I Online") {
+
+  # Define colouring
+  if (length(colour) > 1) {
+    low_colour <- colour[c(1)]
+    concerns_colour <- colour[c(2)]
[…]

### 2019-08-09 R/rob_summary.R
Fixed typo

@@ -257,8 +257,8 @@ if (tool == "ROB2") {
                                                    reverse = TRUE))
   }
 
-# ROBINS-I  ONLINE============================================================
-  if (tool == "ROBINS-I") {
+# ROBINS-I ONLINE============================================================
+  if (tool == "ROBINS-I Online") {
 
     # Define colouring
     if (length(colour) > 1) {

### 2019-08-09 R/rob_traffic_light.R
Update to reorder legend in the ROBINS-I template
Closes #37

@@ -163,10 +163,18 @@ if (tool == "ROBINS-I") {
 
   ssize <- psize - (psize/4)
 
+
+
   rob.tidy$Study <- factor(rob.tidy$Study, levels = unique(data.tmp$Study))
 
+  rob.tidy$judgement <- as.factor(rob.tidy$judgement)
 
-  trafficlightplot <-  ggplot2::ggplot(rob.tidy, ggplot2::aes(x=1, y=1, colour = judgement)) +
+  rob.tidy$judgement <- factor(rob.tidy$judgement,
+                                 levels(rob.tidy$judgement)[c(1,4,3,2)])
+
+
+  trafficlightplot <-
+    ggplot2::ggplot(rob.tidy, ggplot2::aes(x=1, y=1, colour = judgement)) +
     ggplot2::facet_grid(Study ~ factor(domain, levels=c("D1",
                                                "D2",
                                                "D3",
@@ -181,6 +189,7 @@ if (tool == "ROBINS-I") {
                        ymin = -Inf,ymax = Inf, show.legend = FALSE) +
     ggplot2::geom_rect(data = rob.tidy[which(rob.tidy$domain=="Overall"),],fill="#d3d3d3",xmin = -Inf,xmax = Inf,
                        ymin = -Inf,ymax = Inf, show.legend = FALSE) +
+
     ggplot2::geom_point(size = psize, show.legend = FALSE) +
     ggplot2::geom_point(shape = 1, colour = "black", size = psize, show.legend = FALSE) +
     ggplot2::geom_point(size =ssize, colour = "black", ggplot2::aes(shape=judgement), show.legend = FALSE) +
@@ -196,8 +205,8 @@ if (tool == "ROBINS-I") {
                   ") +
     ggplot2::scale_x_discrete(position = "top", name = "Risk of bias domains") +
     ggplot2::scale_y_continuous(limits = c(1, 1), labels = NULL, breaks = NULL, name = "Study", position = "left") +
-    ggplot2::scale_colour_manual(values =c(critical_colour,low_colour,concerns_colour,high_colour), labels = c("Critical", "Low","Some concerns", "High")) +
-    ggplot2::scale_shape_manual(values = c(33,43,63,45), labels = c("Critical", "Low","Some concerns", "High")) +
+    ggplot2::scale_colour_manual(values =c(critical_colour,high_colour,concerns_colour,low_colour), labels = c("Critical","Serious", "Moderate","Low" )) +
[…]

### 2019-08-09 R/rob_summary.R
Updated description of the quiet parameter
Closes #34

@@ -3,7 +3,7 @@
 #' @param data A dataframe containing summary (domain) level risk-of-bias assessments, with the first column containing the study details, the second column containing the first domain of your assessments, and the final column containing a weight to assign to each study. The function assumes that the data includes a column for overall risk-of-bias. For example, a ROB2.0 dataset would have 8 columns (1 for study details, 5 for domain level judgements, 1 for overall judgements, and 1 for weights, in that order).
 #' @param tool The risk of bias assessment tool used. RoB2.0 (tool="ROB2"), ROBINS-I (tool="ROBINS-I"), and QUADAS-2 (tool="QUADAS-2") are currently supported.
 #' @param overall An option to include a bar for overall risk-of-bias in the figure. Default is FALSE.
-#' @param quiet An option to quietly produce and save the plot without it displaying in R/Rstudio.
+#' @param quiet An option to quietly produce the plot without displaying it.
 #' @param colour An argument to specify the colour scheme for the plot. Default is "cochrane" which used the ubiquitous Cochrane colours, while a preset option for a colour-blind friendly palette is also available (colour = "colourblind").
 #' @param weighted An option to specify whether weights should be used in the barplot. Default is TRUE, in line with current Cochrane Collaboration guidance.
 #' @return Risk of bias assessment barplot figure.

### 2019-08-09 R/rob_traffic_light.R

@@ -4,7 +4,7 @@
 #' @param tool The risk of bias assessment tool used. RoB2.0 (tool="ROB2"), ROBINS-I (tool="ROBINS-I"), and QUADAS-2 (tool="QUADAS-2") are currently supported.
 #' @param colour An argument to specify the colour scheme for the plot. Default is "cochrane" which used the ubiquitous Cochrane colours, while a preset option for a colour-blind friendly palette is also available (colour = "colourblind").
 #' @param psize Controll the size of the traffic lights
-#' @param quiet An option to quietly produce and save the plot without it displaying in R/Rstudio.
+#' @param quiet An option to quietly produce the plot without displaying it.
 #' @return Risk-of-bias assessment traffic light plot (ggplot2 object)
 #' @export
 

### 2019-08-09 README.Rmd
Update to the acknowledgement

@@
 * The `rob_summary()` function was based on code forwarded by a colleague.
-I have recently learnt that this code was adapted from the wonderful "[Doing Meta-Analysis in R](https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/)" guide, so I would like to retrospectively acknowledge the authors for their indirect help.
+I have recently learnt that this code was adapted from that presented in the wonderful "[Doing Meta-Analysis in R](https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/plotting-the-summary.html)" guide, so I would like to acknowledge the authors here.
 * [Emily Kothe](https://github.com/ekothe) for help in fixing `ggplot2` coding issues.

### 2019-08-14 R/test_functionality.R
Remove misplaced test function

@@ -1,4 +1,0 @@
-context("Check functionality")
-
-# Can handle with/without weights
-# ROB1 can handle multiple judgements

### 2019-08-14 R/rob_traffic_light.R
Add new variable to function to correctly position caption when number of items in legend varies

@@ -64,6 +64,10 @@ if (tool == "ROB2") {
 
   rob.tidy$Study <- factor(rob.tidy$Study, levels = unique(data.tmp$Study))
 
+  if(length(unique(rob.tidy$judgement))==1){adjust_caption <- -1.3}
+  if(length(unique(rob.tidy$judgement))==2){adjust_caption <- -1.9}
+  if(length(unique(rob.tidy$judgement))==3){adjust_caption <- -2.5}
+  if(length(unique(rob.tidy$judgement))==4){adjust_caption <- -3.1}
 
 trafficlightplot <-  ggplot2::ggplot(rob.tidy, ggplot2::aes(x=1, y=1, colour = judgement)) +
   ggplot2::facet_grid(Study ~ factor(domain, levels=c("D1",
@@ -101,7 +105,7 @@ trafficlightplot <-  ggplot2::ggplot(rob.tidy, ggplot2::aes(x=1, y=1, colour = j
         legend.position = "bottom",
         legend.justification = "right",
         legend.direction = "vertical",
-        legend.margin=ggplot2::margin(t=-0.2, r=0, b=-2.5, l=-10, unit="cm"),
+        legend.margin=ggplot2::margin(t=-0.2, r=0, b=adjust_caption, l=-10, unit="cm"),
         strip.text.x = ggplot2::element_text(size = 10),
         strip.text.y = ggplot2::element_text(angle = 180, size = 10),
         legend.text = ggplot2::element_text(size=9),
@@ -172,6 +176,11 @@ if (tool == "ROBINS-I") {
   rob.tidy$judgement <- factor(rob.tidy$judgement,
                                  levels(rob.tidy$judgement)[c(1,4,3,2)])
 
+  if(length(unique(rob.tidy$judgement))==1){adjust_caption <- -1.3}
+  if(length(unique(rob.tidy$judgement))==2){adjust_caption <- -1.9}
+  if(length(unique(rob.tidy$judgement))==3){adjust_caption <- -2.5}
+  if(length(unique(rob.tidy$judgement))==4){adjust_caption <- -3.1}
+  if(length(unique(rob.tidy$judgement))==5){adjust_caption <- -3.7}
 
   trafficlightplot <-
     ggplot2::ggplot(rob.tidy, ggplot2::aes(x=1, y=1, colour = judgement)) +
@@ -213,7 +222,7 @@ if (tool == "ROBINS-I") {
                    panel.spacing = ggplot2::unit(0, "line"),legend.position = "bottom",
[…]

### 2019-08-14 R/rob_summary.R
Updates to fix legend issues

@@ -216,7 +216,6 @@ if (tool == "ROB2") {
       ) +
       ggplot2::coord_flip(ylim = c(0, 1)) +
       ggplot2::scale_fill_manual(
-        "Risk of Bias",
         values = c(
           "m" = concerns_colour,
           "s" = high_colour,
@@ -224,10 +223,10 @@ if (tool == "ROB2") {
           "c" = critical_colour
         ),
         labels = c(
-          "  Critical risk  ",
-          "  Serious risk  ",
-          "  Moderate risk ",
-          "  Low risk  "
+          " Critical risk  ",
+          " Serious risk  ",
+          " Moderate risk ",
+          " Low risk  "
         )
       ) +
       ggplot2::scale_y_continuous(labels = scales::percent) +
@@ -247,8 +246,8 @@ if (tool == "ROB2") {
         panel.background = ggplot2::element_blank(),
         legend.background = ggplot2::element_rect(linetype = "solid",
                                                   colour = "black"),
-        legend.title = ggplot2::element_text(size=9, face = "bold"),
-        legend.key.size = ggplot2::unit(0.75, "cm"),
+        legend.title = ggplot2::element_blank(),
+        legend.key.size = ggplot2::unit(0.7, "cm"),
         legend.text = ggplot2::element_text(size = 8)
       ) +
       ggplot2::guides(fill = ggplot2::guide_legend(title = "Risk of bias judgement",
@@ -343,7 +342,7 @@ if (tool == "ROB2") {
       ) +
       ggplot2::coord_flip(ylim = c(0, 1)) +
       ggplot2::scale_fill_manual(
-        "Risk of Bias",
+
         values = c(
           "m" = concerns_colour,
           "s" = high_colour,
@@ -351,10 +350,10 @@ if (tool == "ROB2") {
           "c" = critical_colour
         ),
         labels = c(
-          "  Critical risk  ",
-          "  Serious risk  ",
-          "  Moderate risk ",
-          "  Low risk  "
+          " Critical risk  ",
+          " Serious risk  ",
+          " Moderate risk ",
+          " Low risk  "
         )
       ) +
       ggplot2::scale_y_continuous(labels = scales::percent) +
@@ -368,14 +367,13 @@ if (tool == "ROB2") {
           size = 0.5,
           linetype = "solid"
         ),
-        legend.position = "bottom",
         panel.grid.major = ggplot2::element_blank(),
         panel.grid.minor = ggplot2::element_blank(),
[…]

### 2019-08-14 R/rob_summary_tools.R
Added ROBINS-I Online to tool specification function

@@ -7,4 +7,5 @@ rob_tools <- function(){
   print("ROBINS-I")
   print("QUADAS-2")
   print("ROB1")
+  print("ROBINS-I Online")
 }

### 2019-08-14 R/rob_traffic_light.R
Fix order of legends
Closes #39

@@ -64,6 +64,11 @@ if (tool == "ROB2") {
 
   rob.tidy$Study <- factor(rob.tidy$Study, levels = unique(data.tmp$Study))
 
+  rob.tidy$judgement <- as.factor(rob.tidy$judgement)
+
+  rob.tidy$judgement <- factor(rob.tidy$judgement,
+                               levels(rob.tidy$judgement)[c(1,3,2)])
+
   if(length(unique(rob.tidy$judgement))==1){adjust_caption <- -1.3}
   if(length(unique(rob.tidy$judgement))==2){adjust_caption <- -1.9}
   if(length(unique(rob.tidy$judgement))==3){adjust_caption <- -2.5}
@@ -96,8 +101,8 @@ trafficlightplot <-  ggplot2::ggplot(rob.tidy, ggplot2::aes(x=1, y=1, colour = j
                 ") +
   ggplot2::scale_x_discrete(position = "top", name = "Risk of bias domains") +
   ggplot2::scale_y_continuous(limits = c(1, 1), labels = NULL, breaks = NULL, name = "Study", position = "left") +
-  ggplot2::scale_colour_manual(values =c(high_colour,low_colour,concerns_colour), labels = c("High","Low","Some concerns")) +
-  ggplot2::scale_shape_manual(values = c(45,43,63), labels = c("High","Low","Some concerns")) +
+  ggplot2::scale_colour_manual(values =c(high_colour,concerns_colour,low_colour), labels = c("High","Some concerns","Low")) +
+  ggplot2::scale_shape_manual(values = c(45,63,43), labels = c("High","Some concerns","Low")) +
   ggplot2::scale_size(range = c(5,20)) +
   ggplot2::theme_bw() +
   ggplot2::theme(panel.border = ggplot2::element_rect(colour = "grey"),
@@ -397,6 +402,11 @@ if (tool == "QUADAS-2") {
 
   rob.tidy$Study <- factor(rob.tidy$Study, levels = unique(data.tmp$Study))
 
+  rob.tidy$judgement <- as.factor(rob.tidy$judgement)
+
+  rob.tidy$judgement <- factor(rob.tidy$judgement,
+                               levels(rob.tidy$judgement)[c(1,3,2)])
+
   if(length(unique(rob.tidy$judgement))==1){adjust_caption <- -1.3}
   if(length(unique(rob.tidy$judgement))==2){adjust_caption <- -1.9}
   if(length(unique(rob.tidy$judgement))==3){adjust_caption <- -2.5}
[…]

### 2019-08-14 R/rob_traffic_light.R
Update shapes used to denote levels of bias
Closes #30

@@ -102,7 +102,7 @@ trafficlightplot <-  ggplot2::ggplot(rob.tidy, ggplot2::aes(x=1, y=1, colour = j
   ggplot2::scale_x_discrete(position = "top", name = "Risk of bias domains") +
   ggplot2::scale_y_continuous(limits = c(1, 1), labels = NULL, breaks = NULL, name = "Study", position = "left") +
   ggplot2::scale_colour_manual(values =c(high_colour,concerns_colour,low_colour), labels = c("High","Some concerns","Low")) +
-  ggplot2::scale_shape_manual(values = c(45,63,43), labels = c("High","Some concerns","Low")) +
+  ggplot2::scale_shape_manual(values = c(120,45,43), labels = c("High","Some concerns","Low")) +
   ggplot2::scale_size(range = c(5,20)) +
   ggplot2::theme_bw() +
   ggplot2::theme(panel.border = ggplot2::element_rect(colour = "grey"),
@@ -220,7 +220,7 @@ if (tool == "ROBINS-I") {
     ggplot2::scale_x_discrete(position = "top", name = "Risk of bias domains") +
     ggplot2::scale_y_continuous(limits = c(1, 1), labels = NULL, breaks = NULL, name = "Study", position = "left") +
     ggplot2::scale_colour_manual(values =c(critical_colour,high_colour,concerns_colour,low_colour), labels = c("Critical","Serious", "Moderate","Low" )) +
-    ggplot2::scale_shape_manual(values = c(33,45,63,43), labels = c("Critical", "Serious","Moderate", "Low")) +
+    ggplot2::scale_shape_manual(values = c(33,120,45,43), labels = c("Critical", "Serious","Moderate", "Low")) +
     ggplot2::scale_size(range = c(5,20)) +
     ggplot2::theme_bw() +
     ggplot2::theme(panel.border = ggplot2::element_rect(colour = "grey"),
@@ -339,7 +339,7 @@ if (tool == "ROBINS-I Online") {
     ggplot2::scale_x_discrete(position = "top", name = "Risk of bias domains") +
     ggplot2::scale_y_continuous(limits = c(1, 1), labels = NULL, breaks = NULL, name = "Study", position = "left") +
     ggplot2::scale_colour_manual(values =c(critical_colour,high_colour,concerns_colour,low_colour), labels = c("Critical","Serious", "Moderate","Low" )) +
[…]

### 2019-08-14 R/rob_traffic_light.R
Improved processing of input table for ROB1
Closes #20 - decided to limit it to ROB1 as users should use correct judgements based on the tool of choice.

@@ -469,16 +469,20 @@ if (tool == "ROB1") {
     low_colour <- colour[c(1)]
     concerns_colour <- colour[c(2)]
     high_colour <- colour[c(3)]
-  } else {
+    critical_colour <- colour[c(4)]
+  }
+  else {
     if (colour == "colourblind") {
-      low_colour <- "#fee8c8"
-      concerns_colour <- "#fdbb84"
-      high_colour <- "#e34a33"
+      low_colour <- "#fef0d9"
+      concerns_colour <- "#fdcc8a"
+      high_colour <- "#fc8d59"
+      critical_colour <- "#d7301f"
     }
     if (colour == "cochrane") {
       low_colour <- "#02C100"
       concerns_colour <- "#E2DF07"
       high_colour <- "#BF0000"
+      critical_colour <- "#820000"
     }
   }
 
@@ -491,6 +495,7 @@ if (tool == "ROB1") {
       data[[i]] <- trimws(data[[i]])
       data[[i]] <- substr(data[[i]], 0, 1)
       data[[i]] <- gsub("u","s",data[[i]])
+      data[[i]] <- gsub("m","s",data[[i]])
     }
 
     #Select relevant columns, excluding the "Weights" column
@@ -501,6 +506,7 @@ if (tool == "ROB1") {
     data[[i]] <- trimws(data[[i]])
     data[[i]] <- substr(data[[i]], 0, 1)
     data[[i]] <- gsub("u","s",data[[i]])
+    data[[i]] <- gsub("m","s",data[[i]])
   }}
 
   #Remove dots from column names
@@ -537,10 +543,12 @@ if (tool == "ROB1") {
 
   rob.tidy$domain <- factor(rob.tidy$domain, levels = levels(rob.tidy$domain))
 
+  rob.tidy$Study <- factor(rob.tidy$Study, levels = unique(data.tmp$Study))
+
   rob.tidy$judgement <- as.factor(rob.tidy$judgement)
 
   rob.tidy$judgement <- factor(rob.tidy$judgement,
-                               levels(rob.tidy$judgement)[c(1,4,3,2)])
+                               levels(rob.tidy$judgement)[c(2,3,4,1)])
 
   if(length(unique(rob.tidy$judgement))==1){adjust_caption <- -1.3}
   if(length(unique(rob.tidy$judgement))==2){adjust_caption <- -1.9}
@@ -566,8 +574,8 @@ if (tool == "ROB1") {
     ggplot2::labs(caption = caption) +
[…]

### 2019-08-14 README.Rmd

@@
 [![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/mcguinlu/robvis?branch=master&svg=true)](https://ci.appveyor.com/project/mcguinlu/robvis)
+[![Codecov test coverage](https://codecov.io/gh/mcguinlu/robvis/branch/master/graph/badge.svg)](https://codecov.io/gh/mcguinlu/robvis?branch=master)
 [![metaverse Identifier](https://img.shields.io/static/v1.svg?label=Part%20of%20the&message=metaverse&color=informational)](https://www.github.com/rmetaverse/metaverse)

### 2019-09-25 R/rob_paired_plot.R
Initial commits (BROKEN)

@@ -1,0 +1,42 @@
+#' Produce forest plots with risk of bias results
+#' @description A function to take a summary table of risk of bias assessments and produce a traffic light plot from it.
+#' @param data A dataframe containing summary (domain) level risk-of-bias assessments, with the first column containing the study details, the second column containing the first domain of your assessments, and the final column containing a weight to assign to each study. The function assumes that the data includes a column for overall risk-of-bias. For example, a ROB2.0 dataset would have 8 columns (1 for study details, 5 for domain level judgements, 1 for overall judgements, and 1 for weights, in that order).
+#' @export
+
+
+rob_paired_plot <- function(data, tool, colour = "cochrane",
+                              psize = 20, quiet = FALSE) {
+
+  judgement <- NULL
+  Study <- NULL
+  domain <- NULL
+
+
+  # Define colouring
+  if (length(colour) > 1) {
+    low_colour <- colour[c(1)]
+    concerns_colour <- colour[c(2)]
+    high_colour <- colour[c(3)]
+    critical_colour <- colour[c(4)]
+  } else {
+    if (colour == "colourblind") {
+      low_colour <- "#fef0d9"
+      concerns_colour <- "#fdcc8a"
+      high_colour <- "#fc8d59"
+      critical_colour <- "#d7301f"
+    }
+    if (colour == "cochrane") {
+      low_colour <- "#02C100"
+      concerns_colour <- "#E2DF07"
+      high_colour <- "#BF0000"
+      critical_colour <- "#820000"
+    }
+  }
+
+
+  myCsv <- getURL("https://docs.google.com/spreadsheet/pub?key=0AvykV4O1IaendFRSQVVVV3pYN3JZRlNKSzBud0FFa1E&output=csv")
+
+
+
+
+}

### 2019-09-27 R/rob_traffic_light.R
Fix the ROBINS-I Online template

@@ -304,7 +304,7 @@ rob_traffic_light <- function(data, tool, colour = "cochrane",
         }
 
         data <- data[, grepl("studyId|RBJ_answer", names(data))]
-        data <- data[, which(is.na(data) == FALSE)]
+        data <- data[, colSums(is.na(data)) != nrow(data)]
 
         for (i in 2:9) {
             data[[i]] <- tolower(data[[i]])
@@ -338,8 +338,7 @@ rob_traffic_light <- function(data, tool, colour = "cochrane",
 
         rob.tidy$judgement <- as.factor(rob.tidy$judgement)
 
-        rob.tidy$judgement <- factor(rob.tidy$judgement, levels(rob.tidy$judgement)[c(1,
-            4, 3, 2)])
+        rob.tidy$judgement <- factor(rob.tidy$judgement, levels(rob.tidy$judgement)[c(1, 4, 3, 2)])
 
         if (length(unique(rob.tidy$judgement)) == 1) {
             adjust_caption <- -1.3

### 2019-10-24 README.Rmd
Fix typos

@@
 ## Getting started
-### Install the `robvis` pacakage
 First ensure you have the `devtools` package installed:
@@
 #### 2. rob_traffic_light()
-Returns a ggplot object displaying a ["traffic light plot"](https://handbook-5-1.cochrane.org/chapter_8/figure_8_6_c_example_of_a_risk_of_bias_summary_figure.htm), displaying the risk of bias judgement in each domain for each study.
+Returns a ggplot object displaying a ["traffic light plot"](https://handbook-5-1.cochrane.org/chapter_8/figure_8_6_c_example_of_a_risk_of_bias_summary_figure.htm), displaying the risk of bias judgment in each domain for each study.
 
@@
 Outputs a list of the risk of bias assessment tools for which a template currently exists in rob_summary().
-We expect this list to be updated in the near future to inlcude tools such as ROBIS (tool for assessing risk of bias in systematic reviews).
+We expect this list to be updated in the near future to include tools such as ROBIS (tool for assessing risk of bias in systematic reviews).
 
@@
 ### Change the colour scheme
-The `colour` argument of both plotting functions allows users to select from two predefined colour schemes ("cochrane" or "colourblind") or to define their own pallete by providing a vector of hex codes.
+The `colour` argument of both plotting functions allows users to select from two predefined colour schemes ("cochrane" or "colourblind") or to define their own palette by providing a vector of hex codes.
 
@@
 
+## Code of conduct
+
+Please note that the 'robvis' project is released with a
+[Contributor Code of Conduct](CODE_OF_CONDUCT.md).
+By contributing to this project, you agree to abide by its terms.
+
 ## License
@@
 * The `rob_summary()` function was based on code forwarded by a colleague.
-I have recently learnt that this code was adapted from that presented in the wonderful "[Doing Meta-Analysis in R](https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/plotting-the-summary.html)" guide, so I would like to acknowledge the authors here.
+I recently discovered that this code was adapted from that presented in the wonderful "[Doing Meta-Analysis in R](https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/plotting-the-summary.html)" guide, so I would like to acknowledge the authors here.
 * [Emily Kothe](https://github.com/ekothe) for help in fixing `ggplot2` coding issues.

### 2019-10-24 R/rob_summary.R

@@ -1,6 +1,6 @@
 #' Produce summary weighted barplots of risk-of-bias assessments.
 #' @description A function to convert standard risk-of-bias output to tidy data and plot a summary barplot.
-#' @param data A dataframe containing summary (domain) level risk-of-bias assessments, with the first column containing the study details, the second column containing the first domain of your assessments, and the final column containing a weight to assign to each study. The function assumes that the data includes a column for overall risk-of-bias. For example, a ROB2.0 dataset would have 8 columns (1 for study details, 5 for domain level judgements, 1 for overall judgements, and 1 for weights, in that order).
+#' @param data A dataframe containing summary (domain) level risk-of-bias assessments, with the first column containing the study details, the second column containing the first domain of your assessments, and the final column containing a weight to assign to each study. The function assumes that the data includes a column for overall risk-of-bias. For example, a ROB2.0 dataset would have 8 columns (1 for study details, 5 for domain level judgments, 1 for overall judgements, and 1 for weights, in that order).
 #' @param tool The risk of bias assessment tool used. RoB2.0 (tool='ROB2'), ROBINS-I (tool='ROBINS-I'), and QUADAS-2 (tool='QUADAS-2') are currently supported.
 #' @param overall An option to include a bar for overall risk-of-bias in the figure. Default is FALSE.
 #' @param quiet An option to quietly produce the plot without displaying it.
@@ -9,503 +9,678 @@
 #' @return Risk of bias assessment barplot figure.
 #' @export
 
-rob_summary <- function(data, tool, overall = FALSE, weighted = TRUE,
-    colour = "cochrane", quiet = FALSE) {
-
+rob_summary <-
+  function(data,
+           tool,
+           overall = FALSE,
+           weighted = TRUE,
+           colour = "cochrane",
+           quiet = FALSE) {
     judgement <- NULL
     Weights <- NULL
     domain <- NULL
 
-# ROB-2=========================================================================
+    # ROB-2=========================================================================
 
     if (tool == "ROB2") {
-
-        # Define colouring
-        if (length(colour) > 1) {
-            low_colour <- colour[c(1)]
-            concerns_colour <- colour[c(2)]
-            high_colour <- colour[c(3)]
[…]

### 2019-10-24 R/rob_traffic_light.R

@@ -1,9 +1,9 @@
 #' Produce traffic-light plots of risk-of-bias assessments.
 #' @description A function to take a summary table of risk of bias assessments and produce a traffic light plot from it.
-#' @param data A dataframe containing summary (domain) level risk-of-bias assessments, with the first column containing the study details, the second column containing the first domain of your assessments, and the final column containing a weight to assign to each study. The function assumes that the data includes a column for overall risk-of-bias. For example, a ROB2.0 dataset would have 8 columns (1 for study details, 5 for domain level judgements, 1 for overall judgements, and 1 for weights, in that order).
+#' @param data A dataframe containing summary (domain) level risk-of-bias assessments, with the first column containing the study details, the second column containing the first domain of your assessments, and the final column containing a weight to assign to each study. The function assumes that the data includes a column for overall risk-of-bias. For example, a ROB2.0 dataset would have 8 columns (1 for study details, 5 for domain level judgments, 1 for overall judgements, and 1 for weights, in that order).
 #' @param tool The risk of bias assessment tool used. RoB2.0 (tool='ROB2'), ROBINS-I (tool='ROBINS-I'), and QUADAS-2 (tool='QUADAS-2') are currently supported.
 #' @param colour An argument to specify the colour scheme for the plot. Default is 'cochrane' which used the ubiquitous Cochrane colours, while a preset option for a colour-blind friendly palette is also available (colour = 'colourblind').
-#' @param psize Controll the size of the traffic lights
+#' @param psize Control the size of the traffic lights. Default is 20.
 #' @param quiet An option to quietly produce the plot without displaying it.
 #' @return Risk-of-bias assessment traffic light plot (ggplot2 object)
 #' @export

### 2019-10-24 README.Rmd
Fix broken links indicated by CRAN checks

@@
 Please note that the 'robvis' project is released with a
-[Contributor Code of Conduct](CODE_OF_CONDUCT.md).
+[Contributor Code of Conduct](https://github.com/mcguinlu/robvis/blob/master/CODE_OF_CONDUCT.md).
 By contributing to this project, you agree to abide by its terms.
@@
 
-This project is licensed under the MIT License - see the [LICENSE.md](https://github.com/mcguinlu/robvis/blob/traffic_light_plot/LICENSE) file for details.
+This project is licensed under the MIT License - see the [LICENSE.md](https://github.com/mcguinlu/robvis/blob/master/LICENSE) file for details.
 

### 2019-11-25 README.Rmd

@@
 [![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)
+[![CRAN Badge.](https://www.r-pkg.org/badges/version/robvis)](https://cran.r-project.org/web/packages/robvis/index.html)
+[![CRAN Downloads.](https://cranlogs.r-pkg.org/badges/last-month/robvis)](https://cran.r-project.org/web/packages/robvis/index.html)
+<br>
 [![Build Status](https://img.shields.io/travis/mcguinlu/robvis.svg?label=build&logo=travis&branch=master)](https://travis-ci.org/mcguinlu/robvis) 
@@
 [![Codecov test coverage](https://codecov.io/gh/mcguinlu/robvis/branch/master/graph/badge.svg)](https://codecov.io/gh/mcguinlu/robvis?branch=master)
+<br>
 [![metaverse Identifier](https://img.shields.io/static/v1.svg?label=Part%20of%20the&message=metaverse&color=informational)](https://www.github.com/rmetaverse/metaverse)
@@
 ```
-The `robvis` package takes the summary table from risk-of-bias assessments, converts it to tidy data, and produces summary plots formatted according to the assessment tool used.
+The `robvis` package takes the summary table from risk-of-bias assessments and produces plots formatted according to the assessment tool used.
 
 ## Getting started
-First ensure you have the `devtools` package installed:
+
+Install the CRAN version:
+```{r, eval=FALSE}
+install.packages("robvis")
+```
+
+Alternatively, the development version can be installed using:
 
@@
 install.packages("devtools")
-library(devtools)
-```
-
-Then, to install:
-```{r, eval=FALSE}   
-install_github("mcguinlu/robvis")
-library(robvis)
+devtools::install_github("mcguinlu/robvis")
 ```

### 2020-01-11 README.Rmd
Add published examples of robvis

@@
 
+## Examples of `robvis` in published papers
+
+* Habadi, Mohammed Ibrahim, et al.
+"[Prevalence of Panic Disorders in the Primary Health Care Setting: A Systematic Review and Meta-Analysis.](https://www.ecronicon.com/ecmi/pdf/prevalence-of-panic-disorders-in-the-primary-health-care-setting-a-systematic-review-and-meta-analysis.pdf)" EC Microbiology 16.1 (2019): 01-09.
+* Gibb, Kate, et al.
+"[The consistent burden in published estimates of delirium occurrence in medical inpatients over four decades: a systematic review and meta-analysis study.](https://www.medrxiv.org/content/medrxiv/early/2019/08/29/19005165.full.pdf)" medRxiv (2019): 19005165.
+
 ## Code of conduct

### 2020-01-17 JOSS-paper/paper.Rmd
Add scaffold of two maunscripts

---
title: "paper"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2020-01-17 RSM-paper/manuscript.Rmd
Add scaffold of two maunscripts

---
title: "RSM-paper"
bibliography: references.bib
csl: nature.csl
output:
  bookdown::word_document2:
      toc: false
      toc_depth: 3
      reference_docx: word-styles-reference-01.docx
  bookdown::pdf_document2:
  bookdown::html_document2:
      toc: true
      toc_depth: 2
---

## Type

Either of:

__Brief Method Notes__ describe or critique a particular method, procedure, or graphic display. A Brief Method Note should focus on what is innovative or useful, or problematic about the method. The method or procedure should be presented clearly and with sufficient detail. Brief Method Notes are limited to 1,500 words (excluding References).

__Computational Tools and Methods__ describe software tools and computational methods for facilitating evidence synthesis. These types of articles are expected to at least in part describe accompanying software (e.g., an R package or a web-based tool). Typically, these are written upon invitation from the Computational Tools and Methods feature Editor . However, suggestions are always welcome and should be sent directly to the Software Review Editor . Computational Tools and Methods articles are expected to be relatively brief, but we do not impose a formal limit.

## Authors

## Funding

Acknowledge the Bristol Alumni Foundation, the Evidence Synthesis Hackathon and the NIHR.

## Introduction

No other visualisation software exists explicitly for the purpose of visualising risk of bias assessments

## Development

Time

ESH

Community involvement

## R package

## Shiny web-app

## Example: choose review and apply

## Discussion

Anyone can design.

`robvis` forms one part of the `metaverse`, a collection of tools written using R that cover. A key example is `revtools`, original published in this journal

## Back matter

### Acknowledgements

### Supporting information

All code for this project is freely available at www.github.com/mcguinlu/robvis

### Figures

### 2020-01-27 RSM-paper/manuscript.Rmd
Added major updates to the RSM paper

@@
 
-## Type
+``` {r, echo = FALSE}
+library(robvis)
 
-Either of:
+knitr::opts_chunk$set(eval=FALSE)
 
-__Brief Method Notes__ describe or critique a particular method, procedure, or graphic display.
-A Brief Method Note should focus on what is innovative or useful, or problematic about the method.
-The method or procedure should be presented clearly and with sufficient detail.
-Brief Method Notes are limited to 1,500 words (excluding References).
+```
 
-__Computational Tools and Methods__ describe software tools and computational methods for facilitating evidence synthesis.
-These types of articles are expected to at least in part describe accompanying software (e.g., an R package or a web-based tool).
-Typically, these are written upon invitation from the Computational Tools and Methods feature Editor .
-However, suggestions are always welcome and should be sent directly to the Software Review Editor .
-Computational Tools and Methods articles are expected to be relatively brief, but we do not impose a formal limit.
+# Front Matter
+__Title: __  
+Developing visualization tools with R and Shiny: a case study of the new Risk of Bias visualization tool.
 
-## Authors
+&nbsp;
 
-## Funding
+__Authors and Affliations__
 
-Acknowledge the Bristol Alumni Foundation, the Evidence Synthesis Hackathon and the NIHR.
+Luke A McGuinness^1,2^ (ORCID: 0000-0001-8730-9761), 
+Julian PT Higgins^1,2^ (ORCID: 0000-0002-8323-2514)
 
-## Introduction
+(1) MRC University of Bristol Integrative Epidemiology Unit, Bristol, UK
+(2) Bristol Medical School: Population Health Sciences, University of Bristol, Bristol, UK
 
-No other visualisation software exists explicitly for the purpose of visualising risk of bias assessments
+&nbsp;
 
-## Development
+__Corresponding author:__
 
-Time
+Luke McGuinness; Bristol Medical School, University of Bristol,
+Canynge Hall, 39 Whatley Road, Bristol, BS8 2PS, United Kingdom.; luke.mcguinness@bristol.ac.uk
 
-ESH
+&nbsp;
 
-Community involvement
+__Article type__
 
+_Computational Tools and Methods_
+
+&nbsp;
+
+__Funding__
+LAM is supported by an NIHR Doctoral Research Fellowship (DRF-2018-11-ST2-048).
+Attendence at the Evidence Synthesis Hackathon in April 2019 was supported by a grant from the Evidence Synthesis Hackathon itself and the University of Bristol Alumni Foundation.
+
+#####
+
+# Abstract
+At present there is is no open source tool to
+
+Here I present robvis, an R package and Shiny web app that showcase how R can be used to build open source tools for R users and non-users alike. It provides two main functions to
+
+The entire offering is open source, and has benefitted from this fact through several community suggested improvements.
+
+#####
+
+# Highlights
+- No other open-source visualisation tool exists explicitly for the purpose of visualising risk of bias results
+- Here we present `robvis`, an R package and Shiny web app for visualising risk of bias assessment results
+- `robvis` allows users to procude publication quality graphics which confrom to the 
+- `robvis` is completely open-source, and has benefitted from community suggested features.
+- `robvis` forms part of the `metaverse`, a collection of R packages designed to provide an evidence synthesis workflow in R.
+
+#####
+
+# Introduction
+Evidence synthesis as a field has recently experience a substantial growth in software offerings
+
+Risk of bias assessment - assessment of the internal validity of studies included in a systematic review - forms a key part of the evidence synthesis process, particularly in the health sciences.
+There are several tools that are routinely used to produce risk of bias assessments, depending on the type of study under consideration.
+Similarly, there are two recommended formats for presenting graphically the results of the risk of bias assessments.
+While software does exist to create these graphs, they are exclusively commercial offerings.
+`robvis`, a package written in and for the R computing environment, seeks to solve this issue.
+
+`robvis` also originated as part of the `metaverse` a collection of packages for R which seeks to provide an opinionated workflow for performing evidence synthesis.
+
+Tools such as R and Shiny (an R package for building interactive web apps) have made it easier than ever to produce tools to visualize the complex data produced as part of a research synthesis project.
+
+We will present a recently developed tool, robvis (Risk Of Bias VISualization), which allows users to rapidly produce publication quality figures to explore the risk-of-bias assessments that routinely take place as part of systematic review (Supporting Figures 1 & 2).
+We will present a timeline of the tool’s development, its key functionality, its advantages over commercially available software, and the main challenges we encountered in creating it.
+
+Users can download the stable version of `robvis` from CRAN (https://cran.r-project.org/package=robvis); or contribute to the development version on GitHub (https://github.com/mcguinlu/robvis).
+Extended guidance for the tool is also available in the "Doing Meta-Analysis in R" online guide.[@mathias_harrer_2019_2551803].
+
+While created originally for use the major risk of bias assessment tools used in healthcare/epidemiology, a general template within the tool allows users to visualise the results produced by other domain-based risk of bias/quality appraisal tools.
+
+Creating the figure by hand may lead to unintentional errors. IN an age where reproducibility and replicability are crucial to the confidence of
+
+So in an effort to
+
+In the healthcare field, the move from point-based scoring systems and checklists to domain-based assessments of the internal validity of the study has produced a range of domain-based tools.
+[@sterne2016robins; @sterne2019rob; @whiting2011quadas; @whiting2016robis] Many of these are recommneded by the Cochrane Collaboration, the
+
+# Development
+Time/ESH/Community involvement
+
+Development of `robvis` began in April 2019 at the Evidence Synthesis Hackathon in April 2019, with the first completed version fo the software uploaded to CRAN in November 2019.
+
+# Functionality
 ## R package
+``` {r}
 
-## Shiny web-app
+# Stable version
+install.packages(robvis)
 
-## Example: choose review and apply
+# Development version
+install.packages("devtools")
+devtools::install_github("mcguinlu/robvis")
 
-## Discussion
+# Load the package
+library(robvis)
 
-Anyone can design.
+```
 
-`robvis` forms one part of the `metaverse`, a collection of tools written using R that cover. A key example is `revtools`, original published in this journal
+### Data import and cleaning
 
-## Back matter
+`robvis` expects data in a specific format, namely:
 
-### Acknowledgements
+1. The first column 
+2. The second-to-last column
+3. The final column contains the weights
+4. The first row of data does not contain column headings. This can be achieved using the `header = TRUE` argument in the code block above
 
-### Supporting information
+```{r}
 
-All code for this project is freely available at www.github.com/mcguinlu/robvis
+data_rob <- read.csv("path/to/riskofbiasdata.csv", 
+                      header = TRUE)
 
-### Figures
+```
+
+### Templates and example data sets
+
+The tool contains figure templates, created via `ggplot2`(@ggplot2ref) which the uploaded data are used to customize.
+
+Templates for three major tools: the Cochrane RoB2 tool for assessing randomised controlled trials, the ROBINS-I tool for assessing non-randomized studies of interventions, and the QUADAS-2 tool for assessing diagnostic accuracy studies.
+
+The templates automatically apply the correct risk of bias domain names to the figure, and label the judgement levels appropriately.
+
+However,
+
+While developed primarily for use with the tools routinely used in the healthcare field, `robvis` also contains a general template that can be used to visualise the result of any domain-based assesssment tool.
+This template has far more flexibility, allowing a variable number of domains a.
+However, we would encourage authors to not interpret this as a licence to create visualisations of
+
+`robvis` contains an example dataset for each template, and for illustrative purposes, the example data for the RoB2 tool for assessing risk of bias in randomised controlled trials is presented in Table \@ref(tab:robdata)
+
+### Functions
+
+The central functions of `robvis` are `rob_summary()`, which creates a weighted barplot showing the proportion of information at a certain level of risk of bias within each domain of the assessment tool specified, and `rob_traffic_light()`, which
+
+A worked example using these functions is outlined below, showing the ease with which risk of bias plots can be created using `robvis`.
+
+First, install and load the package:
+
+```{r}
+
+install.packages("robvis")
+
+library(robvis)
+
+```
+
+Using the example data set (`data_rob2`) presented in Table \@ref(tab:robdata), the summary barplot shown in Figure \@ref(fig:summaryplot) is created using the following code:
+
+```{r}
+
+rob_summary(data = data_rob2,
+            tool = "ROB2", 
+            overall = TRUE)
+
+```
+
+Similary, using the same data set, the traffic light plot shown in Figure \@ref(fig:trafficplot) is created using:
+
+``` {r}
+
+rob_traffic_light(data = data_rob2,
+                  tool = "ROB2",
+                  colour = "colourblind", 
+                  psize = 15)
+
+```
+
+### Other comments
+
+The tool can deals with small misspellings in terms of judgements (e.g., it can recognise “_Seroius_”), and has the capacity to deal with "No Information" judgements (See Figure \@ref(fig:summaryplot)).
+
+Both graphing functions return a `ggplot` object, meaning the can be easily customised further using the `ggplot2` framework. For example, to add a title to the plot:
+
+``` {r}
+library(ggplot2)
+
+plot <- rob_summary(data_rob2, tool = "ROB2")
+
+plot +
+ggtitle("Summary Bar Plot")
+
+```
+
+A full discussion of the range of post-production modifcations that can be made to the plots via the `ggplot2` package is beyond the scope of this article, though interested readers are directed towards.
+
+## Shiny web app
+
+Although `robvis` was originally designed for use in the command-line–based R programming environment, in order to make the tool available to those without knowledge of the R  environment, `robvis` also exists as a web-app.[@robviswebapp]
+
+The app was built using `Shiny`,[@shinyref] a R package which makes it easy to produce interactive web-apps.
+The app provides users with a Graphical User Interface, allowing users to interact with the functions presented above without the need to download R or type any commands.
+Users can upload their data, choose the tool they used to perform the assessments, select a colour scheme, and define other parameters depending on whether they are producing a traffic light or summary bar plot.
+
+A singular advantage of using `robvis` via the webapp is that images download from the app will be auto-sized for best results. This is intentional, as
+
+and to readily specify a range of download formats (PNG, JPEG, TIFF, & EPS).
+
+# Discussion
+
+__Recap of functionality__
+
+It has been well received by the community, and has already been cited in the published literature [@veloso2020effectiveness; @habadi2019prevalence; @gibb2019consistent].
+
+__Limitations__
+At present, the number of tools with a specific template included in `robvis` is low, 
+Additionally, the tool does not yet allow for the production of paried forest plots, where the risk of bias judgement for each specific result included in the meta-analysis.
+This was initally considered to be beyond the scope of the tool, as it ivolves the visulaisation of something other than risk of bias assessments.
+However, following user-driven demand, this functionality is in development and will be available in the near future.
+
+__Place in the ES ecosystem__
+
+`robvis` was originally designed to fill a specific gap in the evidence synthesis software.
+At the same meeting that robvis was conceived, the `metaverse` project was also born.
+It plans to curate  a collection of tools written using R that cover different aspects of the systematic review and meta-analysis process, and when taken together, form a cohert end-to-end open source alternative to commerical offerings such as Covidence.
+A key example is `revtools`, original published in this journal, litsearcher and metafor.
+The too
+
+__Role of open-source software__
+
+Anyone can design
+
+With reference to robvis, we will explore the benefits that creating visualization tools for complex data visualization can have, both to the individual researcher in terms of career progression and increased competitiveness when applying for funding, and to the field of research synthesis as a whole.
+We will also highlight the advantages of maintaining these visualization tools as open-source projects, with specific reference to new robvis functionality that was added as a result of community involvement (e.g.
+the addition of a colour-blind scheme; see Supporting Figure 2 for an example).
+
+Overall, with reference to robvis, we will argue that if a research synthesist has created a R script to visualize complex data, the tools and resources now exist to package their code in a readily shareable format and to provide a user-friendly graphical interface for it within a very short timeframe.
+
+In broader terms, `robvis` forms part of the metaverse, a collection of R packages that seek to make it easier to produce r
+
+R and the collection of packages it is comprised of, currently represents an untapped source of. This is particularly true of offering such as RMarkdown
+
+#####
+
+# Back Matter
+## Acknowledgments
+The following people provided valuable feedback that contributed to the development of the `robvis` tool: Emily Kothe,  Eliza Grames, Matthew Page, Alexandra Bannach-Brown, Kyle Hamilton, Charles Gray, Vincent Cheng, Wouter van Amsterdamn, Neal Haddaway and Martin Westgate.
+
+## Code/Data availability statement
+The software and data presented in this paper are freely available on GitHub: https://github.com/mcguinlu/robvis
+
+#####
+
+## Tables/Figures
+
+```{r robdata, echo = FALSE, eval = TRUE}
+
+plotdata <- data_rob2
+
+knitr::kable(plotdata, caption = "Example dataset for the ROB2 tool contained within `robvis`")
+
+```
+
+#####
+
+``` {r robarguments, echo = FALSE, eval = TRUE}
+
+arguments <- data.frame(stringsAsFactors=FALSE,
+              argument = c("data", "tool", "colour", "overall", "weighted",
+                           "psize"),
+           rob_summary = c("X", "X", "X", "X", "X", ""),
+     rob_traffic_light = c("X", "X", "X", "", "", "X"),
+           Description = c("Defines the dataframe containing the summary (domain) level risk-of-bias assessments.
+See the text and Table 1 for the format expected by `robvis`", "Defines the risk of bias assessment tool used.
+The RoB2 (`tool='ROB2'`), ROBINS-I (`tool='ROBINS-I'`), and QUADAS-2 (`tool='QUADAS-2'`) assessments tools are currently supported.
+Other tools can be visualised using the generic template (`tool = 'ROB1'`)", "Defines the colour scheme for the plot.
+The default is `colour` = 'cochrane' which uses the ubiquitous Cochrane colours, while a preset option for a colour-blind friendly palette is also available (`colour = 'colourblind'`).
+Alternatively, users can specify their own colour scheme e.g.
+`colour = c('#f442c8', '#bef441', '#000000')`", "Defines whether to include an additional bar showing the distibution of overall risk of bias judgements in the summary barplot figure.
+Default is `overall = FALSE`.", "Defines whether weights should be used to produce the summary barplot figure.
+Default is `weighted = TRUE`, in line with current Cochrane Collaboration guidance.", "Defines the size of the points in the traffic light plot.
+Default is `psize = 20`."))
+
+knitr::kable(arguments,
+             caption = "Description of the arguments available in the two main `robvis` functions",
+             align = c("l","c","c","l"),
+             col.names = c("Argument","`rob_summary()`","`rob_traffic_light()`", "Description"))
+
+```
+
+#####
+
+``` {r summaryplot, echo = FALSE, eval = TRUE, fig.cap = "Example risk of bias summary plot created using `robvis`"}
+
+ggplot2::ggsave(
+          filename = "figs/robsummplot.png",
+          plot = robvis::rob_summary(plotdata, "ROB2", overall = TRUE) +
+   ggplot2::theme(plot.background = ggplot2::element_rect(colour = "black")),
+          width = 8,
+          height = 2.41,
+          dpi = 1000
+          )
+
+knitr::include_graphics("figs/robsummplot.png")
+
+```
+
+######
+
+``` {r trafficplot, echo = FALSE, eval = TRUE, fig.cap = "Example risk of bias traffic light plot created using `robvis`"}
+
+ggplot2::ggsave(
+          filename = "figs/robtfplot.png",
+          plot = robvis::rob_traffic_light(data = plotdata, "ROB2", psize = 15, colour = "colourblind"),
+          width = 7,
+          height = 8,
+          dpi = 1000
+          )
+
+knitr::include_graphics("figs/robtfplot.png")
+```
+
+#####
+
+# Bibliography

### 2020-01-30 RSM-paper/manuscript.Rmd
Updates to RSM Paper

--- 2020-01-17 RSM-paper/manuscript.Rmd
@@
 
-## Type
+``` {r, echo = FALSE}
+library(robvis)
 
-Either of:
+knitr::opts_chunk$set(eval=FALSE)
 
-__Brief Method Notes__ describe or critique a particular method, procedure, or graphic display.
-A Brief Method Note should focus on what is innovative or useful, or problematic about the method.
-The method or procedure should be presented clearly and with sufficient detail.
-Brief Method Notes are limited to 1,500 words (excluding References).
+```
 
-__Computational Tools and Methods__ describe software tools and computational methods for facilitating evidence synthesis.
-These types of articles are expected to at least in part describe accompanying software (e.g., an R package or a web-based tool).
-Typically, these are written upon invitation from the Computational Tools and Methods feature Editor .
-However, suggestions are always welcome and should be sent directly to the Software Review Editor .
-Computational Tools and Methods articles are expected to be relatively brief, but we do not impose a formal limit.
+# Front Matter
+__Title: __  
+Developing visualization tools with R and Shiny: a case study of the new Risk of Bias visualization tool.
 
-## Authors
+&nbsp;
 
-## Funding
+__Authors and Affliations__
 
-Acknowledge the Bristol Alumni Foundation, the Evidence Synthesis Hackathon and the NIHR.
+Luke A McGuinness^1,2^ (ORCID: 0000-0001-8730-9761), 
+Julian PT Higgins^1,2^ (ORCID: 0000-0002-8323-2514)
 
-## Introduction
+(1) MRC University of Bristol Integrative Epidemiology Unit, Bristol, UK
+(2) Bristol Medical School: Population Health Sciences, University of Bristol, Bristol, UK
 
-No other visualisation software exists explicitly for the purpose of visualising risk of bias assessments
+&nbsp;
 
-## Development
+__Corresponding author:__
 
-Time
+Luke McGuinness; Bristol Medical School, University of Bristol,
+Canynge Hall, 39 Whatley Road, Bristol, BS8 2PS, United Kingdom.; luke.mcguinness@bristol.ac.uk
 
-ESH
+&nbsp;
 
-Community involvement
+__Article type__
 
+_Computational Tools and Methods_
+
+&nbsp;
+
+__Funding__
+
+LAM is supported by an NIHR Doctoral Research Fellowship (DRF-2018-11-ST2-048).
+Attendence at the Evidence Synthesis Hackathon in April 2019 was supported by a grant from the Evidence Synthesis Hackathon itself and the University of Bristol Alumni Foundation.
+
+#####
+
+# Abstract
+TBC
+
+#####
+
+# Highlights
+- No other open-source visualisation tool exists explicitly for the purpose of visualising risk of bias results
+- Here we present `robvis`, an R package and `Shiny` web app for visualising risk of bias assessment results
+- `robvis` allows users to procude publication quality graphics which confrom to the 
+- `robvis` is completely open-source, and has benefitted from community suggested features.
+- `robvis` forms part of the `metaverse`, a collection of R packages designed to provide an evidence synthesis workflow in R.
+
+#####
+
+# Introduction
+
+__Intro and importance of evidence synthesis__
+
+Evidence synthesis, the act of drawing together all relevant information to inform, is becoming more important than ever in informing policy across an increasingly wide range of fields.[@donnelly2018four] Risk of bias assessment - assessment of the internal validity of studies included in a systematic review - often forms a key part of the evidence synthesis process, particularly in the health sciences.[@higgins2008assessing] There are several well developed tools that are routinely used to produce risk of bias assessments, depending on the type of study under consideration.
+[@sterne2016robins; @sterne2019rob; @whiting2011quadas; @whiting2016robis] (__Worht including non-health citiations here - example welcome!__) Rather than making use of checklists or point-scoring systems, these tools are domain-based, assessing the risk of bias across a number of equally important categories.
+For example, the first domain in the Cochrane ROB2 tool for the assessmnt of randomised controlled trials deals with "Bias arising due to randomisation".[@sterne2019rob] Accessible graphics summarising the results of these domain-based risk-of-bias assessments are frequently produced, the two most common being weighted barplots, which show the proportion of information with each judgement for each domain in the assessment tool specified, and "traffic light" plots, which tabulate each study by each domain and provide a more detailed view of the results of the risk-of-bias assessment.[@higgins2008assessing]
+
+However, researchers often face a number of barriers in creating such plots.
+While some commerical evidence synthesis platforms, such as RevMan,[@cochrane2014review] are able to produce these visualisations, not all researchers use these systems to conduct their systematic reviews, meaning that copying the risk of bias data into these systems simply to produce the plots is inefficient and error prone.
+Likewise, creating the figures by hand, through software such as MS PowerPoint or Adobe Illustrator, may lead to unintentional errors and require the plots to be redrawn during an (increasingly common) update to the review.
+
+A further barrier is that in recent years, the field of evidence synthesis software has grown rapidly,[@marshall2015systematic] but this growth has not been equally distributed across the different aspects of the systematic review process.
+For example, a recent review found several software offerings aimed specifcally at the abstract screening stage of the review process,[@harrison2020software] but no similar time- and error-reducing tool has been proposed for visualising the results of risk-of-bias assessments.
+
+Fortunately, tools such as R, RStudio and `Shiny` (an R package for building interactive web apps) have made it easier than ever to produce such a tool.[@rref;@shinyref;@rstudioref] Here, we present `robvis` (Risk Of Bias VISualiation), an R package and `Shiny` web-app that allows users to quickly create publication-ready risk-of-bias plots.
+While created originally for use with the major risk of bias assessment tools used in epidemiology, the tool allows users to visualise the results from any domain-based risk of bias assessment or quality appraisal tool.
+
+The tool is open-source and available to use free of charge.
+Users can download a stable version of the R package from CRAN (https://cran.r-project.org/package=robvis); or access and contribute to the development version via GitHub (https://github.com/mcguinlu/robvis).
+Extended guidance for the tool is also available via the "Doing Meta-Analysis in R" online guide.[@mathias_harrer_2019_2551803] Below, we discuss the tools development, key functionality, and role in the evidence synthesis in R eco-system.
+
+# Development
+
+Development of `robvis` began in April 2019 at the Evidence Synthesis Hackathon (ESH), an event which brings together interested researchers, practitioners and coders to discuss and develop new open-source evidence synthesis technologies.
+Testing versions of both the R package and the web app were made available in early June 2019, with attendees of the ESH and members of the evidence synthesis research group at the University of Bristol being invited to test the tool and provide feedback.
+This feedback, along with other feature suggestions from the wider evidence synthesis community captured via GitHub issues, was incorporated and the first release version of the package was uploaded to CRAN in November 2019.
+To date, the tool has been well received and is beginning to be cited in the evidence synthesis literature.[@veloso2020effectiveness; @habadi2019prevalence; @gibb2019consistent].
+
+# Functionality
 ## R package
+### Tool templates and example data sets
 
-## Shiny web-app
+The package works by using user-provided data to populate a predefined templates specific to the assessment tool used.
+These templates automatically apply the correct risk of bias domain names to the figure and label the judgement levels appropriately (e.g.
+"Low", "Some Concerns", "High" in the case of the ROB2 tool).
 
-## Example: choose review and apply
+Currently, the tool contains templates for three major tools: the Cochrane RoB2 tool for assessing randomised controlled trials,[@sterne2019rob] the ROBINS-I tool for assessing non-randomized studies of interventions,[@sterne2016robins] and the QUADAS-2 tool for assessing diagnostic accuracy studies.[@whiting2011quadas]
 
-## Discussion
+`robvis` also contains a general template that can be used to visualise the result of any domain-based assesssment tool.
+This template has greater flexibility than the tool-specific templates, allowing a variable number of domains and custom domain titles to be used.
+However, we would dissuade authors from viewing this as a means to create visualisations of assessments performed using adjusted versions of the tools listed above (e.g.
+with one or more columns removed/added).
 
-Anyone can design.
+In order to help users familiarise themselves with the package and its functionality, `robvis` contains built-in example datasets for each template, and for illustrative purposes, the example data for the RoB2 tool for assessing risk of bias in randomised controlled trials is presented in Table \@ref(tab:robdata).
 
-`robvis` forms one part of the `metaverse`, a collection of tools written using R that cover. A key example is `revtools`, original published in this journal
+### Data import and cleaning
 
-## Back matter
+`robvis` expects certain facts about the risk of bias summary table we provide it (see Table \@ref(tab:robdata) for an example of a correctly formatted data set).
+The first column should contain the unique study/result identifier.
+The second-to-last column should contain the overall risk of bias judgements.
+The final column contains the weights (e.g.
+study precision or the weight assigned in a meta-anlysis).
+This weight column is used to create the summary barplot, as current guidance recommends dividing the bars to show the proportion of information at each level of risk of bias, determined by the cumulative weight at that level, rather than simply showing the number of studies in each category.[@cochranechpt7]
 
-### Acknowledgements
+Once imported, robvis cleans the data, corrects for small spelling errors by coverting each judgement to lowercase and taking only the first letter (e.g.
+"Seriuos" becomes "s", avoiding a potential error from the misspelling), and converts the summary table to a *long tidy format* to aid in creating the plots.
 
-### Supporting information
+### Functions
 
-All code for this project is freely available at www.github.com/mcguinlu/robvis
+`robvis` contains two main functions.
+The first, `rob_summary()`, creates a weighted barplot showing the proportion of information with each judgement for each domain in the assessment tool specified.
+The second, `rob_traffic_light()`, creates a traffic light plot by tabulating each study by each domain, providing a more detailed view of the results of the risk-of-bias assessment.
 
-### Figures
+A worked example using these functions is outlined below, showing the ease with which risk-of-bias plots can be created using `robvis`, while a detailed description of the additional options that can be used with each function is presented in Table  \@ref(tab:robarguments).
+Please note that all examples produced here are created using the stable version available from CRAN.
+
+First, install and load the package:
+
+&nbsp;
+
+```{r}
+
+install.packages("robvis")
+
+library(robvis)
+
+```
+
+&nbsp;
+
+Using the example data set (`data_rob2`) which is built into the package and is presented in Table \@ref(tab:robdata) for reference, the summary barplot shown in Figure \@ref(fig:summaryplot) is created using the following code:
+
+&nbsp;
+
+```{r}
+
+    rob_summary(data = data_rob2,
+                tool = "ROB2", 
+                overall = TRUE)
+
+```
+
+&nbsp;
+
+Similary, using the same data set, the traffic light plot shown in Figure \@ref(fig:trafficplot) is created using:
+
+&nbsp;
+
+``` {r}
+
+    rob_traffic_light(data = data_rob2,
+                      tool = "ROB2",
+                      colour = "colourblind", 
+                      psize = 15)
+
+```
+
+&nbsp;
+
+### Further customisation
+
+The `ggplot2` package in R, based on the "The Grammer of Graphics", allows users to readily create detailed grahpics using a declarative framework and was used to create the templates found in `robvis`.[@wilkinson2012grammar; @ggplot2ref] As a result, both `robvis` functions return a `ggplot` object, meaning they can be easily customised further using the `ggplot2` framework.
+For example, to add a title to the summary bar plot:
+
+&nbsp;
+
+``` {r}
+    library(ggplot2)
+
+    plot <- rob_summary(data_rob2, tool = "ROB2")
+
+    plot +
+    ggtitle("Summary Bar Plot")
+
+```
+
+&nbsp;
+
+A full discussion of the range of post-production modifcations that can be made to the plots via the `ggplot2` package is beyond the scope of this article, though interested readers are directed towards the extensive guidance available.[@ggplot2ref]
+
+## `Shiny` web app
+
+Although `robvis` was originally designed for use in the command-line–based R programming environment, in order to make the tool available to those without knowledge of R, `robvis` also exists as a web-app, available via www.riskofbias.info/.[@robviswebapp]
+
+The app was built using `Shiny`,[@shinyref] a R package which makes it easy to produce interactive web-apps, and provides a Graphical User Interface (GUI) for the `robvis`, allowing users to interact with the functions presented above without the need to download R or type any commands.
+Users can upload their data, choose the tool they used to perform the assessments, select a colour scheme, and define other parameters depending on whether they are producing a traffic light or summary bar plot, all through the online app.
+
+# Discussion
+
+`robvis` enables evidence synthesists with varying levels of ability in R to quickly produce two common risk of bias assessment figures at publication quality.
+While `robvis` is a stable package, there is a range of additional functionality that could be added.
+At present, the number of tools with a specific template included in `robvis` is limited - adding additional templates is a priority.
+For example, a template for ROBIS, a tool for assessing risk of bias in systematic reviews, is in developement.[@whiting2016robis] Additionally, the tool does not yet allow for the production of paired forest plots, where the risk of bias judgement is presented alongside each specific result included in the meta-analysis.[@cochranechpt7] This was initally considered to be beyond the scope of the tool, as it involves the visualisation of something other than risk of bias assessments.
+However, following user-driven demand, this functionality is in development and will be available in the near future.
+Finally, we would like to add similar functionaly as that provided by the `metafor::reporter()` function, which generates a brief paragraph of text describing the results of a meta-analysis.
+The future `robvis::reporter()` function would do the same, but provide a boilerplate description of the assessment tool used and the key domains at risk of bias.
+
+`robvis` serves a good example of the advantages of "packaging" the R scripts that evidence synthesists have created for personal use.[@wickham2015r] For example, it is likely that several other evidence synthesists have written scripts to produce similar risk of bias plots to those presented here - in fact, we personally know of at least one other research group that has done so.
+This duplication of time and effort is inefficient, and creating and sharing well-documented R packages represents one way to reduce this inefficiency.
+Taking this approach one step further, `Shiny` apps represent a straightforward way to provide a user-friendly graphical interface for a newly created package within a very short timeframe, expanding the potential pool of users of the new package to anyone with an internet connection.
+
+Further, creating a package using R has a number of unique advantages.
+In the first instance, it provides access to a range of powerful tools including the `ggplot` infrastructure as demonstated above, but also `RMarkdown`, which allows you to create documents that can be rendered into a range of formats such as PDF, HTML, or Word.[@xie2018r] Additionally, and focusing specifically on evidence synthesis, building new tools as packages in R allows for easy intergration with the range of existing evidence synthesis packages.
+Recently, the `metaverse` project, of which `robvis` is a part, has begun to curate a collection of R packages that cover different aspects of the systematic review and meta-analysis process which, when taken together, form a cohert end-to-end open-source alternative to commerical offerings such as Covidence or RevMan.
+Key offerings in this suite of packages include `litsearcher`, which facilitates systematic search strategy development, `revtools`, a package for managing the review process and performing title and abstract screening, and `metafor`, a package for conducting meta-analyses in R.[@grames2019automated; @westgate2019revtools; @metaforref]
+
+#####
+
+# Back Matter
+## Acknowledgments
+
+The following people provided valuable feedback that contributed to the development of the `robvis` tool: Emily Kothe,  Eliza Grames, Matthew Page, Alexandra Bannach-Brown, Kyle Hamilton, Charles Gray, Vincent Cheng, Wouter van Amsterdamn, Neal Haddaway and Martin Westgate.
+
+## Code/Data availability statement
+The software and data presented in this paper are freely available on GitHub: https://github.com/mcguinlu/robvis 
+#####
+
+# Tables/Figures
+
+```{r robdata, echo = FALSE, eval = TRUE}
+
+plotdata <- data_rob2
+
+knitr::kable(plotdata, caption = "Example dataset for the ROB2 tool contained within `robvis`")
+
+```
+
+#####
+
+``` {r robarguments, echo = FALSE, eval = TRUE}
+
+arguments <- data.frame(stringsAsFactors=FALSE,
+              argument = c("data", "tool", "colour", "overall", "weighted",
+                           "psize"),
+           rob_summary = c("X", "X", "X", "X", "X", ""),
+     rob_traffic_light = c("X", "X", "X", "", "", "X"),
+           Description = c("Defines the dataframe containing the summary (domain) level risk-of-bias assessments.
+See the text and Table 1 for the format expected by `robvis`", "Defines the risk of bias assessment tool used.
+The RoB2 (`tool='ROB2'`), ROBINS-I (`tool='ROBINS-I'`), and QUADAS-2 (`tool='QUADAS-2'`) assessments tools are currently supported.
+Other tools can be visualised using the generic template (`tool = 'ROB1'`)", "Defines the colour scheme for the plot.
+The default is `colour = 'cochrane'` which uses the ubiquitous Cochrane colours, while a preset option for a colour-blind friendly palette is also available (`colour = 'colourblind'`).
+Alternatively, users can specify their own colour scheme e.g.
+`colour = c('#f442c8', '#bef441', '#000000')`", "Defines whether to include an additional bar showing the distibution of overall risk of bias judgements in the summary barplot figure.
+Default is `overall = FALSE`.", "Defines whether weights should be used to produce the summary barplot figure.
+Default is `weighted = TRUE`, in line with current Cochrane Collaboration guidance.", "Defines the size of the points in the traffic light plot.
+Default is `psize = 20`."))
+
+knitr::kable(arguments,
+             caption = "Description of the arguments available in the two main `robvis` functions",
+             align = c("l","c","c","l"),
+             col.names = c("Argument","`rob_summary()`","`rob_traffic_light()`", "Description"))
+
+```
+
+#####
+
+``` {r summaryplot, echo = FALSE, eval = TRUE, fig.cap = "Example risk of bias summary plot created using `robvis`"}
+
+ggplot2::ggsave(
+          filename = "figs/robsummplot.png",
+          plot = robvis::rob_summary(plotdata, "ROB2", overall = TRUE) +
+   ggplot2::theme(plot.background = ggplot2::element_rect(colour = "black")),
+          width = 8,
+          height = 2.41,
+          dpi = 1000
+          )
+
+knitr::include_graphics("figs/robsummplot.png")
+
+```
+
+######
+
+``` {r trafficplot, echo = FALSE, eval = TRUE, fig.cap = "Example risk of bias traffic light plot created using `robvis`"}
+
+ggplot2::ggsave(
+          filename = "figs/robtfplot.png",
+          plot = robvis::rob_traffic_light(data = plotdata, "ROB2", psize = 15, colour = "colourblind"),
+          width = 7,
+          height = 8,
+          dpi = 1000
+          )
+
+knitr::include_graphics("figs/robtfplot.png")
+```
+
+#####
+
+# Bibliography

### 2020-01-30 R/rob_summary.R
Added functionality to check that the tool argument is in an acceptable format

@@ -35,6 +35,17 @@ rob_summary <-
     Weights <- NULL
     domain <- NULL
 
+
+    if((tool %in% rob_tools())==FALSE) {
+      stop(
+        paste("\nTool name \"",
+              tool,
+              "\" not recognised \nAcceptable tools names can be found using the rob_tools() function")
+      )
+    }
+
+
+
     # ROB-2=========================================================================
 
     if (tool == "ROB2") {

### 2020-01-30 R/rob_traffic_light.R

@@ -30,6 +30,14 @@ rob_traffic_light <- function(data, tool, colour = "cochrane",
     Study <- NULL
     domain <- NULL
 
+    if((tool %in% rob_tools())==FALSE) {
+      stop(
+        paste("\nTool name \"",
+              tool,
+              "\" not recognised \nAcceptable tools names can be found using the rob_tools() function")
+      )
+    }
+
 # ROB-2=========================================================================
 
     if (tool == "ROB2") {

### 2020-01-30 R/rob_tools.R
Changed how the rob_tools() function prints output, allowing use as helper function for other functions

@@ -5,9 +5,5 @@
 #' @export
 
 rob_tools <- function() {
-    print("ROB2")
-    print("ROBINS-I")
-    print("QUADAS-2")
-    print("ROB1")
-    print("ROBINS-I Online")
+    c("ROB2", "ROBINS-I", "QUADAS-2", "ROB1", "ROBINS-I ONLINE")
 }

### 2020-02-27 R/rob_summary_tools.R
Remove old rob_tools() function

@@ -1,11 +1,0 @@
-#' List tools covered by rob_summary().
-#' @description rob_tools() will list the tools that can currently be plotted using the rob_summary() function.
-#' @export
-
-rob_tools <- function() {
-    print("ROB2")
-    print("ROBINS-I")
-    print("QUADAS-2")
-    print("ROB1")
-    print("ROBINS-I Online")
-}

### 2020-02-27 tests/testthat/test_robtools.R
Add tests for new rob_tools() function

@@ -1,0 +1,6 @@
+context("rob_tools()")
+
+test_that("Length of rob_tools() output", {
+  # expect_error(rob_summary(data_rob2))
+  expect_equal(length(rob_tools()),5)
+})

### 2020-02-27 README.Rmd

@@
 [![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)
-[![CRAN Badge.](https://www.r-pkg.org/badges/version/robvis)](https://cran.r-project.org/web/packages/robvis/index.html)
+[![CRAN Badge.](https://www.r-pkg.org/badges/version-ago/robvis)](https://cran.r-project.org/web/packages/robvis/index.html)
 [![CRAN Downloads.](https://cranlogs.r-pkg.org/badges/last-month/robvis)](https://cran.r-project.org/web/packages/robvis/index.html)
+[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.3552342.svg)](https://doi.org/10.5281/zenodo.3552342)
 <br>
@@
 
+* Veloso, Andreia, Selene G.
+Vicente, and Marisa G.
+Filipe.
+"[Effectiveness of Cognitive Training for School-Aged Children and Adolescents With Attention Deficit/Hyperactivity Disorder: A Systematic Review.](https://www.frontiersin.org/articles/10.3389/fpsyg.2019.02983/full)" Frontiers in Psychology 10 (2020): 2983.
+* Simillis, Constantinos, et al.
+"[Postoperative chemotherapy improves survival in patients with resected high‐risk stage II colorectal cancer: results of a systematic review and meta‐analysis.](https://onlinelibrary.wiley.com/doi/pdf/10.1111/codi.14994)" Colorectal Disease (2020).
 * Habadi, Mohammed Ibrahim, et al.

### 2020-02-27 RSM-paper/manuscript.Rmd

--- 2020-01-17 RSM-paper/manuscript.Rmd
@@
 ---
-title: "RSM-paper"
+title: "RSM - Call for papers on data visualization"
 bibliography: references.bib
-csl: nature.csl
+csl: ama.csl
 output:
@@
 
-## Type
+``` {r, echo = FALSE, warning=FALSE, message=FALSE }
+library(robvis)
+library(cowplot)
 
-Either of:
+knitr::opts_chunk$set(eval=FALSE)
 
-__Brief Method Notes__ describe or critique a particular method, procedure, or graphic display.
-A Brief Method Note should focus on what is innovative or useful, or problematic about the method.
-The method or procedure should be presented clearly and with sufficient detail.
-Brief Method Notes are limited to 1,500 words (excluding References).
+```
 
-__Computational Tools and Methods__ describe software tools and computational methods for facilitating evidence synthesis.
-These types of articles are expected to at least in part describe accompanying software (e.g., an R package or a web-based tool).
-Typically, these are written upon invitation from the Computational Tools and Methods feature Editor .
-However, suggestions are always welcome and should be sent directly to the Software Review Editor .
-Computational Tools and Methods articles are expected to be relatively brief, but we do not impose a formal limit.
+# Front Matter
+__Title: __  
+robvis: an R package and Shiny web app for visualizing risk-of-bias assessments
 
-## Authors
+&nbsp;
 
-## Funding
+__Authors and Affliations__
 
-Acknowledge the Bristol Alumni Foundation, the Evidence Synthesis Hackathon and the NIHR.
+Luke A McGuinness^1,2^ (ORCID: 0000-0001-8730-9761), 
+Julian PT Higgins^1,2^ (ORCID: 0000-0002-8323-2514)
 
-## Introduction
+(1) MRC University of Bristol Integrative Epidemiology Unit, Bristol, UK
+(2) Bristol Medical School: Population Health Sciences, University of Bristol, Bristol, UK
 
-No other visualisation software exists explicitly for the purpose of visualising risk of bias assessments
+&nbsp;
 
-## Development
+__Corresponding author:__
 
-Time
+Luke McGuinness; Bristol Medical School, University of Bristol,
+Canynge Hall, 39 Whatley Road, Bristol, BS8 2PS, United Kingdom.; luke.mcguinness@bristol.ac.uk
 
-ESH
+&nbsp;
 
-Community involvement
+__Article type__
 
+_Computational Tools and Methods_
+
+&nbsp;
+
+__Funding__
+
+LAM is supported by an NIHR Doctoral Research Fellowship (DRF-2018-11-ST2-048).
+Attendence at the Evidence Synthesis Hackathon in April 2019 was supported by a grant from the Evidence Synthesis Hackathon itself and the University of Bristol Alumni Foundation.
+JPTH is a National Institute for Health Research (NIHR) Senior Investigator (NF-SI-0617-10145).
+JPTH is supported by NIHR Bristol Biomedical Research Centre at University Hospitals Bristol NHS Foundation Trust and the University of Bristol.
+JPTH is supported by the NIHR Applied Research Collaboration West (ARC West) at University Hospitals Bristol NHS Foundation Trust.
+JPTH is a member of the MRC Integrative Epidemiology Unit at the University of Bristol.
+The views expressed in this article are those of the authors and do not necessarily represent those of the NHS, the NIHR, MRC, or the Department of Health and Social Care.
+
+&nbsp;
+
+__Keywords__
+
+Risk of bias; Evidence synthesis; Data visualisation; R
+
+#####
+
+# Abstract
+Despite a major increase in the range and number of software offerings now available to help researchers produce evidence syntheses, there is currently no generic tool for producing figures to display and explore the risk-of-bias  assessments that routinely take place as part of systematic review.
+Fortunately, tools such as the R programming environment and `Shiny` (an R package for building interactive web apps) have made it easier than ever to produce new tools to help in producing evidence syntheses.
+
+We present a new tool, `robvis` (Risk-Of-Bias VISualization; available as an R package and web app) which facilitates rapid production of publication-quality risk-of-bias assessment figures.
+We present a timeline of the tool’s development and its key functionality.
+
+#####
+
+# Introduction
+
+Synthesis of evidence from the totality of relevant research is becoming more important than ever in informing policy across an increasingly wide range of fields.[@donnelly2018] Risk of bias assessment - evaluation of the internal validity of studies included in a systematic review - often forms a key part of the evidence synthesis process, particularly in the health sciences.[@cochranechpt7] A well-developed family of tools is widely used, which have in common the characteristic that they evaluate specific domains of bias rather being constructed as a checklist or a quantitative score.[@cochranechpt7] These tools include the RoB 2 tool for randomized trials,[@sterne2019rob] the ROBINS-I tool for non-randomized studies of interventions,[@sterne2016robins] the QUADAS 2 tool for test accuracy and the ROBIS tool for systematic reviews.[@whiting2011quadas] Within each bias domains a judgement is reached about the strength of the study in that regard: for example, the first domain in the Cochrane RoB 2 tool deals with bias arising from the randomization process.[@sterne2019rob] Accessible graphics summarizing the results of these domain-based risk-of-bias assessments are included in reports of systematic reviews.
+A convenient plot in many reviews is a “traffic light” plot, which tabulates the judgement for each study in each domain.
+For larger numbers of studies, when such a table become unmanageable, a popular alternative is a weighted bar plot, which show the proportion of information with each judgement for each domain.[@higgins2008assessing]
+
+Researchers can face a number of barriers in creating these plots.
+While some evidence synthesis platforms, such as Cochrane’s Review Manager,[@cochrane2014review] are able to produce these visualizations, not all researchers use these systems to conduct their systematic reviews, and copying the risk-of-bias data into these systems simply to produce the plots is inefficient and error prone.
+Likewise, creating the figures by hand, through software such as MS PowerPoint or Adobe Illustrator, may lead to unintentional errors and require the plots to be redrawn during an update to the review.
+Additionally, while the field of evidence synthesis software has grown rapidly in recent years,[@marshall2015systematic] this growth has not been equally distributed across the different aspects of the systematic review process.
+For example, a recent review found several software offerings aimed specifically at the abstract screening stage of the review process,[@harrison2020software] but no similar time- and error-reducing tool has been proposed for visualizing the results of risk-of-bias assessments.
+
+Fortunately, tools such as R, RStudio and `Shiny` (an R package for building interactive web apps) have made it easier than ever to produce such a tool.[@rref; @rstudioref; @shinyref] Here, we present `robvis` (Risk Of Bias VISualiation),[@mcguinness2019a] an R package and `Shiny` web-app that allows users to create publication-ready risk-of-bias plots quickly and easily.
+Originally created for use with the major risk-of-bias assessment tools used in health research, the tool allows users to visualize the results from any domain-based risk-of-bias assessment or quality appraisal tool.
+
+The tool is open-source and available to use free of charge.
+Users can download a stable version of the R package from CRAN ([https://cran.r-project.org/package=robvis](https://cran.r-project.org/package=robvis)); or access and contribute to the development version via GitHub ([https://github.com/mcguinlu/robvis](https://github.com/mcguinlu/robvis)).
+Extended guidance for the tool is also available via the “Doing Meta-Analysis in R” online guide.[@mathias_harrer_2019_2551803] Below, we discuss the tool's development and key functionality.
+
+# Development
+
+Development of `robvis` began in April 2019 at the Evidence Synthesis Hackathon (ESH), an event which brings together interested researchers, practitioners and coders to discuss and develop new open-source evidence synthesis technologies.
+Test versions of both the R package and the web app were made available in early June 2019, with attendees of the ESH and members of the Bristol Appraisal and Review of Research (BARR) group at the University of Bristol being invited to test the tool and provide feedback.
+This feedback, along with other feature suggestions from the wider evidence synthesis community captured via GitHub issues, was incorporated and the first release version of the package was uploaded to CRAN in November 2019.
+The tool has been well received and is beginning to be cited in the evidence synthesis literature.[@gibb2019consistent; @habadi2019prevalence; @veloso2020effectiveness;@simillis2020; @tanneru2020]
+
+# Functionality
 ## R package
+### Tool templates and example data sets
 
-## Shiny web-app
+At the time of writing, the tool includes templates for three major tools: the Cochrane RoB 2 tool for assessing randomised controlled trials,[@sterne2019rob] the ROBINS-I tool for assessing non-randomized studies of interventions,[@sterne2016robins] and the QUADAS-2 tool for assessing diagnostic accuracy studies.[@whiting2011quadas] These templates automatically apply the correct risk-of-bias domain names to the figures, and label the judgement levels appropriately (e.g.
+“Low”, “Some Concerns”, “High” in the case of the RoB 2 tool).
+In addition, `robvis` contains a general template that can be used to visualize the result of any domain-based assessment tool.
+The generic template has greater flexibility than the tool-specific templates, allowing a user-specified number of domains and custom domain titles to be used.
+It is suitable for use with the original version of the Cochrane risk-of-bias tool for randomized trials,[@higgins2011] in which flexibility in the specification of domains was permitted.
+Since users of more recent tools such as RoB 2 and ROBINS-I are not permitted to modify the domains, we strongly encourage use of the in-built templates for these.
 
-## Example: choose review and apply
+In order to help users familiarize themselves with the package and its functionality, `robvis` contains built-in example datasets for each template.
+We illustrate the example data for the RoB 2 tool for assessing risk of bias in randomized controlled trials in Table  \@ref(tab:robdata).
 
-## Discussion
+### Data import and cleaning
 
-Anyone can design.
+`robvis` expects risk-of-bias summary table to be provided in a specific format (see Table 1 for an example).
+The first column should contain the unique study/result identifier.
+The second-to-last column should contain the overall risk-of-bias judgements.
+The final column contains the weights (e.g.
+study precision or the weight assigned in a meta-analysis).
+This weight column is used to create the summary bar plot, as current guidance recommends dividing the bars to show the proportion of information at each level of risk of bias, determined by the cumulative weight at that level, rather than simply showing the number of studies in each category.[@cochranechpt7]
 
-`robvis` forms one part of the `metaverse`, a collection of tools written using R that cover. A key example is `revtools`, original published in this journal
+Once imported, `robvis` cleans the data, corrects for small spelling errors by converting each judgement to lowercase and taking only the first letter (e.g.
+“Seriuos  ” becomes “s”, avoiding a potential error from the misspelling), and converts the summary table to a long tidy format to aid in creating the plots.
 
-## Back matter
+### Functions
 
-### Acknowledgements
+`robvis` contains two main functions.
+The first, `rob_traffic_light()`, creates a traffic light plot by tabulating each study by each domain, providing a more detailed view of the results of the risk-of-bias assessment.
+The second, `rob_summary()`, creates a weighted bar plot  showing the proportion of information with each judgement for each domain in the assessment tool specified.
 
-### Supporting information
+A worked example using these functions is outlined below, showing the ease with which risk-of-bias plots can be created using `robvis`.
+A detailed description of the additional options that can be used with each function is presented in Table 2.
+All examples produced in this article are created using the stable version available from CRAN.
 
-All code for this project is freely available at www.github.com/mcguinlu/robvis
+To install and load the package:
 
-### Figures
+&nbsp;
+
+```{r}
+
+install.packages("robvis")
+
+library(robvis)
+
+```
+
+&nbsp;
+
+Using the example data set (`data_rob2`) which is built into the package and is presented in Table \@ref(tab:robdata) for reference, the traffic light plot shown in Figure \@ref(fig:trafficplot) is created using:
+
+&nbsp;
+
+``` {r}
+
+rob_traffic_light(data = data_rob2,
+                  tool = "ROB2",
+                  colour = "colourblind", 
+                  psize = 15)
+
+```
+
+&nbsp;
+
+Similary, using the same data set, the summary barplot shown in Figure \@ref(fig:summaryplot) is created using:
+
+&nbsp;
+
+```{r}
+
+rob_summary(data = data_rob2,
+            tool = "ROB2", 
+            overall = TRUE)
+
+```
+
+&nbsp;
+
+### Further customisation
+
+The `ggplot2` package in R, based on the “The Grammar of Graphics”, allows users to create detailed graphics using a declarative framework and was used to create the templates found in `robvis`.[@ggplot2ref; @wilkinson2012grammar] As a result, both `robvis` functions return a `ggplot` object, meaning they can be easily customized further using the `ggplot2` framework.
+For example, to add a title to the summary bar plot:
+
+&nbsp;
+
+``` {r}
+    library(ggplot2)
+
+    plot <- rob_summary(data_rob2, tool = "ROB2")
+
+    plot +
+    ggtitle("Summary Bar Plot")
+
+```
+
+&nbsp;
+
+For a full discussion of the range of post-production modifications that can be made to the plots via the `ggplot2` package, we refer the reader to the extensive guidance available.[@wilkinson2012grammar]
+
+## `Shiny` web app
+
+Although `robvis` was originally designed for use in the command-line–based R programming environment, we developed a web app to make the tool available to those without knowledge of R.
+This is available via [www.riskofbias.info](https://www.riskofbias.info).[@robviswebapp] The app was built using `Shiny`,[@shinyref] an R package which makes it easy to produce interactive web-apps, and provides a graphical user interface (GUI) for the `robvis` package, allowing users to interact with the functions presented above without the need to download R or type any commands.
+Users can upload their data as comma-separate values (a CSV file), choose the tool they used to perform the assessments, select a colour scheme, and define other parameters depending on whether they are producing a traffic light or summary bar plot, all through the online app.
+
+####
+
+# Discussion
+
+`robvis`  facilitates the rapid production of two common risk-of-bias assessment figures at publication quality.
+By implementing `robvis` both as an R package and a `Shiny` web app, its functionality is available to evidence synthesists with varying levels of ability in R.
+`robvis` serves as an example of the advantages of “packaging” the R scripts that evidence synthesists often create for personal use.[@wickham2015r] It is likely that several other evidence synthesists have written scripts to produce similar risk-of-bias plots to those presented here - in fact, we personally know of at least one other research group that has done so.
+This duplication of time and effort is inefficient, and creating and sharing well-documented R packages represents one way to reduce this inefficiency.
+Taking this approach one step further, `Shiny` apps represent a straightforward way to provide a user-friendly GUI for a newly created R package within a very short timeframe, expanding the potential pool of users of the package to anyone with an internet connection.
+
+Creating a package using R has a number of particular advantages.
+R provides access to a range of powerful tools including the `ggplot` infrastructure as demonstrated above, and RMarkdown, which enables creation of documents that can be rendered in a range of formats such as PDF, HTML, or Word.[@xie2018r] Furthermore, and focusing specifically on evidence synthesis, building new tools as packages in R allows for easy integration with the range of existing evidence synthesis packages.
+Recently, the `metaverse` project,[@variousauthors2020] of which `robvis` is a part, has begun to curate a collection of R packages that cover different aspects of the systematic review and meta-analysis process which, when taken together, form a coherent end-to-end open-source alternative to commercial offerings such as Covidence or Review Manager.
+Key offerings in this suite of packages include litsearcher, which facilitates systematic search strategy development, revtools, a package for managing the review process and performing title and abstract screening, metaDigitise, a package for automatic extraction of data from figures in research papers, and metafor, a package for conducting meta-analyses in R.[@grames2019automated; @metaforref; @pick2018; @westgate2019revtools]
+
+While `robvis` is a stable package, a range of additional functionality could be added.
+At present, the number of tools with a specific template included in `robvis` is limited - adding additional templates is a priority.
+For example, a template for ROBIS, a tool for assessing risk of bias in systematic reviews, is in developement.[@whiting2016robis] Additionally, the tool does not yet allow for the production of paired forest plots, where the risk-of-bias judgement is presented alongside each specific result included in the meta-analysis.[@cochranechpt7] This was initially considered to be beyond the scope of the tool, as it involves the visualization of something other than risk-of-bias assessments.
+However, following user-driven demand, this functionality is in development and will be available in the near future.
+Finally, we would like to add similar functionality to that provided by the `metafor::reporter()` function, which generates a brief paragraph of text describing the results of a meta-analysis.
+The future `robvis::reporter()` function would provide a boilerplate description of the assessment tool used and the key domains at risk of bias.
+
+#####
+
+# Back Matter
+## Acknowledgments
+
+The following people provided valuable feedback that contributed to the development of the `robvis` tool: Emily Kothe,  Eliza Grames, Matthew Page, Alexandra Bannach-Brown, Kyle Hamilton, Charles Gray, Vincent Cheng, Wouter van Amsterdamn, Neal Haddaway and Martin Westgate.
+
+## Code/Data availability statement
+The software and data presented in this paper are freely available on GitHub: https://github.com/mcguinlu/robvis
+
+#####
+
+# Highlights
+
+* Risk-of-bias assessment is a key element of the systematic review workflow.
+* No other tool exists explicitly for the purpose of visualizing risk-of-bias results. 
+* Here we present `robvis`, an open-source R package and `Shiny` web app for creating publication-ready risk-of-bias assessment figures.
+* `robvis` forms part of the metaverse, a collection of R packages designed to provide an evidence synthesis workflow in R.
+
+#####
+
+# Tables/Figures
+
+```{r robdata, echo = FALSE, eval = TRUE}
+
+plotdata <- robvis::data_rob2
+
+plotdata$Weight <- as.numeric(round(plotdata$Weight,2))
+
+plotdata$Weight <- gsub("\\.00", "", plotdata$Weight)
+
+knitr::kable(plotdata, caption = "Example dataset for the ROB 2 tool contained within `robvis`")
+
+```
+
+#####
+
+``` {r robarguments, echo = FALSE, eval = TRUE}
+
+arguments <- data.frame(stringsAsFactors=FALSE,
+              argument = c("data", "tool", "colour", "overall", "weighted",
+                           "psize"),
+     rob_traffic_light = c("X", "X", "X", "", "", "X"),
+           rob_summary = c("X", "X", "X", "X", "X", ""),
+           Description = c(
+"Defines the dataframe containing the summary (domain) level risk-of-bias assessments. See the text and Table 1 for the format expected by `robvis`",
+"Defines the risk of bias assessment tool used.
+The RoB2 (`tool=\"ROB2\"`), ROBINS-I (`tool=\"ROBINS-I\"`), and QUADAS-2 (`tool=\"QUADAS-2\"`) assessments tools are currently supported.
+Other tools can be visualised using the generic template (`tool = \"Generic\"`) [Note 1]",
+"Defines the colour scheme for the plot.
+The default is `colour = \"cochrane\"` which uses the \"Cochrane\" (red, yellow, green) colours, while a preset option for a colour-blind friendly palette is also available (`colour = \"colourblind\"`).
+Alternatively, users can specify their own colour scheme e.g.
+`colour = c(\"#f442c8\", \"#bef441\", \"#000000\")`",
+"Defines whether to include an additional bar showing the distibution of overall risk of bias judgements in the summary barplot figure. Default is `overall = FALSE`.",
+"Defines whether weights should be used to produce the summary barplot figure. Default is `weighted = TRUE`, in line with current Cochrane Collaboration guidance.",
+"Defines the size of the points in the traffic light plot. Default is `psize = 20`."))
+
+knitr::kable(arguments,escape = T,
+             caption = "Description of the arguments available in the two main `robvis` functions. ‘X’ indicates that the option is available for the respective function.",
+             align = c("l","c","c","l"),
+             col.names = c("Argument","``rob_traffic_light()``","``rob_summary()``", "Description"))
+
+```
+
+Note 1: This option (`tool = "Generic"`) reflects the general template name used in the current development version of `robvis`, which will become the standard for all future iterations of the package.
+However, in the current CRAN version, the generic template is accessed using `tool = "ROB1"`.
+
+######
+
+``` {r trafficplot, echo = FALSE, eval = TRUE, fig.cap = "Example risk of bias traffic light plot created using `robvis`"}
+
+plotdata <- data_rob2
+
+tfplot <- robvis::rob_traffic_light(data = plotdata, "ROB2", psize = 15, colour = "colourblind")
+
+ggplot2::ggsave(
+          filename = "figs/Fig1-rob-traffic-light-plot.tiff",
+          plot = tfplot,
+          width = 7,
+          height = 8,
+          dpi = 1500
+          )
+
+ggplot2::ggsave(
+          filename = "figs/Fig1-rob-traffic-light-plot.png",
+          plot = tfplot,
+          width = 7,
+          height = 8,
+          dpi = 1000
+          )
+
+knitr::include_graphics("figs/Fig1-rob-traffic-light-plot.png")
+```
+
+#####
+
+``` {r summaryplot, echo = FALSE, eval = TRUE, fig.cap = "Example risk of bias summary plot created using `robvis`"}
+
+sumplot <- robvis::rob_summary(plotdata, "ROB2", overall = TRUE) +
+   ggplot2::theme(plot.background = ggplot2::element_rect(colour = "black"))
+
+ggplot2::ggsave(
+          filename = "figs/Fig2-rob-summary-barplot.tiff",
+          plot = sumplot,
+          width = 8,
+          height = 2.41,
+          dpi = 1500
+          )
+
+ggplot2::ggsave(
+          filename = "figs/Fig2-rob-summary-barplot.png",
+          plot = sumplot,
+          width = 8,
+          height = 2.41,
+          dpi = 1000
+          )
+
+knitr::include_graphics("figs/Fig2-rob-summary-barplot.png")
+
+```
+
+#####
+
+# Bibliography

### 2020-02-27 README.Rmd

@@
 <br>
-[![Build Status](https://img.shields.io/travis/mcguinlu/robvis.svg?label=build&logo=travis&branch=master)](https://travis-ci.org/mcguinlu/robvis) 
+[![Build Status](https://img.shields.io/travis/mcguinlu/robvis.svg?label=build&logo=travis&branch=master)](https://travis-ci.com/mcguinlu/robvis) 
 [![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/mcguinlu/robvis?branch=master&svg=true)](https://ci.appveyor.com/project/mcguinlu/robvis)
@@
 
-* Veloso, Andreia, Selene G.
-Vicente, and Marisa G.
-Filipe.
+* Tanneru, Karthik, et al.
+"[Meta-analysis and systematic review of intermediate-term follow-up of prostatic urethral lift for benign prostatic hyperplasia.](https://link.springer.com/article/10.1007/s11255-020-02408-y)" International Urology and Nephrology (2020): 1-10.
+* Veloso, Andreia, et al..
 "[Effectiveness of Cognitive Training for School-Aged Children and Adolescents With Attention Deficit/Hyperactivity Disorder: A Systematic Review.](https://www.frontiersin.org/articles/10.3389/fpsyg.2019.02983/full)" Frontiers in Psychology 10 (2020): 2983.

### 2020-03-19 tests/testthat/test_rob_summary.R
Add skip_on_travis() to tests

@@ -3,6 +3,7 @@ context("rob_summary()")
 test_that("ROB - Summary",{
 
 skip_on_cran()
+skip_on_travis()
 skip_on_appveyor()
 
 vdiffr::expect_doppelganger("ROB2 - Basic", rob_summary(data_rob2,"ROB2"))

### 2020-03-19 tests/testthat/test_rob_traffic_light.R

@@ -3,6 +3,7 @@ context("rob_traffic_light()")
 test_that("ROB - Traffic light",{
 
 skip_on_cran()
+skip_on_travis()
 skip_on_appveyor()
 
 vdiffr::expect_doppelganger("TF - ROB2 - Basic", rob_traffic_light(data_rob2,"ROB2"))

### 2020-03-19 README.Rmd
Add new paper to README

@@
 
+* Perivoliotis, Konstantinos, et al.
+"[Comparing the efficacy and safety of laparoscopic and robotic adrenalectomy: a meta-analysis and trial sequential analysis.](https://link.springer.com/article/10.1007/s00423-020-01860-9)" Langenbeck's Archives of Surgery (2020): 1-11.
+* Adile, Ashley A., et al.
+"[Salvage therapy for progressive, treatment-refractory or recurrent pediatric medulloblastoma: a systematic review protocol.](https://systematicreviewsjournal.biomedcentral.com/articles/10.1186/s13643-020-01307-8)" Systematic Reviews 9.1 (2020): 1-9.
 * Tanneru, Karthik, et al.

### 2020-03-19 RSM-paper/manuscript.Rmd

@@
           height = 8,
-          dpi = 1500
+          dpi = 600
           )
@@
           height = 2.41,
-          dpi = 1500
+          dpi = 600
           )

### 2020-03-26 RSM-paper/manuscript.Rmd
Incorporate reviewer-requested changes

@@
 __Title: __  
-robvis: an R package and Shiny web app for visualizing risk-of-bias assessments
+robvis (Risk-Of-Bias VISualization): an R package and Shiny web app for visualizing risk-of-bias assessments
 
@@
 Despite a major increase in the range and number of software offerings now available to help researchers produce evidence syntheses, there is currently no generic tool for producing figures to display and explore the risk-of-bias  assessments that routinely take place as part of systematic review.
-Fortunately, tools such as the R programming environment and `Shiny` (an R package for building interactive web apps) have made it easier than ever to produce new tools to help in producing evidence syntheses.
+However, tools such as the R programming environment and `Shiny` (an R package for building interactive web apps) have made it easier than ever to produce new tools to help in producing evidence syntheses.
 
@@
 
-Synthesis of evidence from the totality of relevant research is becoming more important than ever in informing policy across an increasingly wide range of fields.[@donnelly2018] Risk of bias assessment - evaluation of the internal validity of studies included in a systematic review - often forms a key part of the evidence synthesis process, particularly in the health sciences.[@cochranechpt7] A well-developed family of tools is widely used, which have in common the characteristic that they evaluate specific domains of bias rather being constructed as a checklist or a quantitative score.[@cochranechpt7] These tools include the RoB 2 tool for randomized trials,[@sterne2019rob] the ROBINS-I tool for non-randomized studies of interventions,[@sterne2016robins] the QUADAS 2 tool for test accuracy and the ROBIS tool for systematic reviews.[@whiting2011quadas] Within each bias domains a judgement is reached about the strength of the study in that regard: for example, the first domain in the Cochrane RoB 2 tool deals with bias arising from the randomization process.[@sterne2019rob] Accessible graphics summarizing the results of these domain-based risk-of-bias assessments are included in reports of systematic reviews.
+Synthesis of evidence from the totality of relevant research is becoming more important than ever in informing policy across an increasingly wide range of fields.[@donnelly2018] Risk of bias assessment - evaluation of the internal validity of studies included in a systematic review - often forms a key part of the evidence synthesis process, particularly in the health sciences.[@cochranechpt7] A well-developed family of tools is widely used, which have in common the characteristic that they evaluate specific domains of bias rather being constructed as a checklist or a quantitative score.[@cochranechpt7] These tools include the RoB (Risk of Bias) 2 tool for randomized controlled  trials,[@sterne2019rob] the ROBINS-I (Risk Of Bias In Non-randomized Studies - of Interventions) tool,[@sterne2016robins] the QUADAS 2 (Quality and Applicability of Diagnostic Accuracy Studies) tool [@whiting2011quadas] and the ROBIS (Risk Of Bias in Systematic Reviews) tool.[@whiting2016robis] Within each bias domain a judgement is reached about the strength of the study in that regard: for example, the first domain in the Cochrane RoB 2 tool deals with bias arising from the randomization process.[@sterne2019rob] Accessible graphics summarizing the results of these domain-based risk-of-bias assessments are included in reports of systematic reviews.
 A convenient plot in many reviews is a “traffic light” plot, which tabulates the judgement for each study in each domain.
-For larger numbers of studies, when such a table become unmanageable, a popular alternative is a weighted bar plot, which show the proportion of information with each judgement for each domain.[@higgins2008assessing]
+For larger numbers of studies, when such a table becomes unmanageable, a popular alternative is a weighted bar plot, which show the proportion of information with each judgement for each domain.[@higgins2008assessing]
 
@@
 
-Fortunately, tools such as R, RStudio and `Shiny` (an R package for building interactive web apps) have made it easier than ever to produce such a tool.[@rref; @rstudioref; @shinyref] Here, we present `robvis` (Risk Of Bias VISualiation),[@mcguinness2019a] an R package and `Shiny` web-app that allows users to create publication-ready risk-of-bias plots quickly and easily.
-Originally created for use with the major risk-of-bias assessment tools used in health research, the tool allows users to visualize the results from any domain-based risk-of-bias assessment or quality appraisal tool.
+However, it is now easier than ever to produce such a tool, thanks to the availability of powerful computing offerings including R, RStudio and `Shiny` (an R package for building interactive web apps) [@rref; @rstudioref; @shinyref] Here, we present `robvis` (Risk Of Bias VISualiation),[@mcguinness2019a] an R package and `Shiny` web-app that allows users to create publication-ready risk-of-bias plots quickly and easily.
+While primarily designed for use with the major risk-of-bias assessment tools used in health research (ROB2, ROBINS-I & QUADAS-2), the tool allows users to visualize the results from any domain-based risk-of-bias assessment or quality appraisal tool.
 
 The tool is open-source and available to use free of charge.
-Users can download a stable version of the R package from CRAN ([https://cran.r-project.org/package=robvis](https://cran.r-project.org/package=robvis)); or access and contribute to the development version via GitHub ([https://github.com/mcguinlu/robvis](https://github.com/mcguinlu/robvis)).
-Extended guidance for the tool is also available via the “Doing Meta-Analysis in R” online guide.[@mathias_harrer_2019_2551803] Below, we discuss the tool's development and key functionality.
+Users can download a stable version of the R package from CRAN ([https://cran.r-project.org/package=robvis](https://cran.r-project.org/package=robvis)); or access and contribute to the open-source code that powers the package via GitHub ([https://github.com/mcguinlu/robvis](https://github.com/mcguinlu/robvis)).
+Extended guidance for the tool, including a step-by-step walk-through for those new to the R programming environment, is also available via the “Doing Meta-Analysis in R” online guide.[@mathias_harrer_2019_2551803] Below, we discuss the tool's development and key functionality.
 
@@
 
-At the time of writing, the tool includes templates for three major tools: the Cochrane RoB 2 tool for assessing randomised controlled trials,[@sterne2019rob] the ROBINS-I tool for assessing non-randomized studies of interventions,[@sterne2016robins] and the QUADAS-2 tool for assessing diagnostic accuracy studies.[@whiting2011quadas] These templates automatically apply the correct risk-of-bias domain names to the figures, and label the judgement levels appropriately (e.g.
+At the time of writing, the tool includes templates for three major tools: the Cochrane RoB 2 tool for assessing randomized controlled trials,[@sterne2019rob] the ROBINS-I tool for assessing non-randomized studies of interventions,[@sterne2016robins] and the QUADAS-2 tool for assessing diagnostic accuracy studies.[@whiting2011quadas] These templates automatically apply the correct risk-of-bias domain names to the figures, and label the judgement levels appropriately (e.g.
 “Low”, “Some Concerns”, “High” in the case of the RoB 2 tool).
@@
 The generic template has greater flexibility than the tool-specific templates, allowing a user-specified number of domains and custom domain titles to be used.
-It is suitable for use with the original version of the Cochrane risk-of-bias tool for randomized trials,[@higgins2011] in which flexibility in the specification of domains was permitted.
+It is suitable for use with the original version of the Cochrane risk-of-bias tool for randomized controlled  trials,[@higgins2011] in which flexibility in the specification of domains was permitted.
 Since users of more recent tools such as RoB 2 and ROBINS-I are not permitted to modify the domains, we strongly encourage use of the in-built templates for these.
@@
 
-`robvis` expects risk-of-bias summary table to be provided in a specific format (see Table 1 for an example).
+`robvis` expects the risk-of-bias summary table to be arranged in a specific way (see Table 1 for an example).
 The first column should contain the unique study/result identifier.
-The second-to-last column should contain the overall risk-of-bias judgements.
-The final column contains the weights (e.g.
-study precision or the weight assigned in a meta-analysis).
-This weight column is used to create the summary bar plot, as current guidance recommends dividing the bars to show the proportion of information at each level of risk of bias, determined by the cumulative weight at that level, rather than simply showing the number of studies in each category.[@cochranechpt7]
+The second-to-last column should contain the overall risk-of-bias judgments.
+The final column contains some measure of the result’s precision (e.g.
+the weight assigned to that result in a meta-analysis, or if no meta-analysis was performed, the sample size of the analysis that produced the result).
+This weight column is used to create the summary bar plot, as current guidance recommends dividing the bars to show the proportion of information at each level of risk of bias, determined by the cumulative weight at that level, rather than simply showing the number of studies/results in each category.[@cochranechpt7]
 
@@
 
-To install and load the package:
+To install and load the package in R, enter the following into the console:
 
@@
 
-Similary, using the same data set, the summary barplot shown in Figure \@ref(fig:summaryplot) is created using:
+Similarly, using the same data set, the summary barplot shown in Figure \@ref(fig:summaryplot) is created using:
 
@@
 
-### Further customisation
+### Further customization
 
@@
 This is available via [www.riskofbias.info](https://www.riskofbias.info).[@robviswebapp] The app was built using `Shiny`,[@shinyref] an R package which makes it easy to produce interactive web-apps, and provides a graphical user interface (GUI) for the `robvis` package, allowing users to interact with the functions presented above without the need to download R or type any commands.
-Users can upload their data as comma-separate values (a CSV file), choose the tool they used to perform the assessments, select a colour scheme, and define other parameters depending on whether they are producing a traffic light or summary bar plot, all through the online app.
+Users can upload their data as either an Excel spreadsheet (recommended) or a comma-separate values (CSV) file, or can manually enter it directly into the app.
+Uploaded data are passed through a number of quality control checks that ensure the app will work correctly, and users are prevented from producing the plots until any issues identified have been addressed.
+Finally, users can customise their plots by defining a colour scheme and other parameters, all through the online app.
 
@@
 This duplication of time and effort is inefficient, and creating and sharing well-documented R packages represents one way to reduce this inefficiency.
-Taking this approach one step further, `Shiny` apps represent a straightforward way to provide a user-friendly GUI for a newly created R package within a very short timeframe, expanding the potential pool of users of the package to anyone with an internet connection.
+Taking this approach one step further, `Shiny` apps represent a straightforward way to provide a user-friendly GUI for a newly created R package within a very short time-frame, expanding the potential pool of users of the package to anyone with an internet connection.
 
@@
 Recently, the `metaverse` project,[@variousauthors2020] of which `robvis` is a part, has begun to curate a collection of R packages that cover different aspects of the systematic review and meta-analysis process which, when taken together, form a coherent end-to-end open-source alternative to commercial offerings such as Covidence or Review Manager.
-Key offerings in this suite of packages include litsearcher, which facilitates systematic search strategy development, revtools, a package for managing the review process and performing title and abstract screening, metaDigitise, a package for automatic extraction of data from figures in research papers, and metafor, a package for conducting meta-analyses in R.[@grames2019automated; @metaforref; @pick2018; @westgate2019revtools]
+Key offerings in this suite of packages include `litsearcher`, which facilitates systematic search strategy development, `revtools`, a package for managing the review process and performing title and abstract screening, `metaDigitise`, a package for automatic extraction of data from figures in research papers, and `metafor`, a package for conducting meta-analyses in R.[@grames2019automated; @metaforref; @pick2018; @westgate2019revtools]
 
@@
 At present, the number of tools with a specific template included in `robvis` is limited - adding additional templates is a priority.
-For example, a template for ROBIS, a tool for assessing risk of bias in systematic reviews, is in developement.[@whiting2016robis] Additionally, the tool does not yet allow for the production of paired forest plots, where the risk-of-bias judgement is presented alongside each specific result included in the meta-analysis.[@cochranechpt7] This was initially considered to be beyond the scope of the tool, as it involves the visualization of something other than risk-of-bias assessments.
+For example, a template for ROBIS, the risk-of-bias assessment tool for systematic reviews,[@whiting2016robis] is in developement.
+Additionally, the `robvis` tool does not yet allow for the production of paired forest plots, where the risk-of-bias judgement is presented alongside each specific result included in the meta-analysis.[@cochranechpt7] This was initially considered to be beyond the scope of the tool, as it involves the visualization of something other than risk-of-bias assessments.
 However, following user-driven demand, this functionality is in development and will be available in the near future.
@@
 
-knitr::kable(plotdata, caption = "Example dataset for the ROB 2 tool contained within `robvis`")
+knitr::kable(plotdata, caption = "Example dataset for the ROB 2 tool contained within `robvis`. Data can be imported to the tool from with an Excel spreadsheet or a CSV file.")
 
@@
 knitr::kable(arguments,escape = T,
-             caption = "Description of the arguments available in the two main `robvis` functions. ‘X’ indicates that the option is available for the respective function.",
+             caption = "Description of the arguments available in the two main functions of the `robvis` R package. ‘X’ indicates that the option is available for the respective function.",
              align = c("l","c","c","l"),
@@
 
-``` {r trafficplot, echo = FALSE, eval = TRUE, fig.cap = "Example risk of bias traffic light plot created using `robvis`"}
+``` {r trafficplot, echo = FALSE, eval = TRUE, fig.cap = "Example risk of bias traffic light plot of ROB2 assessments created using `robvis`"}
 
@@
 
-``` {r summaryplot, echo = FALSE, eval = TRUE, fig.cap = "Example risk of bias summary plot created using `robvis`"}
+``` {r summaryplot, echo = FALSE, eval = TRUE, fig.cap = "Example risk of bias summary plot of ROB2 assessments created using `robvis`"}
 

### 2020-04-07 RSM-paper/manuscript.Rmd
Incorporate JPTH's suggested changes

@@
 __Title: __  
-robvis (Risk-Of-Bias VISualization): an R package and Shiny web app for visualizing risk-of-bias assessments
+Risk-Of-Bias VISualization (robvis): an R package and Shiny web app for visualizing risk-of-bias assessments
 
@@
 
-(1) MRC University of Bristol Integrative Epidemiology Unit, Bristol, UK
-(2) Bristol Medical School: Population Health Sciences, University of Bristol, Bristol, UK
+(1) MRC Integrative Epidemiology Unit at the University of Bristol, Bristol, UK
+(2) Population Health Sciences, Bristol Medical School, University of Bristol, Bristol, UK
 
@@
 Luke McGuinness; Bristol Medical School, University of Bristol,
-Canynge Hall, 39 Whatley Road, Bristol, BS8 2PS, United Kingdom.; luke.mcguinness@bristol.ac.uk
+Canynge Hall, 39 Whatley Road, Bristol, BS8 2PS, United Kingdom; luke.mcguinness@bristol.ac.uk
 
@@
 LAM is supported by an NIHR Doctoral Research Fellowship (DRF-2018-11-ST2-048).
-Attendence at the Evidence Synthesis Hackathon in April 2019 was supported by a grant from the Evidence Synthesis Hackathon itself and the University of Bristol Alumni Foundation.
+Attendance at the Evidence Synthesis Hackathon in April 2019 was supported by a grant from the Evidence Synthesis Hackathon itself and the University of Bristol Alumni Foundation.
 JPTH is a National Institute for Health Research (NIHR) Senior Investigator (NF-SI-0617-10145).
@@
 Despite a major increase in the range and number of software offerings now available to help researchers produce evidence syntheses, there is currently no generic tool for producing figures to display and explore the risk-of-bias  assessments that routinely take place as part of systematic review.
-However, tools such as the R programming environment and `Shiny` (an R package for building interactive web apps) have made it easier than ever to produce new tools to help in producing evidence syntheses.
-
-We present a new tool, `robvis` (Risk-Of-Bias VISualization; available as an R package and web app) which facilitates rapid production of publication-quality risk-of-bias assessment figures.
+However, tools such as the R programming environment and `Shiny` (an R package for building interactive web apps) have made it straightforward to produce new tools to help in producing evidence syntheses.
+We present a new tool, `robvis` (Risk-Of-Bias VISualization), available as an R package and web app, which facilitates rapid production of publication-quality risk-of-bias assessment figures.
 We present a timeline of the tool’s development and its key functionality.
@@
 
-Synthesis of evidence from the totality of relevant research is becoming more important than ever in informing policy across an increasingly wide range of fields.[@donnelly2018] Risk of bias assessment - evaluation of the internal validity of studies included in a systematic review - often forms a key part of the evidence synthesis process, particularly in the health sciences.[@cochranechpt7] A well-developed family of tools is widely used, which have in common the characteristic that they evaluate specific domains of bias rather being constructed as a checklist or a quantitative score.[@cochranechpt7] These tools include the RoB (Risk of Bias) 2 tool for randomized controlled  trials,[@sterne2019rob] the ROBINS-I (Risk Of Bias In Non-randomized Studies - of Interventions) tool,[@sterne2016robins] the QUADAS 2 (Quality and Applicability of Diagnostic Accuracy Studies) tool [@whiting2011quadas] and the ROBIS (Risk Of Bias in Systematic Reviews) tool.[@whiting2016robis] Within each bias domain a judgement is reached about the strength of the study in that regard: for example, the first domain in the Cochrane RoB 2 tool deals with bias arising from the randomization process.[@sterne2019rob] Accessible graphics summarizing the results of these domain-based risk-of-bias assessments are included in reports of systematic reviews.
+Synthesis of evidence from the totality of relevant research is becoming more important than ever in informing policy across an increasingly wide range of fields.[@donnelly2018] Risk of bias assessment - evaluation of the internal validity of studies included in a systematic review - often forms a key part of the evidence synthesis process, particularly in the health sciences.[@cochranechpt7] A well-developed family of tools is widely used, which have in common the characteristic that they evaluate specific domains of bias rather being constructed as a checklist or a quantitative score.[@cochranechpt7] These tools include the RoB (Risk of Bias) 2 tool for randomized trials,[@sterne2019rob] the ROBINS-I (Risk Of Bias In Non-randomized Studies - of Interventions) tool,[@sterne2016robins] the QUADAS 2 (Quality and Applicability of Diagnostic Accuracy Studies) tool [@whiting2011quadas] and the ROBIS (Risk Of Bias in Systematic Reviews) tool.[@whiting2016robis] Within each bias domain a judgement is reached about the strength of the study in that regard: for example, the first domain in the Cochrane RoB 2 tool deals with bias arising from the randomization process.[@sterne2019rob] Accessible graphics summarizing the results of these domain-based risk-of-bias assessments are included in reports of systematic reviews.
 A convenient plot in many reviews is a “traffic light” plot, which tabulates the judgement for each study in each domain.
-For larger numbers of studies, when such a table becomes unmanageable, a popular alternative is a weighted bar plot, which show the proportion of information with each judgement for each domain.[@higgins2008assessing]
+For larger numbers of studies, when such a table becomes unmanageable, a popular alternative is a (possibly weighted) bar plot, which shows the proportion of information with each judgement for each domain.[@higgins2008assessing]
 
 Researchers can face a number of barriers in creating these plots.
-While some evidence synthesis platforms, such as Cochrane’s Review Manager,[@cochrane2014review] are able to produce these visualizations, not all researchers use these systems to conduct their systematic reviews, and copying the risk-of-bias data into these systems simply to produce the plots is inefficient and error prone.
-Likewise, creating the figures by hand, through software such as MS PowerPoint or Adobe Illustrator, may lead to unintentional errors and require the plots to be redrawn during an update to the review.
+While some evidence synthesis platforms, such as Cochrane’s Review Manager,[@cochrane2014review] can produce these visualizations, not all researchers use these systems to conduct their systematic reviews, and copying the risk-of-bias data into these systems solely to produce the plots is inefficient and error prone.
+On the other hand, creating the figures "by hand", through software such as MS PowerPoint or Adobe Illustrator, may lead to unintentional errors and require the plots to be redrawn when a review is updated.
 Additionally, while the field of evidence synthesis software has grown rapidly in recent years,[@marshall2015systematic] this growth has not been equally distributed across the different aspects of the systematic review process.
@@
 
-However, it is now easier than ever to produce such a tool, thanks to the availability of powerful computing offerings including R, RStudio and `Shiny` (an R package for building interactive web apps) [@rref; @rstudioref; @shinyref] Here, we present `robvis` (Risk Of Bias VISualiation),[@mcguinness2019a] an R package and `Shiny` web-app that allows users to create publication-ready risk-of-bias plots quickly and easily.
+It is now straightforward to produce such a tool, thanks to the availability of powerful computing offerings including R, RStudio and `Shiny` (an R package for building interactive web apps) [@rref; @rstudioref; @shinyref] Here, we present `robvis` (Risk Of Bias Visualiation),[@mcguinness2019a] an R package and `Shiny` web-app that allows users to create publication-ready risk-of-bias plots quickly and easily.
 While primarily designed for use with the major risk-of-bias assessment tools used in health research (ROB2, ROBINS-I & QUADAS-2), the tool allows users to visualize the results from any domain-based risk-of-bias assessment or quality appraisal tool.
@@
 
-At the time of writing, the tool includes templates for three major tools: the Cochrane RoB 2 tool for assessing randomized controlled trials,[@sterne2019rob] the ROBINS-I tool for assessing non-randomized studies of interventions,[@sterne2016robins] and the QUADAS-2 tool for assessing diagnostic accuracy studies.[@whiting2011quadas] These templates automatically apply the correct risk-of-bias domain names to the figures, and label the judgement levels appropriately (e.g.
+At the time of writing, the tool includes templates for three major tools: the Cochrane RoB 2 tool for assessing randomized trials,[@sterne2019rob] the ROBINS-I tool for assessing non-randomized studies of interventions,[@sterne2016robins] and the QUADAS-2 tool for assessing diagnostic accuracy studies.[@whiting2011quadas] These templates automatically apply the correct risk-of-bias domain names to the figures, and label the judgement levels appropriately (e.g.
 “Low”, “Some Concerns”, “High” in the case of the RoB 2 tool).
@@
 The generic template has greater flexibility than the tool-specific templates, allowing a user-specified number of domains and custom domain titles to be used.
-It is suitable for use with the original version of the Cochrane risk-of-bias tool for randomized controlled  trials,[@higgins2011] in which flexibility in the specification of domains was permitted.
+It is suitable for use with the original version of the Cochrane risk-of-bias tool for randomized trials,[@higgins2011] in which flexibility in the specification of domains was permitted.
 Since users of more recent tools such as RoB 2 and ROBINS-I are not permitted to modify the domains, we strongly encourage use of the in-built templates for these.
@@
 In order to help users familiarize themselves with the package and its functionality, `robvis` contains built-in example datasets for each template.
-We illustrate the example data for the RoB 2 tool for assessing risk of bias in randomized controlled trials in Table  \@ref(tab:robdata).
+We illustrate the example data for the RoB 2 tool for assessing risk of bias in randomized trials in Table  \@ref(tab:robdata).
 
-### Data import and cleaning
+### Data import
 
-`robvis` expects the risk-of-bias summary table to be arranged in a specific way (see Table 1 for an example).
+`robvis` expects the risk-of-bias data file to be arranged in a specific way (see Table 1 for an example).
 The first column should contain the unique study/result identifier.
@@
 The final column contains some measure of the result’s precision (e.g.
-the weight assigned to that result in a meta-analysis, or if no meta-analysis was performed, the sample size of the analysis that produced the result).
-This weight column is used to create the summary bar plot, as current guidance recommends dividing the bars to show the proportion of information at each level of risk of bias, determined by the cumulative weight at that level, rather than simply showing the number of studies/results in each category.[@cochranechpt7]
-
-Once imported, `robvis` cleans the data, corrects for small spelling errors by converting each judgement to lowercase and taking only the first letter (e.g.
-“Seriuos  ” becomes “s”, avoiding a potential error from the misspelling), and converts the summary table to a long tidy format to aid in creating the plots.
+the weight assigned to that result in a meta-analysis, or the sample size of the analysis that produced the result).
+This weight column is used to create the summary bar plot, as current guidance recommends dividing the bars to show the proportion of information at each level of risk of bias, determined by the cumulative weight at that level, rather than simply showing the number of studies/results in each category.[@cochranechpt7] If a measure of precision is not available, or to reproduce ‘equally’ weighted bar charts as have traditionally been presented in Cochrane Reviews to date, these weights may all be specified to be 1.
 
@@
 `robvis` contains two main functions.
-The first, `rob_traffic_light()`, creates a traffic light plot by tabulating each study by each domain, providing a more detailed view of the results of the risk-of-bias assessment.
-The second, `rob_summary()`, creates a weighted bar plot  showing the proportion of information with each judgement for each domain in the assessment tool specified.
+The first, `rob_traffic_light()`, creates a _traffic light plot_.
+This displays every risk-of-bias judgement in a matrix, with domains along the horizontal and results/studies down the vertical, similar to the data set.
+The second function, `rob_summary()`, creates a _weighted bar plot_.
+This shows the proportion of information with each risk-of-bias judgement seperately for each domain in the assessment tool specified.
 
-A worked example using these functions is outlined below, showing the ease with which risk-of-bias plots can be created using `robvis`.
+A worked example using these functions is outlined below, illustrating the simple steps involved in creating risk-of-bias plots using `robvis`.
 A detailed description of the additional options that can be used with each function is presented in Table 2.
@@
 
-Using the example data set (`data_rob2`) which is built into the package and is presented in Table \@ref(tab:robdata) for reference, the traffic light plot shown in Figure \@ref(fig:trafficplot) is created using:
+Using the example data set (`data_rob2`) that is built into the package and is presented in Table \@ref(tab:robdata) for reference, the traffic light plot shown in Figure \@ref(fig:trafficplot) is created using:
 
@@
 
-The `ggplot2` package in R, based on the “The Grammar of Graphics”, allows users to create detailed graphics using a declarative framework and was used to create the templates found in `robvis`.[@ggplot2ref; @wilkinson2012grammar] As a result, both `robvis` functions return a `ggplot` object, meaning they can be easily customized further using the `ggplot2` framework.
+The `ggplot2` package in R, based on the “The Grammar of Graphics”, allows users to create detailed graphics and was used to create the templates found in `robvis`.[@ggplot2ref; @wilkinson2012grammar] As a result, both `robvis` functions return a `ggplot` object, meaning they can be easily customized further using the `ggplot2` framework.
 For example, to add a title to the summary bar plot:
@@
 
-Although `robvis` was originally designed for use in the command-line–based R programming environment, we developed a web app to make the tool available to those without knowledge of R.
+Although `robvis` was originally designed for use in the command-line–based R programming environment, we developed a web app to make the tool accessible to those without knowledge of R.
 This is available via [www.riskofbias.info](https://www.riskofbias.info).[@robviswebapp] The app was built using `Shiny`,[@shinyref] an R package which makes it easy to produce interactive web-apps, and provides a graphical user interface (GUI) for the `robvis` package, allowing users to interact with the functions presented above without the need to download R or type any commands.
@@
 Uploaded data are passed through a number of quality control checks that ensure the app will work correctly, and users are prevented from producing the plots until any issues identified have been addressed.
-Finally, users can customise their plots by defining a colour scheme and other parameters, all through the online app.
+Finally, users can customize their plots by defining a colour scheme and other parameters, all through the online app.
 
@@
 The RoB2 (`tool=\"ROB2\"`), ROBINS-I (`tool=\"ROBINS-I\"`), and QUADAS-2 (`tool=\"QUADAS-2\"`) assessments tools are currently supported.
-Other tools can be visualised using the generic template (`tool = \"Generic\"`) [Note 1]",
+Other tools can be visualized using the generic template (`tool = \"Generic\"`) [Note 1]",
 "Defines the colour scheme for the plot.
@@
 
-``` {r trafficplot, echo = FALSE, eval = TRUE, fig.cap = "Example risk of bias traffic light plot of ROB2 assessments created using `robvis`"}
+``` {r trafficplot, echo = FALSE, eval = TRUE, fig.cap = "Example risk of bias traffic light plot of ROB2 assessments created using `robvis` and the colourblind palette."}
 
@@
 
-``` {r summaryplot, echo = FALSE, eval = TRUE, fig.cap = "Example risk of bias summary plot of ROB2 assessments created using `robvis`"}
+``` {r summaryplot, echo = FALSE, eval = TRUE, fig.cap = "Example risk of bias summary plot of ROB2 assessments created using `robvis` and the standard Cochrane palette."}
 

### 2020-04-20 RSM-paper/manuscript.Rmd
Add new versions of RSM paper Includes accepted version (RSM Revision Submitted)

@@
 ---
-title: "RSM - Call for papers on data visualization"
+title: ""
 bibliography: references.bib
@@
 __Title: __  
-Risk-Of-Bias VISualization (robvis): an R package and Shiny web app for visualizing risk-of-bias assessments
+Risk-Of-Bias VISualization (`robvis`): an R package and Shiny web app for visualizing risk-of-bias assessments
 
@@
 
-__Authors and Affliations__
+__Authors and Affiliations__
 
@@
 
-Risk of bias; Evidence synthesis; Data visualisation; R
+Risk of bias; Evidence synthesis; Data visualization; R
 
@@
 
-It is now straightforward to produce such a tool, thanks to the availability of powerful computing offerings including R, RStudio and `Shiny` (an R package for building interactive web apps) [@rref; @rstudioref; @shinyref] Here, we present `robvis` (Risk Of Bias Visualiation),[@mcguinness2019a] an R package and `Shiny` web-app that allows users to create publication-ready risk-of-bias plots quickly and easily.
+It is now straightforward to produce such a tool, thanks to the availability of powerful computing offerings including R, RStudio and `Shiny` (an R package for building interactive web apps) [@rref; @rstudioref; @shinyref] Here, we present `robvis` (Risk Of Bias VISualization),[@mcguinness2019a] an R package and `Shiny` web-app that allows users to create publication-ready risk-of-bias plots quickly and easily.
 While primarily designed for use with the major risk-of-bias assessment tools used in health research (ROB2, ROBINS-I & QUADAS-2), the tool allows users to visualize the results from any domain-based risk-of-bias assessment or quality appraisal tool.
@@
 
-In order to help users familiarize themselves with the package and its functionality, `robvis` contains built-in example datasets for each template.
+In order to help users familiarize themselves with the package and its functionality, `robvis` contains built-in example data-sets for each template.
 We illustrate the example data for the RoB 2 tool for assessing risk of bias in randomized trials in Table  \@ref(tab:robdata).
@@
 The second function, `rob_summary()`, creates a _weighted bar plot_.
-This shows the proportion of information with each risk-of-bias judgement seperately for each domain in the assessment tool specified.
+This shows the proportion of information with each risk-of-bias judgement separately for each domain in the assessment tool specified.
 
@@
 At present, the number of tools with a specific template included in `robvis` is limited - adding additional templates is a priority.
-For example, a template for ROBIS, the risk-of-bias assessment tool for systematic reviews,[@whiting2016robis] is in developement.
+For example, a template for ROBIS, the risk-of-bias assessment tool for systematic reviews,[@whiting2016robis] is in development.
 Additionally, the `robvis` tool does not yet allow for the production of paired forest plots, where the risk-of-bias judgement is presented alongside each specific result included in the meta-analysis.[@cochranechpt7] This was initially considered to be beyond the scope of the tool, as it involves the visualization of something other than risk-of-bias assessments.
@@
 `colour = c(\"#f442c8\", \"#bef441\", \"#000000\")`",
-"Defines whether to include an additional bar showing the distibution of overall risk of bias judgements in the summary barplot figure. Default is `overall = FALSE`.",
+"Defines whether to include an additional bar showing the distribution of overall risk of bias judgments in the summary barplot figure. Default is `overall = FALSE`.",
 "Defines whether weights should be used to produce the summary barplot figure. Default is `weighted = TRUE`, in line with current Cochrane Collaboration guidance.",

### 2020-04-28 README.Rmd
Range of updates Add final submitted version of the manuscript Add DOI to README

@@
 [![CRAN Downloads.](https://cranlogs.r-pkg.org/badges/last-month/robvis)](https://cran.r-project.org/web/packages/robvis/index.html)
-[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.3552342.svg)](https://doi.org/10.5281/zenodo.3552342)
 <br>
@@
 <br>
+[![DOI](https://img.shields.io/static/v1.svg?label=Publication&message=10.1002/jrsm.1411&color=informational)](https://doi.org/10.1002/jrsm.1411)
 [![metaverse Identifier](https://img.shields.io/static/v1.svg?label=Part%20of%20the&message=metaverse&color=informational)](https://www.github.com/rmetaverse/metaverse)

### 2020-09-07 tests/testthat/test_errors.R
Major updates to existing tests, plus added new test for new functions

@@ -2,19 +2,25 @@ context("Check error messages")
 
 # Tool must be specified
 test_that("No tool specified", {
-          expect_error(rob_summary(data_rob2))
-          expect_error(rob_traffic_light(data_rob2))
-          })
+  expect_error(rob_summary(data_rob2))
+  expect_error(rob_traffic_light(data_rob2))
+})
 
 test_that("Tool specified incorrectly", {
-  expect_error(rob_summary(data_rob2,"Rob2"))
+  expect_error(rob_summary(data_rob2, "Rob2"))
   expect_error(rob_traffic_light(data_rob2, "Rob2"))
 })
 
-# test_that("Colour errors", {
-#           expect_error(rob_summary(data_rob2, "ROB2", colour = c("#FFFFFF")))
-#           expect_error(rob_traffic_light(data_rob2,"ROB2", colour = c("#FFFFFF")))
-# })
+
+test_that("ROB1 gives message", {
+  expect_message(rob_summary(data_rob1, "ROB1"))
+  expect_message(rob_traffic_light(data_rob1, "ROB1"))
+})
+
+test_that("Colour errors", {
+          expect_error(rob_summary(data_rob2, "ROB2", colour = c("#FFFFFF")))
+          expect_error(rob_traffic_light(data_robins,"ROBINS-I", colour = c("#FFFFFF")))
+})
 
 test_sum <- data_rob2[, c(1:7)]
 test_tf <- data_rob2[, c(1:6)]
@@ -38,6 +44,10 @@ test_tf <- data_quadas[, c(1:5)]
 test_that("Too few columns", {
   expect_error(rob_summary(test_sum, "QUADAS-2"))
   expect_error(rob_traffic_light(test_tf, "QUADAS-2"))
+})
+
+test_that("Error on saving with wrong file ext",{
+  expect_error(rob_save(rob_fig,"test.pgg"))
 })
 
 # Need to add specific test for ROB1

### 2020-09-07 tests/testthat/test_helpers.R

@@ -1,0 +1,8 @@
+test_that("Correct number of colours returned", {
+  expect_equal(length(get_colour("ROB2", "cochrane")), 5)
+  expect_equal(length(get_colour("ROB2", "colourblind")), 5)
+})
+
+test_that("Convert weird spelling of colour", {
+  expect_equal(weird_spelling("colorblind"), "colourblind")
+})

### 2020-09-07 tests/testthat/test_rob_save.R

@@ -1,0 +1,41 @@
+rob_fig <- rob_traffic_light(data_rob2, "ROB2")
+
+rob_save(rob_fig,"test.png")
+
+test_that("Test PNG download", {
+  expect_equal(file.exists("test.png"),TRUE)
+})
+
+if (file.exists("test.png") == TRUE) {
+  unlink("test.png", recursive = TRUE)
+}
+
+rob_save(rob_fig,"test.jpeg")
+
+test_that("Test jpeg download", {
+  expect_equal(file.exists("test.jpeg"),TRUE)
+})
+
+if (file.exists("test.jpeg") == TRUE) {
+  unlink("test.jpeg", recursive = TRUE)
+}
+
+rob_save(rob_fig,"test.tiff")
+
+test_that("Test tiff download", {
+  expect_equal(file.exists("test.tiff"),TRUE)
+})
+
+if (file.exists("test.tiff") == TRUE) {
+  unlink("test.tiff", recursive = TRUE)
+}
+
+rob_save(rob_fig,"test.eps")
+
+test_that("Test eps download", {
+  expect_equal(file.exists("test.eps"),TRUE)
+})
+
+if (file.exists("test.eps") == TRUE) {
+  unlink("test.eps", recursive = TRUE)
+}

### 2020-09-07 tests/testthat/test_rob_traffic_light.R

@@ -1,39 +1,34 @@
 context("rob_traffic_light()")
 
-test_that("ROB - Traffic light",{
+test_that("ROB - Traffic light", {
 
-skip_on_cran()
-# skip_on_travis()
-# skip_on_appveyor()
+  vdiffr::expect_doppelganger("TF - ROB2 - Basic", rob_traffic_light(data_rob2, "ROB2", psize = 20))
+  vdiffr::expect_doppelganger("TF - ROB2 - Point Size", rob_traffic_light(data_rob2, "ROB2", psize = 10))
+  vdiffr::expect_doppelganger("TF - ROB2 - Colour - cochrane", rob_traffic_light(data_rob2, "ROB2", colour = "cochrane", psize = 20))
+  vdiffr::expect_doppelganger("TF - ROB2 - Colour - colourblind", rob_traffic_light(data_rob2, "ROB2", colour = "colourblind", psize = 20))
+  vdiffr::expect_doppelganger("TF - ROB2 - Colour - custom", rob_traffic_light(data_rob2, "ROB2", psize = 20, colour = c("#f442c8", "#bef441", "#000000", "#333333")))
 
-vdiffr::expect_doppelganger("TF - ROB2 - Basic", rob_traffic_light(data_rob2,"ROB2"))
-vdiffr::expect_doppelganger("TF - ROB2 - Point Size", rob_traffic_light(data_rob2,"ROB2", psize = 10))
-vdiffr::expect_doppelganger("TF - ROB2 - Colour - cochrane", rob_traffic_light(data_rob2,"ROB2", colour = "cochrane"))
-vdiffr::expect_doppelganger("TF - ROB2 - Colour - colourblind", rob_traffic_light(data_rob2,"ROB2", colour = "colourblind"))
-vdiffr::expect_doppelganger("TF - ROB2 - Colour - custom", rob_traffic_light(data_rob2,"ROB2", colour = c("#f442c8","#bef441","#000000","#333333")))
+  vdiffr::expect_doppelganger("TF - ROB2C - Basic", rob_traffic_light(data_rob2_cluster, "ROB2-Cluster", psize = 20))
+  vdiffr::expect_doppelganger("TF - ROB2C - Point Size", rob_traffic_light(data_rob2_cluster, "ROB2-Cluster", psize = 10))
[…]

### 2020-09-07 R/rob_paired_plot.R
Remove rob_paired_plot file

@@ -1,42 +1,0 @@
-#' Produce forest plots with risk of bias results
-#' @description A function to take a summary table of risk of bias assessments and produce a traffic light plot from it.
-#' @param data A dataframe containing summary (domain) level risk-of-bias assessments, with the first column containing the study details, the second column containing the first domain of your assessments, and the final column containing a weight to assign to each study. The function assumes that the data includes a column for overall risk-of-bias. For example, a ROB2.0 dataset would have 8 columns (1 for study details, 5 for domain level judgements, 1 for overall judgements, and 1 for weights, in that order).
-#' @export
-
-
-rob_paired_plot <- function(data, tool, colour = "cochrane",
-                              psize = 20, quiet = FALSE) {
-
-  judgement <- NULL
-  Study <- NULL
-  domain <- NULL
-
-
-  # Define colouring
-  if (length(colour) > 1) {
-    rob_colours$low_colour <- colour[c(1)]
-    rob_colours$concerns_colour <- colour[c(2)]
-    rob_colours$high_colour <- colour[c(3)]
-    rob_colours$critical_colour <- colour[c(4)]
-  } else {
-    if (colour == "colourblind") {
-      rob_colours$low_colour <- "#fef0d9"
-      rob_colours$concerns_colour <- "#fdcc8a"
-      rob_colours$high_colour <- "#fc8d59"
-      rob_colours$critical_colour <- "#d7301f"
-    }
-    if (colour == "cochrane") {
-      rob_colours$low_colour <- "#02C100"
-      rob_colours$concerns_colour <- "#E2DF07"
-      rob_colours$high_colour <- "#BF0000"
-      rob_colours$critical_colour <- "#820000"
-    }
-  }
-
-
-  myCsv <- getURL("https://docs.google.com/spreadsheet/pub?key=0AvykV4O1IaendFRSQVVVV3pYN3JZRlNKSzBud0FFa1E&output=csv")
-
-
-
-
-}

### 2020-09-07 R/helpers.R
Range of edits including - Add pkgdown keywords - Add new supporting funtions to helpers.R - Split out rob_summary.R into component parts - Finalise rob_save.R

@@ -1,8 +1,23 @@
-get_colour <- function(tool, colour){
+# Check colours
+check_colour <- function(tool, colour) {
+  if(!(colour[1] %in% c("cochrane","colourblind"))){
+    if (tool == "ROB2" || tool == "ROB2-Cluster" || tool == "QUADAS-2") {
+      if(length(colour)!=4){
+        stop("Wrong number of colours specified. This template expects 4 colours.")
+      }
 
+    } else{
+      if(length(colour)!=5){
+        stop("Wrong number of colours specified. This template expects 5 colours.")
+      }
+    }
+  }
+}
+
+# Define colours used
+get_colour <- function(tool, colour) {
   rob_colours <- c()
 
-  # Define colours
   rob_colours$na_colour <- "#cccccc"
 
   if (tool == "ROB2" || tool == "ROB2-Cluster" || tool == "QUADAS-2") {
@@ -25,7 +40,7 @@ get_colour <- function(tool, colour){
         rob_colours$ni_colour <- "#4EA1F7"
       }
     }
-  }else{
+  } else {
     if (length(colour) > 1) {
       rob_colours$low_colour <- colour[c(1)]
       rob_colours$concerns_colour <- colour[c(2)]
@@ -53,26 +68,83 @@ get_colour <- function(tool, colour){
   return(rob_colours)
 }
 
-get_height <- function(data, tool, psize = 15, type = "tf"){
+# Make sure specified tool is allowed
+check_tool <- function(tool) {
+  tools <- c(suppressMessages(rob_tools()), "ROB1")
+
+  if ((tool %in% tools) == FALSE) {
+    stop(
+      paste(
+        "\nTool name \"",
+        tool,
+        "\" not recognised \nAcceptable tools names can be found using the rob_tools() function"
+      )
+    )
+  }
+}
+
+# Give depreciated warning if "ROB1" specified
+rob1_warning <- function(tool) {
+  if (tool == "ROB1") {
+    message(
+      paste0(
+        "Note: In future versions of robvis, the 'tool = \"ROB1\"' ",
+        "argument will be depreciated.\n",
+        "Please use 'tool = \"Generic\"' instead."
+      )
+    )
+  }
+}
+
+# Get recommended height of figure, used by rob_save
+get_height <- function(data, tool, psize, type = "tf") {
   if (type == "tf") {
-    tool_adj <- ifelse(tool %in% c("ROBINS-I","Generic"), 2.5, 2)
[…]

### 2020-09-07 R/rob_save.R

@@ -1,0 +1,36 @@
+#' Save ROB plots to a file using sensible parameters
+#'
+#' @param rob_object Object created using either rob_summary() or
+#'   rob_traffic_light()
+#' @param file Destination file, with extension (e.g. "rob_figure.png")
+#' @param height Height of resulting image, in inches. Defaults to "default"
+#'   which uses recommended values based on the number of studies included.
+#' @param width Width of resulting image, in inches. Defaults to "default" which
+#'   uses recommended values based on the number of characters in the Study and
+#'   Domain names. dpi
+#' @param dpi Plot resolution.
+#'
+#' @family helper
+#' @export
+
+rob_save <- function(rob_object,
+                     file = "rob_figure.png",
+                     height = "default",
+                     width = "default",
+                     dpi = 800) {
+
+  check_extension(file)
+
+  width <- ifelse(width == "default", rob_object$rec_width, width)
+  height <- ifelse(height == "default", rob_object$rec_height, height)
+
+  ggplot2::ggsave(
+    file,
+    plot = rob_object,
+    width = width,
+    height = height,
+    units = "in",
+    dpi = dpi,
+    limitsize = FALSE
+  )
+}

### 2020-09-07 R/rob_summary.R

@@ -3,638 +3,767 @@
 #' @param data A dataframe containing summary (domain) level risk-of-bias assessments, with the first column containing the study details, the second column containing the first domain of your assessments, and the final column containing a weight to assign to each study. The function assumes that the data includes a column for overall risk-of-bias. For example, a ROB2.0 dataset would have 8 columns (1 for study details, 5 for domain level judgments, 1 for overall judgements, and 1 for weights, in that order).
 #' @param tool The risk of bias assessment tool used. RoB2.0 (tool='ROB2'), ROBINS-I (tool='ROBINS-I'), and QUADAS-2 (tool='QUADAS-2') are currently supported.
 #' @param overall An option to include a bar for overall risk-of-bias in the figure. Default is FALSE.
-#' @param quiet An option to quietly produce the plot without displaying it.
 #' @param colour An argument to specify the colour scheme for the plot. Default is 'cochrane' which used the ubiquitous Cochrane colours, while a preset option for a colour-blind friendly palette is also available (colour = 'colourblind').
 #' @param weighted An option to specify whether weights should be used in the barplot. Default is TRUE, in line with current Cochrane Collaboration guidance.
 #' @return Risk of bias assessment barplot figure.
+#' @family main
 #' @examples
 #'
-#' data <- data.frame(stringsAsFactors=FALSE,
-#'                    Study = c("Study 1", "Study 2"),
-#'                    D1 = c("Low", "Some concerns"),
-#'                    D2 = c("Low", "Low"),
-#'                    D3 = c("Low", "Low"),
-#'                    D4 = c("Low", "Low"),
-#'                    D5 = c("Low", "Low"),
-#'                    Overall = c("Low", "Low"),
-#'                    Weight = c(33.33333333, 33.33333333)
-#'                    )
+#' data <- data.frame(
+#'   stringsAsFactors = FALSE,
+#'   Study = c("Study 1", "Study 2"),
+#'   D1 = c("Low", "Some concerns"),
+#'   D2 = c("Low", "Low"),
+#'   D3 = c("Low", "Low"),
+#'   D4 = c("Low", "Low"),
+#'   D5 = c("Low", "Low"),
+#'   Overall = c("Low", "Low"),
+#'   Weight = c(33.33333333, 33.33333333)
+#' )
 #'
 #' rob_summary(data, "ROB2")
-#'
 #' @export
 
-rob_summary <-
-  function(data,
-           tool,
-           overall = FALSE,
[…]

### 2020-09-07 R/rob_traffic_light.R

@@ -8,172 +8,185 @@
 #' @param ... Arguments to be passed to the tool specific functions.
 #'
 #' @return Risk-of-bias assessment traffic light plot (ggplot2 object)
+#' @family main
 #' @examples
 #'
-#' data <- data.frame(stringsAsFactors=FALSE,
-#'                    Study = c("Study 1", "Study 2"),
-#'                    D1 = c("Low", "Some concerns"),
-#'                    D2 = c("Low", "Low"),
-#'                    D3 = c("Low", "Low"),
-#'                    D4 = c("Low", "Low"),
-#'                    D5 = c("Low", "Low"),
-#'                    Overall = c("Low", "Low"),
-#'                    Weight = c(33.33333333, 33.33333333)
-#'                    )
+#' data <- data.frame(
+#'   stringsAsFactors = FALSE,
+#'   Study = c("Study 1", "Study 2"),
+#'   D1 = c("Low", "Some concerns"),
+#'   D2 = c("Low", "Low"),
+#'   D3 = c("Low", "Low"),
+#'   D4 = c("Low", "Low"),
+#'   D5 = c("Low", "Low"),
+#'   Overall = c("Low", "Low"),
+#'   Weight = c(33.33333333, 33.33333333)
+#' )
 #'
 #' rob_traffic_light(data, "ROB2")
-#'
 #' @export
 
-rob_traffic_light <- function(data, tool, colour = "cochrane",psize = 20, ...) {
+rob_traffic_light <- function(data, tool, colour = "cochrane", psize = 10, ...) {
 
-    # Allow for depreciated "ROB1" argument
-    tools <- c(rob_tools(),"ROB1")
+  check_tool(tool)
+  colour <- weird_spelling(colour)
 
-    if((tool %in% tools)==FALSE) {
-      stop(
-        paste("\nTool name \"",
-              tool,
-              "\" not recognised \nAcceptable tools names can be found using the rob_tools() function")
-     )
-    }
+  check_colour(tool = tool, colour = colour)
+  # Define colours
+  rob_colours <- get_colour(tool = tool, colour = colour)
 
-
-    # Define colours
-    rob_colours <- get_colour(tool = tool, colour = colour)
-
-
-    if (tool == "ROB2") {
-      plot <- rob_traffic_light_rob2(
-        data = data,
-        tool = tool,
-        rob_colours = rob_colours,
-        psize = psize
-      )
-    }
-
-    if (tool == "ROB2-Cluster") {
[…]

### 2020-09-07 R/robvis.R

@@ -4,5 +4,6 @@
 #' risk-of-bias assessment figures.
 #' @docType package
 #' @name robvis
+#' @keywords internal
 
-globalVariables(c("domain", "Study","judgement"))
+globalVariables(c("domain", "Study", "judgement", "Weights"))

### 2020-09-07 R/data_quadas.R
Add pkgdown internal keyword

@@ -11,4 +11,5 @@
 #'   \item{Weight}{Weight measure for each study}
 #'          }
 #' @source {Created for this package}
+#' @keywords internal
 "data_quadas"

### 2020-09-07 R/data_rob1.R

@@ -14,4 +14,6 @@
 #'   \item{Weight}{Weight measure for each study}
 #'          }
 #' @source {Created for this package}
+#' @keywords internal
+
 "data_rob1"

### 2020-09-07 README.Rmd

@@
 
-Install the CRAN version:
-```{r, eval=FALSE}
-install.packages("robvis")
-```
-
-Alternatively, the development version can be installed using:
+Install the development version which contains new functionality and a range of bug fixes:
 
@@
 To update the package, run the `install_github("mcguinlu/robvis")` command again.
+
+If you wish to use the older CRAN version of the package, use the following command:
+
+```{r, eval=FALSE}
+install.packages("robvis")
+```
 
@@
 trafficlight_rob <- rob_traffic_light(data = data_rob2, tool = "ROB2")
-ggplot2::ggsave(
-          "man/figures/rob2trafficlight.png",
-          plot = trafficlight_rob,
-          device = "png",
-          width = 6,
-          height = 9,
-          units = "in",
-          dpi = 800, 
-          limitsize = FALSE)
+rob_save(trafficlight_rob,"man/figures/rob2trafficlight.png")
 ```
@@
 ### Other functions
+
+#### rob_save()
+Pass the `robvis` to this function, along with a destination file, to save your risk-of-bias plots using sensible defaults.
+
+```{r, eval = FALSE}
+rob_save(trafficlight_rob, "rob_fig.png")
+```
+
 #### rob_tools()
@@
 
+```{r}
 rob_tools()
-    [1] "ROB2"
-    [1] "ROBINS-I"
-    [1] "QUADAS-2"
-    [1] "ROB1"
+```
 
@@
 ```{r, fig.height=3}
-summary_rob <- rob_summary(data = data_rob2, tool = "ROB2", colour = c("#f442c8","#bef441","#000000"))
+summary_rob <- rob_summary(data = data_rob2, tool = "ROB2", colour = c("#f442c8","#bef441","#000000","#d16684"))
 summary_rob
@@
 
+See more [here](https://scholar.google.com/scholar?cites=12564214960529060925&as_sdt=2005&sciodt=0,5&hl=en).
+
 ## Code of conduct

### 2020-10-30 README.Rmd

@@
 ```{r, fig.height=3}
-summary_rob <- rob_summary(data = data_rob2, tool = "ROB2", colour = "colourblind")
+summary_rob <- rob_summary(data = data_rob2,
+                           tool = "ROB2",
+                           colour = "colourblind")
 summary_rob
@@
 ```{r, fig.height=3}
-summary_rob <- rob_summary(data = data_rob2, tool = "ROB2", colour = c("#f442c8","#bef441","#000000","#d16684"))
+summary_rob <- rob_summary(data = data_rob2,
+                           tool = "ROB2",
+                           colour = c("#f442c8",
+                                      "#bef441",
+                                      "#000000",
+                                      "#d16684"))
 summary_rob

### 2020-10-30 README.Rmd
Update R CMD check badge

@@
 <br>
-[![Build Status](https://img.shields.io/travis/mcguinlu/robvis.svg?label=build&logo=travis&branch=master)](https://travis-ci.com/mcguinlu/robvis) 
-[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/mcguinlu/robvis?branch=master&svg=true)](https://ci.appveyor.com/project/mcguinlu/robvis)
+[![R build status](https://github.com/mcguinlu/robvis/workflows/R-CMD-check/badge.svg)](https://github.com/mcguinlu/robvis/actions)
 [![Codecov test coverage](https://codecov.io/gh/mcguinlu/robvis/branch/master/graph/badge.svg)](https://codecov.io/gh/mcguinlu/robvis?branch=master)

### 2020-11-11 README.Rmd

@@
 [![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)
-[![CRAN Badge.](https://www.r-pkg.org/badges/version-ago/robvis)](https://cran.r-project.org/web/packages/robvis/index.html)
-[![CRAN Downloads.](https://cranlogs.r-pkg.org/badges/last-month/robvis)](https://cran.r-project.org/web/packages/robvis/index.html)
+[![CRAN Badge.](https://www.r-pkg.org/badges/version-ago/robvis)](https://CRAN.R-project.org/package=robvis)
+[![CRAN Downloads.](https://cranlogs.r-pkg.org/badges/last-month/robvis)](https://CRAN.R-project.org/package=robvis)
 <br>
@@
 ```{r, eval=FALSE}
-trafficlight_rob <- rob_traffic_light(data = data_rob2, tool = "ROB2")
+trafficlight_rob <- rob_traffic_light(data = data_rob2,
+                                      tool = "ROB2",
+                                      psize = 10)
 trafficlight_rob
@@
 ``` {r, include=FALSE}
-trafficlight_rob <- rob_traffic_light(data = data_rob2, tool = "ROB2")
+trafficlight_rob <- rob_traffic_light(data = data_rob2,
+                                      tool = "ROB2",
+                                      psize = 10)
 rob_save(trafficlight_rob,"man/figures/rob2trafficlight.png")

### 2020-12-03 R/helpers.R
New functionality to better handle weighted and overall options, plus tests

@@ -1,7 +1,106 @@
+check_cols <- function(data,
+                       max_domain_column,
+                       overall,
+                       type = "tf",
+                       weight = FALSE){
+
+  expected_col <- max_domain_column + 1
+
+  if (!overall & !weight) {
+    expected_col <- expected_col - 2
+    domain_text = paste0(expected_col,
+                         ": a \"Study\" column and ",
+                         max_domain_column - 2,
+                         " \"Domain\" columns.")
+    var_ind <- "neither"
+
+  }
+
+  if (!overall & weight) {
+    expected_col <- expected_col - 1
+    domain_text = paste0(
+      expected_col,
+      ": a \"Study\" column, ",
+      max_domain_column - 1,
+      " \"Domain\" columns, and \"Weight\" column."
+    )
+    var_ind <- "weight"
+  }
+
+  if (overall & !weight) {
+    expected_col <- expected_col - 1
+    domain_text = paste0(
+      expected_col,
+      ": a \"Study\" column, ",
+      max_domain_column - 1,
+      " \"Domain\" columns, and an \"Overall\" column."
+    )
+    var_ind <- "overall"
+  }
+
+  if (overall & weight) {
+    expected_col <- expected_col
+    domain_text = paste0(
+      expected_col,
+      ": a \"Study\" column, ",
+      max_domain_column - 2,
+      " \"Domain\" columns, an \"Overall\" column and a \"Weight\" column."
+    )
+    var_ind <- "both"
+  }
+
+  if (type == "summ") {
+    weighted_text <- paste(" and weighted =", weight)
+  } else {
+    weighted_text <- ""
+  }
+
+  if (ncol(data) == expected_col) {
+    if ((var_ind %in% c("both", "weight")) &&
+        unique(grepl("^[-]{0,1}[0-9]{0,}.{0,1}[0-9]{1,}$",
+                     data[[ncol(data)]])) == FALSE) {
+      stop(
+        "Error. The final column does not seem to contain numeric values ",
+        "(expected for weighted = TRUE)."
+      )
+    }} else {
+      if (ncol(data) != expected_col) {
+      stop(
+        "The number of columns in your data (",
+        ncol(data),
+        ") does not match the number expected for this",
+        " tool when using overall = ", overall, weighted_text,
+        ". The expected number of columns is ",
+        domain_text
+      )}
+    }
+  }
+
+
 tidy_data <- function(data,
                       max_domain_column,
[…]

### 2020-12-03 tests/testthat/test_errors.R

@@ -1,6 +1,6 @@
 context("Check error messages")
 
-# Tool must be specified
+# Tools ----
 test_that("No tool specified", {
   expect_error(rob_summary(data_rob2))
   expect_error(rob_traffic_light(data_rob2))
@@ -11,52 +11,65 @@ test_that("Tool specified incorrectly", {
   expect_error(rob_traffic_light(data_rob2, "Rob2"))
 })
 
-
 test_that("ROB1 gives message", {
   expect_message(rob_summary(data_rob1, "ROB1"))
   expect_message(rob_traffic_light(data_rob1, "ROB1"))
 })
+
+# Colours ----
 
 test_that("Colour errors", {
           expect_error(rob_summary(data_rob2, "ROB2", colour = c("#FFFFFF")))
           expect_error(rob_traffic_light(data_robins,"ROBINS-I", colour = c("#FFFFFF")))
 })
 
-test_sum <- data_rob2[, c(1:7)]
+# Columns ----
+
+test_sum <- data_rob2[, c(1:6)]
+
+test_that("Wrong number of columns - summary", {
+  expect_error(
+    rob_summary(test_sum, "ROB2", overall = TRUE, weighted = FALSE),
+    "an \"Overall\" column."
+  )
+  expect_error(
+    rob_summary(test_sum, "ROB2", overall = FALSE, weighted = TRUE),
+    "columns, and \"Weight\" column"
+  )
+  expect_error(
+    rob_summary(test_sum, "ROB2", overall = TRUE, weighted = TRUE),
+    "an \"Overall\" column and a \"Weight\" column."
+  )
+
+  expect_error(
+    rob_summary(data_rob2[, c(1:5)], "ROB2", overall = FALSE, weighted = FALSE),
+    "\"Domain\" columns."
+  )
+})
+
+test_that("Last column not weights - summary", {
+  expect_error(
+    rob_summary(data_rob2[, c(1:7)], "ROB2", overall = FALSE, weighted = TRUE),
+    "expected for weighted = TRUE"
+  )
+  expect_error(
+    rob_summary(data_rob2[, c(1:7)], "Generic", overall = FALSE, weighted = TRUE),
+    "expected for weighted = TRUE"
+  )
+})
+
 test_tf <- data_rob2[, c(1:6)]
 
-test_that("Too few columns", {
-  expect_error(rob_summary(test, "ROB2"))
-  expect_error(rob_traffic_light(test, "ROB2"))
[…]

### 2020-12-03 tests/testthat/test_rob_summary.R

@@ -1,41 +1,39 @@
 context("Check summary plots")
 
 test_that("ROB - Summary", {
-  vdiffr::expect_doppelganger("ROB2 - Basic", rob_summary(data_rob2, "ROB2"))
-  vdiffr::expect_doppelganger("ROB2 - Weighted", rob_summary(data_rob2, "ROB2", weighted = FALSE))
-  vdiffr::expect_doppelganger("ROB2 - Overall", rob_summary(data_rob2, "ROB2", overall = TRUE))
-  vdiffr::expect_doppelganger("ROB2 - Colour - cochrane", rob_summary(data_rob2, "ROB2", colour = "cochrane"))
-  vdiffr::expect_doppelganger("ROB2 - Colour - colourblind", rob_summary(data_rob2, "ROB2", colour = "colourblind"))
-  vdiffr::expect_doppelganger("ROB2 - Colour - custom", rob_summary(data_rob2, "ROB2", colour = c("#f442c8", "#bef441", "#000000", "#bef441")))
+  vdiffr::expect_doppelganger("ROB2 - Basic", rob_summary(data_rob2, "ROB2", overall = FALSE, weighted = TRUE))
+  vdiffr::expect_doppelganger("ROB2 - Weighted", rob_summary(data_rob2, "ROB2", weighted = FALSE, overall = FALSE))
+  vdiffr::expect_doppelganger("ROB2 - Overall", rob_summary(data_rob2, "ROB2", weighted = TRUE))
+  vdiffr::expect_doppelganger("ROB2 - Colour - cochrane", rob_summary(data_rob2, "ROB2", colour = "cochrane", overall = FALSE, weighted = TRUE))
+  vdiffr::expect_doppelganger("ROB2 - Colour - colourblind", rob_summary(data_rob2, "ROB2", colour = "colourblind", overall = FALSE, weighted = TRUE))
+  vdiffr::expect_doppelganger("ROB2 - Colour - custom", rob_summary(data_rob2, "ROB2", colour = c("#f442c8", "#bef441", "#000000", "#bef441"), overall = FALSE, weighted = TRUE))
 
+  vdiffr::expect_doppelganger("ROB1 - Basic", rob_summary(data_rob1, "Generic", overall = FALSE, weighted = TRUE))
+  vdiffr::expect_doppelganger("ROB1 - Weighted", rob_summary(data_rob1, "Generic", weighted = FALSE, overall = FALSE))
[…]

### 2020-12-03 README.Rmd
Update README

@@
   fig.height=3)
+
+fig_count <- 1
 ```
@@
 #### 1. rob_summary()
-Returns a ggplot object displaying a weighted barchart of the risk of bias of included studies across the domains of the specified tool.
+Returns a ggplot object displaying a barchart of the risk of bias of included studies across the domains of the specified tool.
+[*Note: the defaults used in this function have changed from their original settings, so that a un-weighted barplot is now produced by default.
+See the NEWS.md file for further information.*]
 
-```{r, fig.height=3}
+```{r, eval = FALSE}
 summary_rob <- rob_summary(data = data_rob2, tool = "ROB2")
+
 summary_rob
 ```
+
+``` {r, echo = FALSE}
+plot <- rob_summary(data = data_rob2, tool = "ROB2")
+file = paste0("man/figures/robplot",fig_count,".png")
+rob_save(plot, file)
+fig_count <- fig_count + 1
+```
+<div style="text-align:center"><img src=`r file` width="70%" height="70%"/></div>
 
@@
                                       psize = 10)
+
 trafficlight_rob
@@
 
-``` {r, include=FALSE}
-trafficlight_rob <- rob_traffic_light(data = data_rob2,
+``` {r, echo = FALSE}
+plot <- rob_traffic_light(data = data_rob2,
                   tool = "ROB2",
                   psize = 10)
-rob_save(trafficlight_rob,"man/figures/rob2trafficlight.png")
+file = paste0("man/figures/robplot",fig_count,".png")
+rob_save(plot, file)
+fig_count <- fig_count + 1
 ```
-<div style="text-align:center"><img src="man/figures/rob2trafficlight.png" width="70%" height="70%"/></div>
+<div style="text-align:center"><img src=`r file` width="70%" height="70%"/></div>
 
@@
 
-```{r, fig.height=3}
-summary_rob <- rob_summary(data = data_rob2,
+```{r, eval=FALSE}
+rob_summary(data = data_rob2,
             tool = "ROB2",
             colour = "colourblind")
-summary_rob
+
 ```
 
+``` {r, echo = FALSE}
+plot <- rob_summary(data = data_rob2,
+                           tool = "ROB2",
+                           colour = "colourblind")
+file = paste0("man/figures/robplot",fig_count,".png")
+rob_save(plot, file)
+fig_count <- fig_count + 1
+```
+<div style="text-align:center"><img src=`r file` width="70%" height="70%"/></div>
+
 And to define your own colour scheme:
-```{r, fig.height=3}
-summary_rob <- rob_summary(data = data_rob2,
+```{r, eval=FALSE}
+rob_summary(
+  data = data_rob2,
+  tool = "ROB2",
+  colour = c("#f442c8",
+             "#bef441",
+             "#000000",
+             "#d16684")
+)
+
+```
+
+``` {r, echo = FALSE}
+plot <- rob_summary(data = data_rob2,
                            tool = "ROB2",
@@
                                       "#d16684"))
+file = paste0("man/figures/robplot",fig_count,".png")
+rob_save(plot, file)
+fig_count <- fig_count + 1
+```
+<div style="text-align:center"><img src=`r file` width="70%" height="70%"/></div>
+
+### No "Overall" judgement
+
+By default, both functions include an "Overall" risk of bias domain. To prevent this, set `overall = FALSE`.
+
+```{r, eval=FALSE}
+summary_rob <- rob_summary(data = data_rob2, tool = "ROB2", overall = FALSE)
 summary_rob
@@
 
-### Created an unweighted summary barplot
-By default, the `rob_summary()` function creates a barplot weighted by some measure of a study's precision.
-This can be prevented using the "weighted" argument.
-For example, compare the following two plots:
+``` {r, echo = FALSE}
+plot <- rob_summary(data = data_rob2,
+                           tool = "ROB2",
+                           colour = c("#f442c8",
+                                      "#bef441",
+                                      "#000000",
+                                      "#d16684"))
+file = paste0("man/figures/robplot",fig_count,".png")
+rob_save(plot, file)
+fig_count <- fig_count + 1
+```
+<div style="text-align:center"><img src=`r file` width="70%" height="70%"/></div>
 
-```{r, fig.height=3}
-summary_rob <- rob_summary(data = data_rob2, tool = "ROB2")
-summary_rob
+```{r, eval=FALSE}
+rob_traffic_light(data = data_rob2,
+                  tool = "ROB2",
+                  overall = FALSE)
 ```
 
-```{r, fig.height=3}
-summary_rob <- rob_summary(data = data_rob2, tool = "ROB2", weighted = FALSE)
-summary_rob
+``` {r, echo = FALSE}
+plot <- rob_traffic_light(data = data_rob2,
+                                      tool = "ROB2",
+                                      overall = FALSE)
+file = paste0("man/figures/robplot",fig_count,".png")
+rob_save(plot, file)
+fig_count <- fig_count + 1
 ```
+<div style="text-align:center"><img src=`r file` width="70%" height="70%"/></div>
 
@@
 
-For example, to add a title to the unweighted RoB2.0 plot created above:
-```{r warning=FALSE, fig.height=3}
+For example, to add a title:
+```{r, eval=FALSE}
 library(ggplot2)
 
-summary_rob +
-  ggtitle("Summary of RoB2.0 assessments")
+rob_summary(data = data_rob2, tool = "ROB2") +
+  ggtitle("Summary of RoB 2.0 assessments")
 ```
+
+``` {r, echo = FALSE}
+plot <- rob_summary(data = data_rob2, tool = "ROB2") +
+  ggplot2::ggtitle("Summary of RoB2.0 assessments")
+file = paste0("man/figures/robplot",fig_count,".png")
+rob_save(plot, file)
+fig_count <- fig_count + 1
+```
+<div style="text-align:center"><img src=`r file` width="70%" height="70%"/></div>
 

### 2021-01-15 R/rob_append_to_forest.R
Clean-up

@@ -1,0 +1,272 @@
+#' @title Append a risk-of-bias traffic-light plot to forest plot
+#'
+#' @description A wrapper for metafor::forest function, which adds a risk of
+#'   bias traffic-light plot to the right-hand side of the forest plot. The
+#'   heavy lifting for this function is done by metafor. Note that if not
+#'   specified as additional arguments, this functions sets the header argument
+#'   of metafor::forest() to TRUE.
+#'
+#' @param res Output from metafor meta-analysis function
+#' @param rob_data Risk of bias dataset in standard robvis format
+#' @param rob_psize Size of the points in the appended risk of bias table
+#' @param rob_colour Risk of bias colour scheme to use for the traffic-light
+#'   plot
+#' @param rob_caption Logical specifying whether a message containing the
+#'   risk-of-bias domains should be printed. Default is TRUE
+#' @param rob_legend Logical specifying whether a legend for the risk-of-bias
+#'   plot should be shown. Default is TRUE.
+#' @param ... Additional arguments to be passed to the metafor::forest()
+#'   function
+#' @export
+
+rob_append_to_forest <-
+  function(res,
+           rob_data,
+           rob_colour = "cochrane",
+           rob_psize = 2,
+           rob_caption = TRUE,
+           rob_legend = TRUE,
+           ...) {
+
+    rob <- rob_data
+    tool <- "ROB2"
+    colour <- rob_colour
+
+    # Checks
+
+    if (!("rma" %in% class(res))) {
+      stop("Result objects need to be of class \"meta\" - output from metafor package functions")
+    }
+
+    # Check that the specif
+    check_tool(tool, forest = TRUE)
+    check_data(rob)
+    colour <- weird_spelling(colour)
+
+    # Check names
+    res$slab <- gsub(",", "", res$slab)
+
+    colnames(rob) <- stringr::str_to_lower(colnames(rob))
+
+    if (!all(res$slab %in% rob$study)) {
+      stop("Mismatched names between the \"meta\" object and the risk of bias dataset")
+    }
+
+    # Clean data
+    max_domain_column <- ifelse(tool == "ROB2",7,9)
+
+    rob <-
+      cbind(rob[, 1], data.frame(lapply(rob[, 2:max_domain_column], clean_data),
+                                 stringsAsFactors = F))
+
+
[…]

### 2021-01-15 R/rob_blobbogram.R

@@ -1,278 +1,3 @@
-#' @title Append a risk-of-bias traffic-light plot to forest plot
-#'
-#' @description A wrapper for metafor::forest function, which adds a risk of
-#'   bias traffic-light plot to the right-hand side of the forest plot. The
-#'   heavy lifting for this function is done by metafor. Note that if not
-#'   specified as additional arguments, this functions sets the header argument
-#'   of metafor::forest() to TRUE.
-#'
-#' @param res Output from metafor meta-analysis function
-#' @param rob_data Risk of bias dataset in standard robvis format
-#' @param rob_psize Size of the points in the appended risk of bias table
-#' @param rob_colour Risk of bias colour scheme to use for the traffic-light
-#'   plot
-#' @param rob_caption Logical specifying whether a message containing the
-#'   risk-of-bias domains should be printed. Default is TRUE
-#' @param rob_legend Logical specifying whether a legend for the risk-of-bias
-#'   plot should be shown. Default is TRUE.
-#' @param ... Additional arguments to be passed to the metafor::forest()
-#'   function
-#' @export
-
-rob_append_to_forest <-
-  function(res,
-           rob_data,
-           rob_colour = "cochrane",
-           rob_psize = 2,
-           rob_caption = TRUE,
-           rob_legend = TRUE,
-           ...) {
-
-    rob <- rob_data
-    tool <- "ROB2"
-    colour <- rob_colour
-
-    # Checks
-
-    if (!("rma" %in% class(res))) {
-      stop("Result objects need to be of class \"meta\" - output from metafor package functions")
-    }
-
-    # Check that the specif
-    check_tool(tool, forest = TRUE)
-    check_data(rob)
-    colour <- weird_spelling(colour)
-
-    # Check names
-    res$slab <- gsub(",", "", res$slab)
-
-    colnames(rob) <- stringr::str_to_lower(colnames(rob))
-
-    if (!all(res$slab %in% rob$study)) {
-      stop("Mismatched names between the \"meta\" object and the risk of bias dataset")
-    }
-
-    # Clean data
-    max_domain_column <- ifelse(tool == "ROB2",7,9)
-
-    rob <-
-      cbind(rob[, 1], data.frame(lapply(rob[, 2:max_domain_column], clean_data),
-                                 stringsAsFactors = F))
-
-
[…]

### 2021-01-15 tests/testthat/test_blobbogram.R

@@ -36,17 +36,17 @@ context("Check Blobbograms")
   dat.robins <- rbind(data_robins, data_robins[1,])
   dat.robins$Study <- paste(dat$author,dat$year)
 
-  # test_that("ROB - Append forest - Errors", {
-  #
-  #   vector <- c()
-  #
-  #   expect_error(rob_append_to_forest(vector, dat.rob2))
-  #
-  #   dat.rob.misnamed <- dat.rob2
-  #   dat.rob.misnamed[3,1] <- "Blarg"
-  #
-  #   expect_error(rob_append_to_forest(res, dat.rob.misnamed))
-  # })
+  test_that("ROB - Append forest - Errors", {
+
+    vector <- c()
+
+    expect_error(rob_append_to_forest(vector, dat.rob2))
+
+    dat.rob.misnamed <- dat.rob2
+    dat.rob.misnamed[3,1] <- "Blarg"
+
+    expect_error(rob_append_to_forest(res, dat.rob.misnamed))
+  })
 
   test_that("ROB - Append forest - ROB2",{
 
@@ -89,24 +89,3 @@ context("Check Blobbograms")
                               writer = svg_ordered)
 
   })
-
-
-  # test_that("ROB Blobbogram",{
-  #   # Note, for this approach to work, you need to run
-  #   # visualTest::getFingerprint() on the image that you know is correct. This
-  #   # then provides the hash key used in visualTest::isSimilar()
-  #
-  #   ff <- tempfile(fileext = ".png")
-  #
-  #   suppressWarnings(rob_blobbogram(res,
-  #                                   dat.rob2,
-  #                                   file_path = ff,
-  #                                   display = FALSE))
-  #
-  #   new <- visualTest::getFingerprint(ff)
-  #
-  #   expect_true(visualTest::isSimilar(ff,"AB78BF62800DF08F", ))
-  #
-  #   unlink(ff)
-  #
-  # })

### 2021-01-15 R/data_quadas.R
Clean-up data file definitions

@@ -1,15 +1,0 @@
-#' Example QUADAS-2 assessment
-#'
-#' @format A data frame:
-#' \describe{
-#'   \item{Study}{Study details}
-#'   \item{D1}{Domain 1}
-#'   \item{D2}{Domain 2}
-#'   \item{D3}{Domain 3}
-#'   \item{D4}{Domain 4}
-#'   \item{Overall}{Overall risk of bias}
-#'   \item{Weight}{Weight measure for each study}
-#'          }
-#' @source {Created for this package}
-#' @keywords internal
-"data_quadas"

### 2021-01-15 R/data_rob1.R

@@ -1,19 +1,0 @@
-#' Example ROB1 assessment
-#'
-#' @format A data frame:
-#' \describe{
-#'   \item{Study}{Study details}
-#'   \item{Random.sequence.generation.}{Domain 1}
-#'   \item{Allocation.concealment.}{Domain 2}
-#'   \item{Blinding.of.participants.and.personnel.}{Domain 3}
-#'   \item{Blinding.of.outcome.assessment}{Domain 4}
-#'   \item{Incomplete.outcome.data}{Domain 5}
-#'   \item{Selective.reporting.}{Domain 6}
-#'   \item{Other.sources.of.bias.}{Domain 7}
-#'   \item{Overall}{Overall risk of bias}
-#'   \item{Weight}{Weight measure for each study}
-#'          }
-#' @source {Created for this package}
-#' @keywords internal
-
-"data_rob1"

### 2021-01-15 R/data_rob2_cluster.R

@@ -1,18 +1,0 @@
-#' Example ROB2.0 assessment
-#'
-#' @format A data frame:
-#' \describe{
-#'   \item{Study}{Study details}
-#'   \item{D1}{Domain 1}
-#'   \item{D1b}{Domain 1b}
-#'   \item{D2}{Domain 2}
-#'   \item{D3}{Domain 3}
-#'   \item{D4}{Domain 4}
-#'   \item{D5}{Domain 5}
-#'   \item{Overall}{Overall risk of bias}
-#'   \item{Weight}{Weight measure for each study}
-#'          }
-#' @source {Created for this package}
-#' @keywords internal
-
-"data_rob2_cluster"

### 2021-01-15 R/rob_append_to_forest.R

@@ -22,15 +22,14 @@
 rob_append_to_forest <-
   function(res,
            rob_data,
+           rob_tool = "ROB2",
            rob_colour = "cochrane",
            rob_psize = 2,
            rob_caption = TRUE,
            rob_legend = TRUE,
            ...) {
 
-    rob <- rob_data
-    tool <- "ROB2"
-    colour <- rob_colour
+    rob_colour <- rob_colour
 
     # Checks
 
@@ -38,35 +37,38 @@ rob_append_to_forest <-
       stop("Result objects need to be of class \"meta\" - output from metafor package functions")
     }
 
-    # Check that the specif
-    check_tool(tool, forest = TRUE)
-    check_data(rob)
-    colour <- weird_spelling(colour)
+    # Check that the specified tool is supported
+    check_tool(rob_tool, forest = TRUE)
+
+    # Check the data supplied is okay
+    check_data(rob_data)
+
+    # Convert spelling if US
+    rob_colour <- weird_spelling(rob_colour)
 
     # Check names
     res$slab <- gsub(",", "", res$slab)
 
-    colnames(rob) <- stringr::str_to_lower(colnames(rob))
+    colnames(rob_data) <- stringr::str_to_lower(colnames(rob_data))
 
-    if (!all(res$slab %in% rob$study)) {
+    if (!all(res$slab %in% rob_data$study)) {
       stop("Mismatched names between the \"meta\" object and the risk of bias dataset")
     }
 
     # Clean data
-    max_domain_column <- ifelse(tool == "ROB2",7,9)
+    max_domain_column <- ifelse(rob_tool == "ROB2",7,9)
 
-    rob <-
-      cbind(rob[, 1], data.frame(lapply(rob[, 2:max_domain_column], clean_data),
+    rob_data <-
+      cbind(rob_data[, 1], data.frame(lapply(rob_data[, 2:max_domain_column], clean_data),
                                  stringsAsFactors = F))
 
 
     # Get and expand original x limits to allow for ROB plot ====
 
-
     # Call metafor::forest to get returned plot values
-    # Funct
-    t <- forest.invisible(res, ...)
+    # Function is defined in blobbogram_helpers.R
 
+    t <- forest.invisible(res, ...)
 
     # Using original x_lim, create elements needed for new plot
     # Position of columns along the x-axis
[…]

### 2021-01-15 R/rob_data.R

@@ -1,0 +1,109 @@
+#' Example QUADAS-2 assessment
+#'
+#' @format A data frame:
+#' \describe{
+#'   \item{Study}{Study details}
+#'   \item{D1}{Domain 1}
+#'   \item{D2}{Domain 2}
+#'   \item{D3}{Domain 3}
+#'   \item{D4}{Domain 4}
+#'   \item{Overall}{Overall risk of bias}
+#'   \item{Weight}{Weight measure for each study}
+#'          }
+#' @source {Created for this package}
+#' @keywords internal
+"data_quadas"
+
+#' Example QUIPS assessment
+#'
+#' @format A data frame:
+#' \describe{
+#'   \item{Study}{Study details}
+#'   \item{D1}{Domain 1}
+#'   \item{D2}{Domain 2}
+#'   \item{D3}{Domain 3}
+#'   \item{D4}{Domain 4}
+#'   \item{D5}{Domain 5}
+#'   \item{D6}{Domain 6}
+#'   \item{Overall}{Overall risk of bias}
+#'   \item{Weight}{Weight measure for each study}
+#'          }
+#' @source {Created for this package}
+#' @keywords internal
+"data_quips"
+
+#' Example ROB1 assessment
+#'
+#' @format A data frame:
+#' \describe{
+#'   \item{Study}{Study details}
+#'   \item{Random.sequence.generation.}{Domain 1}
+#'   \item{Allocation.concealment.}{Domain 2}
+#'   \item{Blinding.of.participants.and.personnel.}{Domain 3}
+#'   \item{Blinding.of.outcome.assessment}{Domain 4}
+#'   \item{Incomplete.outcome.data}{Domain 5}
+#'   \item{Selective.reporting.}{Domain 6}
+#'   \item{Other.sources.of.bias.}{Domain 7}
+#'   \item{Overall}{Overall risk of bias}
+#'   \item{Weight}{Weight measure for each study}
+#'          }
+#' @source {Created for this package}
+#' @keywords internal
+
+"data_rob1"
+
+#' Example ROB2.0 assessment
+#'
+#' @format A data frame:
+#' \describe{
+#'   \item{Study}{Study details}
+#'   \item{D1}{Domain 1}
+#'   \item{D2}{Domain 2}
+#'   \item{D3}{Domain 3}
+#'   \item{D4}{Domain 4}
+#'   \item{D5}{Domain 5}
+#'   \item{Overall}{Overall risk of bias}
[…]

### 2021-01-15 R/rob_append_to_forest.R
Range of updates - should be back to working now!

@@ -1,4 +1,4 @@
-#' @title Append a risk-of-bias traffic-light plot to forest plot
+#' @title Append a risk-of-bias traffic-light plot to a forest plot
 #'
 #' @description A wrapper for metafor::forest function, which adds a risk of
 #'   bias traffic-light plot to the right-hand side of the forest plot. The
@@ -9,6 +9,8 @@
 #' @param res Output from metafor meta-analysis function
 #' @param rob_data Risk of bias dataset in standard robvis format
 #' @param rob_psize Size of the points in the appended risk of bias table
+#' @param rob_tool The risk-of-bias assessment tool used to perform the
+#'   assessments
 #' @param rob_colour Risk of bias colour scheme to use for the traffic-light
 #'   plot
 #' @param rob_caption Logical specifying whether a message containing the

### 2021-01-15 R/rob_tools.R

@@ -44,7 +44,7 @@ rob_tools <- function(forest = FALSE) {
 #' @export
 #'
 #' @examples
-#'
+#' \donttest{
 #' dat.bcg <- metafor::dat.bcg[c(1:9),]
 #'
 #' dat <-
@@ -62,9 +62,10 @@ rob_tools <- function(forest = FALSE) {
 #'
 #' data_rob2$Study <- paste(dat$author,dat$year)
 #'
-#' rob_weighted_data <- rob_append_weights(data_rob2, res)
+#' rob_weighted_data <- rob_append_weights(data_rob2[,1:7], res)
 #'
 #' rob_summary(rob_weighted_data, tool = "ROB2", weighted = TRUE)
+#' }
 
 rob_append_weights <- function(data, res){
 

### 2021-01-27 README.Rmd

@@
 #### 1. rob_summary()
-Returns a ggplot object displaying a barchart of the risk of bias of included studies across the domains of the specified tool.
+Returns a ggplot object displaying a bar-chart of the risk of bias of included studies across the domains of the specified tool.
 [*Note: the defaults used in this function have changed from their original settings, so that a un-weighted barplot is now produced by default.
@@
 ``` {r, echo = FALSE}
-plot <- rob_summary(data = data_rob2,
-                           tool = "ROB2",
-                           colour = c("#f442c8",
-                                      "#bef441",
-                                      "#000000",
-                                      "#d16684"))
+plot <- rob_summary(data = data_rob2, tool = "ROB2", overall = FALSE)
 file = paste0("man/figures/robplot",fig_count,".png")

### 2021-01-27 R/rob_blobbogram.R
fully rewritten rob_blobbogram() which offloads much of the heavy lifting for alignment and prep of the forest plot itself to the forester package

@@ -1,498 +1,261 @@
-#' # Put in NEWS.md when ready
-#'
-#' # * A new function, `rob_blobbogram()` has been added in response to
-#' # https://github.com/mcguinlu/robvis/issues/102 by @rdboyes.
-#'
-#'
-#'
-#' #' Risk of bias blobbogram plot
-#' #'
-#' #' @param rma an rma object from the metafor package
-#' #' @param rob a risk of bias table formatted like data_rob2
-#' #' @param rob_tool risk of bias tool used
-#' #' @param rob_colour risk of bias colour scheme
-#' #' @param subset_col Column containing the variable to subset the MA by
-#' #' @param add_tests include summary of statistical tests by subgroup
-#' #' @param overall_estimate show a summary measure across groups?
-#' #' @param theme optional theme for the forest plot table
-#' #' @param ggplot_is_x_times_right_width relative width of the forest plot
-#' #' @param null_line_at what value is the null? default 1.0
-#' #' @param file_path path to save the image
-#' #' @param dpi image resolution
-#' #' @param display should the image be shown in the viewer? set to false for markdown
-#' #' @param blank_na show NA values? default is FALSE
-#' #' @param font_family (experimental) change fonts in the table
-#' #' @param estimate_col_name title of the estimate column, default "Estimate"
-#' #'
-#' #' @return an image
-#' rob_blobbogram <- function(rma,
-#'                            rob,
-#'                            rob_tool = "ROB2",
-#'                            rob_colour = "cochrane",
-#'                            subset_col = "Overall",
-#'                            add_tests = TRUE,
-#'                            overall_estimate = TRUE,
-#'                            theme = NULL,
-#'                            ggplot_is_x_times_right_width = 1.2,
-#'                            null_line_at = 1,
-#'                            file_path = tempfile(pattern = "rob_blobbogram", fileext = ".png"),
-#'                            dpi = 600,
-#'                            display = TRUE,
-#'                            blank_na = TRUE,
-#'                            font_family = "mono",
-#'                            estimate_col_name = "Estimate"){
-#'
[…]

### 2021-01-27 R/rob_blobbogram.R
added last helper function

@@ -259,3 +259,28 @@ metafor_object_to_table <- function(rma,
 
   return(dplyr::left_join(ordered_table, rob, by = "Study"))
 }
+
+select_rob_columns <- function(dataframe, tool){
+  if(tool == "QUADAS-2"){
+    return_data <- select(dataframe, D1, D2, D3, D4, Overall)
+  }else if(tool == "ROB1"){
+    return_data <- select(dataframe,
+                          RS = Random.sequence.generation.,
+                          A = Allocation.concealment.,
+                          BP = Blinding.of.participants.and.personnel.,
+                          BO = Blinding.of.outcome.assessment,
+                          I = Incomplete.outcome.data,
+                          SR = Selective.reporting.,
+                          Oth = Other.sources.of.bias.,
+                          Overall = Overall)
+  }else if(tool == "ROB2"){
+    return_data <- select(dataframe, D1, D2, D3, D4, D5, Overall)
+  }else if(tool == "ROB2-Cluster"){
+    return_data <- select(dataframe, D1, D1b, D2, D3, D4, D5, Overall)
+  }else if(tool == "Robins"){
+    return_data <- select(dataframe, D1, D2, D3, D4, D5, D6, D7, Overall)
+  }else{
+    stop("Tool is not supported.")
+  }
+  return(return_data)
+}

### 2021-01-27 R/rob_blobbogram.R
fixe whitespace

@@ -3,8 +3,6 @@
 # * A new function, `rob_blobbogram()` has been added in response to
 # https://github.com/mcguinlu/robvis/issues/102 by @rdboyes.
 
-
-
 #' Risk of bias blobbogram plot
 #'
 #' @param rma an rma object from the metafor package

### 2021-06-04 README.Rmd
Test commit hook

@@
 * [Eliza Grames](https://github.com/elizagrames) for creating the `robvis` hex sticker.
+
+### Research notice
+
+Please note that this repository is participating in a study into sustainability of open source projects.
+Data will be gathered about this repository for approximately the next 12 months, starting from June 2021.
+
+Data collected will include number of contributors, number of PRs, time taken to close/merge these PRs, and issues closed.
+
+For more information, please visit [the informational page](https://sustainable-open-science-and-software.github.io/) or download the [participant information sheet](https://sustainable-open-science-and-software.github.io/assets/PIS_sustainable_software.pdf).

### 2021-06-04 README.Rmd
Add README GitHub Action

@@
 
-By default, both functions include an "Overall" risk of bias domain. To prevent this, set `overall = FALSE`.
+By default, both functions include an "Overall" risk of bias domain. To prevent this, remove the overall column from your dataset and set `overall = FALSE`.
 
 ```{r, eval=FALSE}
-summary_rob <- rob_summary(data = data_rob2, tool = "ROB2", overall = FALSE)
+summary_rob <- rob_summary(data = data_rob2[1:6], tool = "ROB2", overall = FALSE)
 summary_rob
@@
 ``` {r, echo = FALSE}
-plot <- rob_summary(data = data_rob2, tool = "ROB2", overall = FALSE)
+plot <- rob_summary(data = data_rob2[1:6], tool = "ROB2", overall = FALSE)
 file = paste0("man/figures/robplot",fig_count,".png")
@@
 ```{r, eval=FALSE}
-rob_traffic_light(data = data_rob2,
+rob_traffic_light(data = data_rob2[1:6],
                   tool = "ROB2",
@@
 ``` {r, echo = FALSE}
-plot <- rob_traffic_light(data = data_rob2,
+plot <- rob_traffic_light(data = data_rob2[1:6],
                                       tool = "ROB2",

### 2022-09-03 R/rob_dummy.R
Add support for ROBINS-E

@@ -24,8 +24,13 @@ rob_dummy <- function(n, tool = "ROB2", study = TRUE){
     ncol = 5
   }
 
-  if (tool %in% c("ROBINS-I","ROBINS-E")) {
-    prob = c(.025, .5, .5, 0.25, 0.025)
+  if (tool == "ROBINS-E") {
+    prob = c(.025, .45, .55, 0.25, 0.025)
+    ncol = 7
+  }
+
+  if (tool == "ROBINS-I") {
+    prob = c(.025, .55, .45, 0.25, 0.025)
     ncol = 7
   }
 

### 2022-09-03 R/rob_tools.R

@@ -14,7 +14,8 @@ rob_tools <- function(forest = FALSE) {
 
   if (forest) {
     tools <- c("ROB2",
-               "ROBINS-I")
+               "ROBINS-I",
+               "ROBINS-E")
   } else {
     tools <- c("ROB2",
                "ROB2-Cluster",

### 2022-09-03 R/helpers.R
Add testing helper

@@ -575,12 +575,35 @@ clean_data <- function(col) {
   return(col)
 }
 
-# Used in testing
-save_png <- function(code, width = 1200, height = 800) {
+# Used in testing ==============================================================
+save_png <- function(code, width = 1400, height = 800) {
   path <- tempfile(fileext = ".png")
-  png(path, width = width, height = height)
-  on.exit(dev.off())
+  grDevices::png(path, width = width, height = height)
+  on.exit(grDevices::dev.off())
   code
 
   return(path)
+}
+
+get_res <- function(tool){
+
+  dat.bcg <-
+    cbind(metadat::dat.bcg, rob_dummy(13, tool, study = FALSE))
+
+  dat <-
+    metafor::escalc(
+      measure = "RR",
+      ai = tpos,
+      bi = tneg,
+      ci = cpos,
+      di = cneg,
+      data = dat.bcg,
+      slab = paste(author, year, sep = ", ")
+    ) %>%
+    dplyr::mutate(Study = paste(author, year))
+
+  # Prep bias datasets
+  res <- metafor::rma(yi, vi, data = dat, slab = paste(author, year))
+
+  return(res)
 }

### 2022-09-03 R/rob_forest.R
Improve robustness of rob_forest

@@ -47,13 +47,7 @@ rob_forest <-
 
 
     if (is.null(rob_levels)) {
-
-    if (rob_tool == "ROB2") {
-      rob_levels <- rev(c("Low","Some concerns","High","Critical"))
-    } else {
-      rob_levels <- rev(c("Low","Moderate","Serious","Critical"))
-    }
-
+      rob_levels <- get_judgements(rob_tool)
     }
 
     colnames(res$data) <- stringr::str_to_lower(colnames(res$data))
@@ -114,10 +108,11 @@ rob_forest <-
       x_min = -10
     } else {
       x_min <- arg$x_min
+      arg$x_min <- NULL
     }
 
     x_max = 4.6 - log(3) + x_adj
-    textpos <- c(x_min, x_max-1)
+    textpos <- c(x_min, x_max-0.5)
     y_max <- max(rows)+4
 
     #-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-
@@ -171,7 +166,8 @@ rob_forest <-
     }
 
     if (rob_tool == "ROBINS-I") {
-      judgements<-   c("Serious risk of bias",
+      judgements<-   c("Critical risk of bias",
+                       "Serious risk of bias",
                        "Moderate risk of bias",
                        "Low risk of bias",
                        "No information")
@@ -201,18 +197,73 @@ rob_forest <-
 
     }
 
+
+    if (rob_tool == "ROBINS-E") {
+      judgements<-   c("Very high risk of bias",
+                       "High risk of bias",
+                       "Some concerns",
+                       "Low risk of bias",
+                       "No information")
+      cols <- c(
+        v = rob_colours$critical_colour,
+        h = rob_colours$high_colour,
+        s = rob_colours$concerns_colour,
+        l = rob_colours$low_colour,
+        n = rob_colours$ni_colour,
+        x = rob_colours$na_colour
+      )
+
+      syms <- c(v = "!",
+                h = "X",
+                s = "-",
+                l = "+",
+                n = "",
+                x = "")
+
+
+      shapes <- c(v = 15,
+                  h = 15,
+                  s = 15,
+                  l = 15,
+                  n = 15,
+                  x = 15)
+
+    }
[…]

### 2022-09-03 R/rob_summary.R
Hide unused levels in main functions

@@ -175,7 +175,9 @@ rob_summary_rob2 <- function(data,
         s = "  Some concerns   ",
         l = "  Low risk        ",
         x = "  N/A  "
-      )
+      ),
+      drop = TRUE,
+      limits = force
     )
 
   return(plot)
@@ -217,21 +219,23 @@ rob_summary_robinsi <- function(data,
     rob_summ_theme(overall, max_domain_column - 2) +
     ggplot2::scale_fill_manual(
       values = c(
-        n = rob_colours$ni_colour,
-        m = rob_colours$concerns_colour,
-        s = rob_colours$high_colour,
         l = rob_colours$low_colour,
+        x = rob_colours$na_colour,
+        n = rob_colours$ni_colour,
         c = rob_colours$critical_colour,
-        x = rob_colours$na_colour
+        s = rob_colours$high_colour,
+        m = rob_colours$concerns_colour
       ),
       labels = c(
-        n = " No information ",
-        c = " Critical risk  ",
-        s = " Serious risk  ",
-        m = " Moderate risk ",
         l = " Low risk  ",
+        m = " Moderate risk ",
+        s = " Serious risk  ",
+        c = " Critical risk  ",
+        n = " No information ",
         x = " N/A "
-      )
+      ),
+      drop = TRUE,
+      limits = force
     )
 
   return(plot)
@@ -279,12 +283,14 @@ rob_summary_robinse <- function(data,
       ),
       labels = c(
         n = " No information ",
-        v = " Critical risk  ",
-        h = " Serious risk  ",
-        s = " Moderate risk ",
+        v = " Very high risk ",
+        h = " High risk  ",
+        s = " Some concerns ",
         l = " Low risk  ",
         x = " N/A "
-      )
+      ),
+      drop = TRUE,
+      limits = force
     )
 
   return(plot)
@@ -323,10 +329,10 @@ rob_summary_quadas2 <- function(data,
     ggplot2::scale_fill_manual(
       "Risk of Bias",
       values = c(
-        n = rob_colours$ni_colour,
-        h = rob_colours$high_colour,
-        s = rob_colours$concerns_colour,
         l = rob_colours$low_colour,
+        s = rob_colours$concerns_colour,
+        h = rob_colours$high_colour,
+        n = rob_colours$ni_colour,
         x = rob_colours$na_colour
       ),
       labels = c(
@@ -335,7 +341,9 @@ rob_summary_quadas2 <- function(data,
[…]

### 2022-09-03 R/rob_traffic_light.R

@@ -203,7 +203,9 @@ rob_traffic_light_rob2 <- function(data,
         l = "Low",
         n = "No information",
         x = "Not applicable"
-      )
+      ),
+      drop = TRUE,
+      limits = force
     ) +
     ggplot2::scale_shape_manual(
       values = c(
@@ -219,7 +221,9 @@ rob_traffic_light_rob2 <- function(data,
         l = "Low",
         n = "No information",
         x = "Not applicable"
-      )
+      ),
+      drop = TRUE,
+      limits = force
     )
 
   return(trafficlightplot)
@@ -283,7 +287,9 @@ rob_traffic_light_rob2_cluster <- function(data,
         l = "Low",
         n = "No information",
         x = "Not applicable"
-      )
+      ),
+      drop = TRUE,
+      limits = force
     ) +
     ggplot2::scale_shape_manual(
       values = c(
@@ -299,7 +305,9 @@ rob_traffic_light_rob2_cluster <- function(data,
         l = "Low",
         n = "No information",
         x = "Not applicable"
-      )
+      ),
+      drop = TRUE,
+      limits = force
     )
 
 
@@ -370,7 +378,9 @@ rob_traffic_light_robinsi <- function(data,
         l = "Low",
         n = "No information",
         x = "Not applicable"
-      )
+      ),
+      drop = TRUE,
+      limits = force
     ) +
     ggplot2::scale_shape_manual(
       values = c(
@@ -388,7 +398,9 @@ rob_traffic_light_robinsi <- function(data,
         l = "Low",
         n = "No information",
         x = "Not applicable"
-      )
+      ),
+      drop = TRUE,
+      limits = force
     )
 
   return(trafficlightplot)
@@ -457,7 +469,9 @@ rob_traffic_light_robinse <- function(data,
         l = "Low",
         n = "No information",
         x = "Not applicable"
-      )
+      ),
+      drop = TRUE,
+      limits = force
     ) +
     ggplot2::scale_shape_manual(
       values = c(
@@ -475,7 +489,9 @@ rob_traffic_light_robinse <- function(data,
         l = "Low",
         n = "No information",
         x = "Not applicable"
-      )
+      ),
+      drop = TRUE,
+      limits = force
     )
 
   return(trafficlightplot)
@@ -537,7 +553,9 @@ rob_traffic_light_quadas2 <- function(data,
         l = "Low",
         n = "No information",
         x = "Not applicable"
-      )
[…]

### 2022-09-03 R/robvis.R
Fix global variables issue

@@ -28,5 +28,11 @@ globalVariables(c(
   "row_n",
   "study",
   "type",
-  "yi"
+  "yi",
+  "cneg",
+  "cpos",
+  "tneg",
+  "tpos",
+  "vi",
+  "year"
 ))

### 2022-09-03 tests/testthat/test_forest.R
Improve testing approach

@@ -1,0 +1,63 @@
+# Set-up ----
+
+# Perform meta-analysis
+set.seed(1)
+
+test_that("Check paired plots", {
+  expect_snapshot_file(save_png({
+    rob_forest(get_res("ROB2"),"ROB2")
+
+  }), "paired_rob2.png")
+
+
+    expect_snapshot_file(save_png({
+      rob_forest(get_res("ROBINS-I"),"ROBINS-I")
+
+    }), "paired_robinsi.png")
+
+    expect_snapshot_file(save_png({
+      rob_forest(get_res("ROBINS-E"),"ROBINS-E")
+
+    }), "paired_robinse.png")
+
+
+  expect_snapshot_file(save_png({
+    rob_forest(
+      get_res("ROB2"),
+      atransf = exp,
+      xlim = c(-16, 7),
+      at = log(c(.05, .25, 1, 4)),
+      ilab = cbind(metadat::dat.bcg$tpos,
+                   metadat::dat.bcg$tneg,
+                   metadat::dat.bcg$cpos,
+                   metadat::dat.bcg$cneg),
+      ilab.xpos = c(-9.5, -8, -6, -4.5),
+      header = "Author(s) and Year",
+      textpos = c(-16, 6),
+      cex = 1,
+      mlab = "RE Model (Q=",
+      rob_caption = FALSE
+    )
+  }), "paired_rob2_complex.png")
+
+  expect_snapshot_file(save_png({
+    rob_forest(
+      get_res("ROBINS-I"),
+      rob_tool = "ROBINS-I",
+      atransf = exp,
+      xlim = c(-16, 7),
+      at = log(c(.05, .25, 1, 4)),
+      ilab = cbind(metadat::dat.bcg$tpos,
+                   metadat::dat.bcg$tneg,
+                   metadat::dat.bcg$cpos,
+                   metadat::dat.bcg$cneg),
+      ilab.xpos = c(-9.5, -8, -6, -4.5),
+      header = "Author(s) and Year",
+      textpos = c(-16, 6),
+      cex = 1,
+      mlab = "RE Model (Q=",
+      rob_caption = FALSE
+    )
+  }), "paired_robinsi_complex.png")
+
+})

### 2022-09-03 tests/testthat/test_rob_traffic_light.R

@@ -24,6 +24,13 @@ test_that("ROB - Traffic light", {
   expect_snapshot_file(name = "TF - ROBINS-I - Colour - custom.png", rob_save(file = tempfile(fileext = ".png"), rob_traffic_light(data_robins, "ROBINS-I", colour = c("#f442c8", "#bef441", "#000000", "#bef441", "#333333"))))
   expect_snapshot_file(name = "TF - ROBINS-I - Overall.png", rob_save(file = tempfile(fileext = ".png"), rob_traffic_light(data_robins[1:8], "ROBINS-I", overall = FALSE)))
 
+  expect_snapshot_file(name = "TF - ROBINS-E - Basic.png", rob_save(file = tempfile(fileext = ".png"), rob_traffic_light(data_robins, "ROBINS-I")))
+  expect_snapshot_file(name = "TF - ROBINS-E - Point Size.png", rob_save(file = tempfile(fileext = ".png"), rob_traffic_light(data_robins, "ROBINS-I", psize = 10)))
+  expect_snapshot_file(name = "TF - ROBINS-E - Colour - cochrane.png", rob_save(file = tempfile(fileext = ".png"), rob_traffic_light(data_robins, "ROBINS-I", colour = "cochrane")))
+  expect_snapshot_file(name = "TF - ROBINS-E - Colour - colourblind.png", rob_save(file = tempfile(fileext = ".png"), rob_traffic_light(data_robins, "ROBINS-I", colour = "colourblind")))
+  expect_snapshot_file(name = "TF - ROBINS-E - Colour - custom.png", rob_save(file = tempfile(fileext = ".png"), rob_traffic_light(data_robins, "ROBINS-I", colour = c("#f442c8", "#bef441", "#000000", "#bef441", "#333333"))))
+  expect_snapshot_file(name = "TF - ROBINS-E - Overall.png", rob_save(file = tempfile(fileext = ".png"), rob_traffic_light(data_robins[1:8], "ROBINS-I", overall = FALSE)))
+
   expect_snapshot_file(name = "TF - QUADAS - Basic.png", rob_save(file = tempfile(fileext = ".png"), rob_traffic_light(data_quadas, "QUADAS-2")))
   expect_snapshot_file(name = "TF - QUADAS - Point size.png", rob_save(file = tempfile(fileext = ".png"), rob_traffic_light(data_quadas, "QUADAS-2", psize = 10)))
[…]

### 2022-09-03 tests/testthat/test_datasets.R
Update a bunch of tests

@@ -11,9 +11,14 @@ test_that("Data dimensions correct - data_rob1", {
   expect_equal(nrow(data_rob1), 9)
 })
 
-test_that("Data dimensions correct - data_robins", {
-  expect_equal(ncol(data_robins), 9)
-  expect_equal(nrow(data_robins), 12)
+test_that("Data dimensions correct - data_robins_i", {
+  expect_equal(ncol(data_robins_i), 9)
+  expect_equal(nrow(data_robins_i), 10)
+})
+
+test_that("Data dimensions correct - data_robins_e", {
+  expect_equal(ncol(data_robins_e), 9)
+  expect_equal(nrow(data_robins_e), 10)
 })
 
 test_that("Data dimensions correct - data_quadas", {

### 2022-09-03 tests/testthat/test_errors.R

@@ -17,7 +17,7 @@ test_that("ROB1 gives message", {
 
 test_that("Colour errors", {
           expect_error(rob_summary(data_rob2, "ROB2", colour = c("#FFFFFF")))
-          expect_error(rob_traffic_light(data_robins,"ROBINS-I", colour = c("#FFFFFF")))
+          expect_error(rob_traffic_light(data_robins_i,"ROBINS-I", colour = c("#FFFFFF")))
 })
 
 test_sum <- data_rob2[, c(1:6)]
@@ -28,8 +28,8 @@ test_that("Too few columns", {
   expect_error(rob_traffic_light(test_tf, "ROB2"))
 })
 
-test_sum <- data_robins[, c(1:8)]
-test_tf <- data_robins[, c(1:8)]
+test_sum <- data_robins_i[, c(1:8)]
+test_tf <- data_robins_i[, c(1:8)]
 
 test_that("Too few columns", {
   expect_error(rob_summary(test_sum, "ROBINS-I"))

### 2022-09-03 tests/testthat/test_forest.R

@@ -35,8 +35,7 @@ test_that("Check paired plots", {
       header = "Author(s) and Year",
       textpos = c(-16, 6),
       cex = 1,
-      mlab = "RE Model (Q=",
-      rob_caption = FALSE
+      mlab = "RE Model (Q="
     )
   }), "paired_rob2_complex.png")
 
@@ -55,8 +54,7 @@ test_that("Check paired plots", {
       header = "Author(s) and Year",
       textpos = c(-16, 6),
       cex = 1,
-      mlab = "RE Model (Q=",
-      rob_caption = FALSE
+      mlab = "RE Model (Q="
     )
   }), "paired_robinsi_complex.png")
 

### 2022-09-03 tests/testthat/test_rob_summary.R

@@ -11,13 +11,19 @@ test_that("ROB - Summary", {
   expect_snapshot_file(name = "ROB1 - Colour - colourblind.png", rob_save(file = tempfile(fileext = ".png"),  rob_summary(data_rob1, "Generic", colour = "colourblind")))
   expect_snapshot_file(name = "ROB1 - Colour - custom.png", rob_save(file = tempfile(fileext = ".png"),  rob_summary(data_rob1, "Generic", colour = c("#f442c8", "#bef441", "#000000", "#bef441", "#4EA1F7"))))
   expect_snapshot_file(name = "ROB1 - Judgement Labels.png", rob_save(file = tempfile(fileext = ".png"),  rob_summary(data_rob1, "Generic", judgement_labels = c("Test1","Test2","Test3","Test4","NI"))))
-  expect_snapshot_file(name = "ROB1 - ROBINS-I Judgement Labels.png", rob_save(file = tempfile(fileext = ".png"),  rob_summary(data_robins, "Generic", judgement_labels = c("Test1","Test2","Test3","Test4","NI"), overall = TRUE)))
+  expect_snapshot_file(name = "ROB1 - ROBINS-I Judgement Labels.png", rob_save(file = tempfile(fileext = ".png"),  rob_summary(data_robins_i, "Generic", judgement_labels = c("Test1","Test2","Test3","Test4","NI"), overall = TRUE)))
 
-  expect_snapshot_file(name = "ROBINS-I - Basic.png", rob_save(file = tempfile(fileext = ".png"),  rob_summary(data_robins, "ROBINS-I")))
-  expect_snapshot_file(name = "ROBINS-I - Overall.png", rob_save(file = tempfile(fileext = ".png"),  rob_summary(data_robins[1:8], "ROBINS-I", overall = FALSE)))
-  expect_snapshot_file(name = "ROBINS-I - Colour - cochrane.png", rob_save(file = tempfile(fileext = ".png"),  rob_summary(data_robins, "ROBINS-I", colour = "cochrane")))
-  expect_snapshot_file(name = "ROBINS-I - Colour - colourblind.png", rob_save(file = tempfile(fileext = ".png"),  rob_summary(data_robins, "ROBINS-I", colour = "colourblind")))
[…]

### 2022-09-03 tests/testthat/test_rob_traffic_light.R

@@ -17,19 +17,19 @@ test_that("ROB - Traffic light", {
   expect_snapshot_file(name = "TF - ROB2C - Colour - custom.png", rob_save(file = tempfile(fileext = ".png"), rob_traffic_light(data_rob2_cluster, "ROB2-Cluster", colour = c("#f442c8", "#bef441", "#000000", "#333333"))))
   expect_snapshot_file(name = "TF - ROB2C - Overall.png", rob_save(file = tempfile(fileext = ".png"), rob_traffic_light(data_rob2_cluster[1:7], "ROB2-Cluster", overall = FALSE)))
 
-  expect_snapshot_file(name = "TF - ROBINS-I - Basic.png", rob_save(file = tempfile(fileext = ".png"), rob_traffic_light(data_robins, "ROBINS-I")))
-  expect_snapshot_file(name = "TF - ROBINS-I - Point Size.png", rob_save(file = tempfile(fileext = ".png"), rob_traffic_light(data_robins, "ROBINS-I", psize = 10)))
-  expect_snapshot_file(name = "TF - ROBINS-I - Colour - cochrane.png", rob_save(file = tempfile(fileext = ".png"), rob_traffic_light(data_robins, "ROBINS-I", colour = "cochrane")))
-  expect_snapshot_file(name = "TF - ROBINS-I - Colour - colourblind.png", rob_save(file = tempfile(fileext = ".png"), rob_traffic_light(data_robins, "ROBINS-I", colour = "colourblind")))
-  expect_snapshot_file(name = "TF - ROBINS-I - Colour - custom.png", rob_save(file = tempfile(fileext = ".png"), rob_traffic_light(data_robins, "ROBINS-I", colour = c("#f442c8", "#bef441", "#000000", "#bef441", "#333333"))))
-  expect_snapshot_file(name = "TF - ROBINS-I - Overall.png", rob_save(file = tempfile(fileext = ".png"), rob_traffic_light(data_robins[1:8], "ROBINS-I", overall = FALSE)))
+  expect_snapshot_file(name = "TF - ROBINS-I - Basic.png", rob_save(file = tempfile(fileext = ".png"), rob_traffic_light(data_robins_i, "ROBINS-I")))
+  expect_snapshot_file(name = "TF - ROBINS-I - Point Size.png", rob_save(file = tempfile(fileext = ".png"), rob_traffic_light(data_robins_i, "ROBINS-I", psize = 10)))
[…]

### 2022-09-06 README.Rmd
Remove unnneeded library calls

@@
 library(robvis)
-
-library(kableExtra)
-library(magrittr)
 ```

### 2022-09-06 R/rob_data.R
Fix problems with pkgdown build

@@ -155,5 +155,7 @@
 #'   \item{\code{d7d}}{character COLUMN_DESCRIPTION}
 #'   \item{\code{overall}}{character COLUMN_DESCRIPTION}
 #'}
-#' @details DETAILS
+#' @source {Created for this package}
+#' @keywords internal
+
 "data_bias_direction"

### 2022-09-06 R/rob_direction.R

@@ -17,7 +17,7 @@
 #' @param label_subgroup_summary Annotation text for subgroup label
 #' @param ... Other arguments to pass to metafor::forest
 #'
-#' @export
+#' @keywords internal
 
 rob_direction <-
   function(dat,
@@ -29,11 +29,6 @@ rob_direction <-
            grouping_levels = c("MR","NRSI","NRSE","RCT"),
            label_subgroup_summary = "RE Model for Subgroup",
            ...) {
-
-
-
-
-
 
     ### calculate log risk ratios and corresponding sampling variances (and use
     ### the 'slab' argument to store study labels as part of the data frame)
@@ -49,7 +44,7 @@ rob_direction <-
         dplyr::mutate(overall = factor(overall, levels = rob_levels)) %>%
         dplyr::arrange(type, overall, dplyr::desc(study))
 
-    dat[is.na(dat)] <- "None"
+   dat[is.na(dat)] <- "None"
 
 
     # Use this to define the gaps between different groups

### 2023-06-27 README.Rmd
Updated README

@@
 
-* Perivoliotis, Konstantinos, et al.
-"[Comparing the efficacy and safety of laparoscopic and robotic adrenalectomy: a meta-analysis and trial sequential analysis.](https://link.springer.com/article/10.1007/s00423-020-01860-9)" Langenbeck's Archives of Surgery (2020): 1-11.
-* Adile, Ashley A., et al.
-"[Salvage therapy for progressive, treatment-refractory or recurrent pediatric medulloblastoma: a systematic review protocol.](https://systematicreviewsjournal.biomedcentral.com/articles/10.1186/s13643-020-01307-8)" Systematic Reviews 9.1 (2020): 1-9.
-* Tanneru, Karthik, et al.
-"[Meta-analysis and systematic review of intermediate-term follow-up of prostatic urethral lift for benign prostatic hyperplasia.](https://link.springer.com/article/10.1007/s11255-020-02408-y)" International Urology and Nephrology (2020): 1-10.
-* Veloso, Andreia, et al..
-"[Effectiveness of Cognitive Training for School-Aged Children and Adolescents With Attention Deficit/Hyperactivity Disorder: A Systematic Review.](https://www.frontiersin.org/articles/10.3389/fpsyg.2019.02983/full)" Frontiers in Psychology 10 (2020): 2983.
-* Simillis, Constantinos, et al.
-"[Postoperative chemotherapy improves survival in patients with resected high‐risk stage II colorectal cancer: results of a systematic review and meta‐analysis.](https://onlinelibrary.wiley.com/doi/pdf/10.1111/codi.14994)" Colorectal Disease (2020).
-* Habadi, Mohammed Ibrahim, et al.
-"[Prevalence of Panic Disorders in the Primary Health Care Setting: A Systematic Review and Meta-Analysis.](https://www.ecronicon.com/ecmi/pdf/prevalence-of-panic-disorders-in-the-primary-health-care-setting-a-systematic-review-and-meta-analysis.pdf)" EC Microbiology 16.1 (2019): 01-09.
-* Gibb, Kate, et al.
-"[The consistent burden in published estimates of delirium occurrence in medical inpatients over four decades: a systematic review and meta-analysis study.](https://www.medrxiv.org/content/medrxiv/early/2019/08/29/19005165.full.pdf)" medRxiv (2019): 19005165.
-
-See more [here](https://scholar.google.com/scholar?cites=12564214960529060925&as_sdt=2005&sciodt=0,5&hl=en).
+To date, `robvis` has been cited in more than 1500 academic articles - these can be explored [here](https://scholar.google.com/scholar?cites=12564214960529060925&as_sdt=2005&sciodt=0,5&hl=en).
 
@@
 * [Eliza Grames](https://github.com/elizagrames) for creating the `robvis` hex sticker.
-
-### Research notice
-
-Please note that this repository is participating in a study into sustainability of open source projects.
-Data will be gathered about this repository for approximately the next 12 months, starting from June 2021.
-
-Data collected will include number of contributors, number of PRs, time taken to close/merge these PRs, and issues closed.
-
-For more information, please visit [the informational page](https://sustainable-open-science-and-software.github.io/) or download the [participant information sheet](https://sustainable-open-science-and-software.github.io/assets/PIS_sustainable_software.pdf).

### 2023-06-27 R/rob_traffic_light.R
Cleaned helper functions - closes #108 Organsied helper functions into groups by type Standardised helper function names Updated calls in main functions to new helper function naming scheme

@@ -49,8 +49,8 @@ rob_traffic_light <-
            ...) {
 
     check_tool(tool)
-    check_data(data)
-    colour <- weird_spelling(colour)
+    check_first_row(data)
+    colour <- clean_colour_spelling(colour)
 
     check_colour(tool = tool, colour = colour)
 
@@ -157,7 +157,7 @@ rob_traffic_light_rob2 <- function(data,
   max_domain_column <- 7
   domain_names <- c("Study", "D1", "D2", "D3", "D4", "D5", "Overall")
 
-  rob.tidy <- tidy_data(data,
+  rob.tidy <- tidy_data_tf(data,
                         max_domain_column = max_domain_column,
                         domain_names = domain_names,
                         overall = overall,
@@ -172,7 +172,7 @@ rob_traffic_light_rob2 <- function(data,
                     ggplot2::aes(x = 1,
                                  y = 1,
                                  colour = judgement)) +
-    rob_tf_theme(rob.tidy,
+    theme_rob_tf(rob.tidy,
                  domain_names,
                  psize,
                  ssize,
@@ -241,7 +241,7 @@ rob_traffic_light_rob2_cluster <- function(data,
   max_domain_column <- 8
   domain_names <- c("Study", "D1", "D1b", "D2", "D3", "D4", "D5", "Overall")
 
-  rob.tidy <- tidy_data(data,
+  rob.tidy <- tidy_data_tf(data,
                         max_domain_column = max_domain_column,
                         domain_names = domain_names,
                         overall = overall,
@@ -255,7 +255,7 @@ rob_traffic_light_rob2_cluster <- function(data,
                                       ggplot2::aes(x = 1,
                                                    y = 1,
                                                    colour = judgement)) +
-    rob_tf_theme(rob.tidy,
+    theme_rob_tf(rob.tidy,
                  domain_names,
                  psize,
                  ssize,
@@ -329,7 +329,7 @@ rob_traffic_light_robinsi <- function(data,
   domain_names <-
     c("Study", "D1", "D2", "D3", "D4", "D5", "D6", "D7", "Overall")
 
-  rob.tidy <- tidy_data(data,
+  rob.tidy <- tidy_data_tf(data,
                         max_domain_column = max_domain_column,
                         domain_names = domain_names,
                         overall = overall,
@@ -343,7 +343,7 @@ rob_traffic_light_robinsi <- function(data,
                                       ggplot2::aes(x = 1,
                                                    y = 1,
[…]

### 2023-06-27 tests/testthat/test_helpers.R

@@ -4,5 +4,5 @@ test_that("Correct number of colours returned", {
 })
 
 test_that("Convert weird spelling of colour", {
-  expect_equal(weird_spelling("colorblind"), "colourblind")
+  expect_equal(clean_colour_spelling("colorblind"), "colourblind")
 })

### 2023-06-27 README.Rmd
Updated README intro paragraph Closes #117

@@
 ```
-The `robvis` package takes the summary table from risk-of-bias assessments and produces plots formatted according to the assessment tool used.
+
+The `robvis` (Risk-Of-Bias VISualization) package facilitates the rapid production of publication-quality risk-of-bias assessment figures, correctly formatted according to the assessment tool used.
+
+The motivation for this package is more fully described in the (open access) article introducing the tool, available [here](https://doi.org/10.1002/jrsm.1411).
 
